### 2013-10-14 article.tex
Added outline for the article.

\documentclass[fleqn,10pt]{SelfArx} % Document font size and equations flushed left

\setlength{\columnsep}{0.55cm} % Distance between the two columns of text
\setlength{\fboxrule}{0.75pt} % Width of the border around the abstract

\definecolor{color1}{RGB}{0,0,0} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings

\newlength{\tocsep} 
\setlength\tocsep{1.5pc} % Sets the indentation of the sections in the table of contents
\setcounter{tocdepth}{3} % Show only three levels in the table of contents section: sections, subsections and subsubsections

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{float}

\JournalInfo{\today} % Journal information
\Archive{First~Draft} % Additional notes (e.g. copyright, DOI, review/research article)

\PaperTitle{A~Study~into~the~Performance~of~Emulated~GPGPU~Kernels} % Article title

\Authors{Eric~Nilsson} % Authors
\affiliation{EricNNilsson@gmail.com}
%\affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

\Keywords{GPGPU, GPU, Performance, Emulation, Simulation} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

% ABSTRACT
\Abstract{
Abstract here.
}

\begin{document}
\flushbottom % Makes all text pages the same height
\maketitle % Print the title and abstract box

\noindent
\textit{"Inspirational quote."}
\begin{center}
- Someone smart.
\end{center}

\tableofcontents % Print the contents section
\thispagestyle{empty} % Removes page numbering from the first page

% INTRODUCTION
\section*{Introduction} % The \section*{} command stops section numbering
\addcontentsline{toc}{section}{\hspace*{-\tocsep}Introduction} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
Introductional things.

% ACKNOWLEDGEMENTS
\section*{Acknowledgments} % The \section*{} command stops section numbering
\addcontentsline{toc}{section}{\hspace*{-\tocsep}Acknowledgments} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.

\bibliographystyle{IEEEtranS}
\bibliography{doc}
\end{document}

### 2013-10-14 article.tex
Added description for each section.

@@
 Abstract here.
+
+% Background	(what)
+%	Vilket sammanhang utgör studiens bakgrund?
+% Challenge		(why)
+%	Vilka utmaningar omfattar studien?
+% Approach		(how)
+%	Vilken ansats tillämpas i studien?
+% Results 		(what)
+%	Vilka resultat gav studien?
 }
@@
 \addcontentsline{toc}{section}{\hspace*{-\tocsep}Introduction} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
-Introductional things.
+\label{sec:introduction}
+% Background and Challenge
+%	Vilket sammanhang utgör studiens bakgrund?
+%	Vilka utmaningar omfattar studien?
+When developing \textit{GPGPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
+between on-chip hardware.
+Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-
+technologies.\\
+\\
+% Approach and Result
+%	Vilken ansats tillämpas i studien?
+%	Vilka resultat gav studien?
+The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from graphics cards - possibly due to architectural differences in-between chip manufacturers.
+A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for a substantial performance-loss.
+This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
+\\
+% Outline and Conclusion
+%	Vilket upplägg har resterande delar av matrialet?
+As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.
 
-% ACKNOWLEDGEMENTS
+% CONTRIBUTION
+\section{Contribution}
+\label{sec:contribution}
+% Introduction
+%	Vilka principer, modeller, metoder och teknologier omfattar studiens design?
+% Contribution
+%	Vilka empiriska resultat erhölls vid experimentdesignens implementation?
+% Conclusion
+% ...for each segment brought up under Contribution.
+
+% CONCLUSION
+\section{Conclusion}
+\label{sec:conclusion}
+% Summary
+%	Vilken bakgrund, utmaning, ansats och resultat omfattar studien?
+% Discussion
+%	Vilka relaterade studier förhåller sig materialet till?
+%	Vilka tvetydliga aspekter av studien kräver diskussion?
+% Answer and Oppertunity
+%	Vilka fortsatta studier föreslår rapportens författare?
+
+% ACKNOWLEDGMENTS
 \section*{Acknowledgments} % The \section*{} command stops section numbering
 \addcontentsline{toc}{section}{\hspace*{-\tocsep}Acknowledgments} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
+\label{sec:acknowledgments}
 I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.

### 2013-10-14 article.tex
Added Introduction and Contribution headlines.

@@
 
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\usepackage{float}
+\usepackage{mdwlist}
 \usepackage{caption}
 \usepackage{verbatim}
-\usepackage{float}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+
+% Consider inserting:
+%\usepackage{kpfonts}
 
@@
 \Archive{First~Draft} % Additional notes (e.g. copyright, DOI, review/research article)
-
-\PaperTitle{A~Study~into~the~Performance~of~Emulated~GPGPU~Kernels} % Article title
-
+\PaperTitle{Emulated~GPGPU~Kernels\\A~Study~into~Performance} % Article title
 \Authors{Eric~Nilsson} % Authors
@@
 %\affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author
-
 \Keywords{GPGPU, GPU, Performance, Emulation, Simulation} % Keywords - if you don't want any simply remove all the text between the curly brackets
@@
 \Abstract{
-Abstract here.
-
+\ldots \\
+As such, the hypothesis suggested in this proposal may be summarized as follows:
+\quote{\textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}}
 % Background	(what)
@@
 This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
+This study concerns an investigation into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some precision.
+\\
+A logical next step of such an evaluation would be to investigate any influence Microsoft WARP may have on computational precision.
+Thus, it is important that the result such a kernel would produce is measurable and deterministic.
+\\
+\\
+This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity.
+As such, Microsoft \textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
+Link to Microsofts page on WARP here!}.\\
 \\
@@
 \label{sec:contribution}
+
+% CONTRIBUTION - METHOD
+\subsection{Method}
+\label{sec:contribution:method}
 % Introduction
 %	Vilka principer, modeller, metoder och teknologier omfattar studiens design?
+The experiment performed includes a DirectCompute \textit{GPGPU}-kernel consisting of a large matrix-multiplication which is calculated, in it’s entirety, in aforementioned kernel.
+The motivation behind such a task is that the result is easily verified as correct, and the precision of such an operation can be tested with different data-types - with regard to the effect Microsoft~\textit{WARP} may have on computational precision.\\
+The test-cases investigated may be summarized as follows:
+% Describe these modes and what they entail:
+\begin{description*}
+\item[Hardware-Acceleration:] \hfill \\
+	The execution of a DirectCompute-kernel on a graphics card. Thus, this case will act as a reference for the remaining experiments.\\
+	Expected high performance.
+\item[Windows~Advanced~Rasterization~Platform~(\textit{WARP}):] \hfill \\
+	The emulated execution of a DirectCompute-kernel using a special software rasterizer devised by Microsoft in their latest revision of the DirectX-framework.\\	
+	Expectations unclear, but expected to perform better than standard software rasterization.
+\item[Software~Rasterization~(DirectX~Reference~Device):] \hfill \\
+	The emulated execution of a DirectCompute-kernel using a software rasterizer.\\
+	Expected poor performance.
+\end{description*}
+In addition to these scenarios, the performance of several kernels with varying lavel of optimization have been examined. These entail the following:
+\begin{enumerate*}
+	\item Basic un-optimized kernel.
+	\item \ldots
+\end{enumerate*}
+% Un-optimized basic kernel.
+% Tiled kernel basic kernel.
+% Tiled kernel utilizing shared memory.
+% Tiled kernel utilizing shared memory with memory coalescing.
+Furthermore, all test-cases have been performed with both integer- and floating-point precision\footnote{Not yet!}.
+As such, the experiment has been devised of the following approximate steps for each scenario:
+\begin{enumerate*}
+	\item Randomize two matrices \textbf{A} \& \textbf{B} using the specified data-type. These matrices will be the subjects of the experiment.
+	\item Establish the product-matrix \textbf{Ref} of the two matrices. The resulting matrix will be used as a reference matrix to verify the final result.
+	\item Start a synchronized high-precision timer.
+	\item Dispatch the DirectCompute-kernel calculating the product matrix \textbf{A}\textbf{B}=\textbf{C}
+	\item Stop the timer once the DirectCompute-kernel has finished.
+	\item Assure that the resulting matrix is correct by comparing \textbf{C} to the previously established reference-matrix \textbf{Ref}.
+\end{enumerate*}
+
+% CONTRIBUTION - TECHNOLOGIES
+\subsection{Technologies}
+\label{sec:contribution:technologies}
+The experiment was subdivided into two major components, both of which use Microsoft~Visual~Studio~2012 for compilation. These are presented below.
+
+\subsubsection*{matrixgen}
+The first, \textit{matrixgen},  was a utility developed to generate matrices of different dimensions and data-types.
+Furthermore, \textit{matrixgen} compiles the reference matrix \textbf{Ref} used when verifying the result returned from DirectCompute.
+\\
+\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices \textbf{A} \& \textbf{B} into product matrix \textbf{Ref}.
+In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
+
+\subsubsection*{experiment}
+The second, \textit{experiment}, uses DirectCompute from the Microsoft~DirectX-framwork to compile the product matrix \textbf{C} from the matrices generated by \textit{matrixgen}.
+\textit{experiment} is written in \texttt{C++} with its respective DirectCompute-kernels written in \texttt{HLSL}.
+As \textit{experiment} is developed using the Windows~8 SDK, Windows~8 is required to run the application.
+\\
+\\
+In order to ease the experimental process, a script was developed to run both \textit{matrixgen} and \textit{experiment} consecutively a number of times with the desired configurations.
+This script, written in \texttt{Python}, then collect and present the results.
+\\
+\\
+The source code used during this study is freely available on \textit{GitHub}\footnote{Link here!}, along with a guide on how to compile and run the solution.
+
+\subsubsection*{Equipment}
+The experiment has been performed on a system with the following specifications:
+\begin{description*}
+	\item[CPU] \hfill \\
+		Intel Q9550 Quad Core 2.83GHz
+	\item[GPU] \hfill \\
+		ATI Radeon HD 5800
+	\item[OS] \hfill \\
+		Windows 8.0
+\end{description*}
+
+% CONTRIBUTION - RESULTS
+\subsection{Results}
+\label{sec:contribution:results}
+
 % Contribution
@@
 
+% CONCLUSION - FUTURE WORK
+\subsection{Future~Work}
+\label{sec:conclusion:futurework}
+
 % ACKNOWLEDGMENTS
@@
 \end{document}
+
+% To-be-inserted references and/or footnotes:
+% Microsoft Warp: http://msdn.microsoft.com/en-us/library/windows/desktop/gg615082%28v=vs.85%29.aspx

### 2013-10-14 article.tex
Added preliminary results.

@@
 \label{sec:contribution:results}
+Preliminary results indicate a surprisingly well-performing WARP, roughly only doubling the execution time in regards to the same kernel hardware accelerated.
+Each configuration has been has been run using the same integer-precision 200x200-matrix.
+To gather the results presented below, each scenario has been run 100 times each.
+Please observe that these are preliminary tests, and more data is to be gathered before the closing of this article.
+\\
+The results gathered during preliminary testing are presented below:
+\begin{center}
+	\begin{tabular}{| l | l | l | l |}
+	\hline
+	Acceleration & Min (ms) & Max (ms) & Average (ms)	\\ \hline
+	Hardware & 25.86  & 43.12  & 26.41			\\ \hline
+	Software & 16141.6 & 16906.7 & 16390.6		\\ \hline
+	WARP & 46.18 & 64.25 & 48.47				\\
+	\hline
+	\end{tabular}
+\end{center}
 
@@
 \label{sec:conclusion}
+Conclusion left out in regards to further development and analysis.
 % Summary

### 2013-10-14 article.tex
Grammar.

@@
 %	Vilka utmaningar omfattar studien?
-When developing \textit{GPGPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
+When developing \textit{GPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
 between on-chip hardware.
@@
 This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
-This study concerns an investigation into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some precision.
+Furthermore, this study concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some computational precision.
 \\

### 2013-10-19 dv2549.py
Script now performs a sequence of experiments of all configurations.

@@ -124,17 +124,34 @@ def experiment( desc ):
 
 # Entry point:
 print( "---\ndv2549\n---" )
-argPrec = "FLOAT"
 
-# Generate a viable matrix:
-matrixgen( factoryDescMat( argPrec, "200", "0", "10" ) )
+# Generate a viable integer matrix:
+matrixgen( factoryDescMat( "INT", "200", "0", "10" ) )
 
-# Perform experiments:
-tasks = []
-tasks.append( factoryDescExp( "TILE", "HARD", argPrec, 5 ) )
-tasks.append( factoryDescExp( "TILE", "SOFT", argPrec, 1 ) )
-tasks.append( factoryDescExp( "TILE", "WARP", argPrec, 5 ) )
-for task in tasks:
+tasksI = []
+tasksI.append( factoryDescExp( "BASIC", "HARD", "INT", 100 ) )
+tasksI.append( factoryDescExp( "BASIC", "SOFT", "INT", 100 ) )
+tasksI.append( factoryDescExp( "BASIC", "WARP", "INT", 100 ) )
+tasksI.append( factoryDescExp( "TILE", "HARD", "INT", 100 ) )
+tasksI.append( factoryDescExp( "TILE", "SOFT", "INT", 100 ) )
+tasksI.append( factoryDescExp( "TILE", "WARP", "INT", 100 ) )
+for task in tasksI:
+	print( "\nPerforming " + str( task.num ) + " experiments with properties:\n\tAcceleration:\t" + task.acc + "\n\tPrecision:\t" + task.prec + "\n" )
+	experiment( task )
+
+# Generate a viable floating point matrix:
+matrixgen( factoryDescMat( "FLOAT", "200", "0", "10" ) )
+
+# Perform experiments of all configurations for floating point precision.
+tasksF = []
+tasksF.append( factoryDescExp( "BASIC", "HARD", "FLOAT", 100 ) )
+tasksF.append( factoryDescExp( "BASIC", "SOFT", "FLOAT", 100 ) )
+tasksF.append( factoryDescExp( "BASIC", "WARP", "FLOAT", 100 ) )
+tasksF.append( factoryDescExp( "TILE", "HARD", "FLOAT", 100 ) )
+tasksF.append( factoryDescExp( "TILE", "SOFT", "FLOAT", 100 ) )
+tasksF.append( factoryDescExp( "TILE", "WARP", "FLOAT", 100 ) )
+
+for task in tasksF:
[…]

### 2013-10-19 article.tex
A more understandable article outline and terminology.

@@
 \JournalInfo{\today} % Journal information
-\Archive{First~Draft} % Additional notes (e.g. copyright, DOI, review/research article)
+\Archive{Unpublished} % Additional notes (e.g. copyright, DOI, review/research article)
 \PaperTitle{Emulated~GPGPU~Kernels\\A~Study~into~Performance} % Article title
@@
 %\affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author
-\Keywords{GPGPU, GPU, Performance, Emulation, Simulation} % Keywords - if you don't want any simply remove all the text between the curly brackets
+\Keywords{GPGPU, GPU,  Simulation, Emulation, DirectCompute, WARP} % Keywords - if you don't want any simply remove all the text between the curly brackets
 \newcommand{\keywordname}{Keywords} % Defines the keywords heading name
@@
 \maketitle % Print the title and abstract box
-
-\noindent
-\textit{"Inspirational quote."}
-\begin{center}
-- Someone smart.
-\end{center}
-
-\tableofcontents % Print the contents section
 \thispagestyle{empty} % Removes page numbering from the first page
@@
 technologies.\\
-\\
 % Approach and Result
 %	Vilken ansats tillämpas i studien?
+The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from the hardware - possibly due to architectural differences in-between chip manufacturers.
+A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for substantial performance-losses.
+Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable.
+This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
+\\
+Furthermore, this study concerns inquiry into the \texttt{DirectCompute}-framework on the \texttt{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \texttt{DirectX} standard software rasterizer, and utilizing the \texttt{DirectX~11.1}-addition Microsoft~\texttt{WARP}\footnote{\texttt{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{Citation needed!}.
+\\
 %	Vilka resultat gav studien?
-The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from graphics cards - possibly due to architectural differences in-between chip manufacturers.
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for a substantial performance-loss.
-This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
-Furthermore, this study concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some computational precision.
-\\
-A logical next step of such an evaluation would be to investigate any influence Microsoft WARP may have on computational precision.
-Thus, it is important that the result such a kernel would produce is measurable and deterministic.
-\\
-\\
-This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity.
-As such, Microsoft \textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
+%\\
+%This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity.
+As such, Microsoft~\texttt{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
 Link to Microsofts page on WARP here!}.\\
@@
 % Outline and Conclusion
+As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.
 %	Vilket upplägg har resterande delar av matrialet?
-As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.
 
@@
 \label{sec:contribution}
+% Introduction
+%	Vilka principer, modeller, metoder och teknologier omfattar studiens design?
 
 % CONTRIBUTION - METHOD
+\subsection{Object~of~Study}
+\label{sec:contribution:objectofstudy}
+Considering possible precision loss caused by \texttt{WARP}, it is important that the object~of~study is measurable and deterministic.
+For the purpose of this experiment, the data computed corresponds to a square matrix~multiplication of dimension 200x200\footnote{Why 200x200?}.
+The result of such an operation can easily be verified as correct, and potential losses in computational precision may be extracted from the expected data-type.
+This operation was therefore considered suitable for the purpose of the experiment.\\
+Throughout this material, the compiled data will thusly be referred to as \textbf{AB=C}\footnote{Insert math!}.
+
 \subsection{Method}
 \label{sec:contribution:method}
-% Introduction
-%	Vilka principer, modeller, metoder och teknologier omfattar studiens design?
-The experiment performed includes a DirectCompute \textit{GPGPU}-kernel consisting of a large matrix-multiplication which is calculated, in it’s entirety, in aforementioned kernel.
-The motivation behind such a task is that the result is easily verified as correct, and the precision of such an operation can be tested with different data-types - with regard to the effect Microsoft~\textit{WARP} may have on computational precision.\\
-The test-cases investigated may be summarized as follows:
+In order to establish the object~of~study \textbf{AB=C}, the experiment utilizes \textit{GPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
+The experiment is devised of the following approximate steps in order to compile the object~of~study \textbf{AB=C}:
+\begin{enumerate*}
+	\item Randomize two matrices \textbf{A} \& \textbf{B} using desired data-type.
+	\item Establish the product-matrix \textbf{AB=Ref}. The resulting matrix will be used as a reference matrix to verify the final result.
+	\item Start a synchronized high-precision timer.
+	\item Dispatch \textit{GPU}-kernel calculating the product matrix \textbf{A}\textbf{B}=\textbf{C}.
+	\item Stop the timer once the kernel has finished execution.
+	\item Establish possible deviation in-between resulting matrix \textbf{C} and the previously established matrix \textbf{Ref}.
+\end{enumerate*}
+
+\subsection{Subjects~of~Study}
+\label{sec:contribution:subjectofstudy}
 % Describe these modes and what they entail:
-\begin{description*}
-\item[Hardware-Acceleration:] \hfill \\
-	The execution of a DirectCompute-kernel on a graphics card. Thus, this case will act as a reference for the remaining experiments.\\
+The \textit{GPU}-kernels described in Section~\ref{sec:contribution:method} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft~\texttt{DirectCompute}.
+These kernels are run using three types of hardware~acceleration with varying methods of \textit{GPU}-kernel emulation.
+These are comprised of the following:
+\paragraph{Standard~GPU~Hardware-Acceleration}
+	The execution of a \texttt{DirectCompute}-kernel on a graphics card. Thus, this case will act as a reference for the emulated subjects.\\
 	Expected high performance.
-\item[Windows~Advanced~Rasterization~Platform~(\textit{WARP}):] \hfill \\
-	The emulated execution of a DirectCompute-kernel using a special software rasterizer devised by Microsoft in their latest revision of the DirectX-framework.\\	
-	Expectations unclear, but expected to perform better than standard software rasterization.
-\item[Software~Rasterization~(DirectX~Reference~Device):] \hfill \\
-	The emulated execution of a DirectCompute-kernel using a software rasterizer.\\
+\paragraph{Software~Rasterization}
+	The emulated execution of a \texttt{DirectCompute}-kernel using the \texttt{DirectX}~Reference~Device~Driver.\\
 	Expected poor performance.
-\end{description*}
+\paragraph{Windows~Advanced~Rasterization~Platform}
+	The emulated execution of a \texttt{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \texttt{DirectX}-framework.\\	
+	Expectations unclear, but expected to perform better than standard software rasterization.\\
+
+\noindent
+These three \texttt{DirectX} driver-types make out the subjects of this study.
+% From these kernels, data entailing the execution time of said kernel may be retrieved - which will make out the main subject~of~study throughout this material.
+Additional data retrieved from the execution concerning the experiment make out precision deviations in resulting matrix \textbf{C} compared to the expected result \textbf{Ref}.\\
+
 In addition to these scenarios, the performance of several kernels with varying lavel of optimization have been examined. These entail the following:
@@
 \end{enumerate*}
+
 % Un-optimized basic kernel.
@@
 % Tiled kernel utilizing shared memory with memory coalescing.
-Furthermore, all test-cases have been performed with both integer- and floating-point precision\footnote{Not yet!}.
-As such, the experiment has been devised of the following approximate steps for each scenario:
-\begin{enumerate*}
-	\item Randomize two matrices \textbf{A} \& \textbf{B} using the specified data-type. These matrices will be the subjects of the experiment.
-	\item Establish the product-matrix \textbf{Ref} of the two matrices. The resulting matrix will be used as a reference matrix to verify the final result.
-	\item Start a synchronized high-precision timer.
-	\item Dispatch the DirectCompute-kernel calculating the product matrix \textbf{A}\textbf{B}=\textbf{C}
-	\item Stop the timer once the DirectCompute-kernel has finished.
-	\item Assure that the resulting matrix is correct by comparing \textbf{C} to the previously established reference-matrix \textbf{Ref}.
-\end{enumerate*}
+
+%Furthermore, all test-cases have been performed with both integer- and floating-point precision\footnote{Not yet!}.
 
@@
 \label{sec:conclusion:futurework}
+% Investigate double precision as to establish probable precision loss in terms of Microsoft WARP.
 
@@
 
+\section*{Appendix}
+\addcontentsline{toc}{section}{\hspace*{-\tocsep}Acknowledgments} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
+\label{sec:appendix}
+% Pseudocode, or source code, or DirectCompute-kernels
+
 \bibliographystyle{IEEEtranS}

### 2013-10-19 article.tex
Re-wrote introduction and Contribution-segments.

@@
 \documentclass[fleqn,10pt]{SelfArx} % Document font size and equations flushed left
+
+\usepackage{float}
+\usepackage{mdwlist}
+\usepackage{caption}
+\usepackage{hyperref}
+\usepackage{verbatim}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{listings}
+
+% Consider inserting:
+%\usepackage{kpfonts}
 
@@
 
-\usepackage{float}
-\usepackage{mdwlist}
-\usepackage{caption}
-\usepackage{verbatim}
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-
-% Consider inserting:
-%\usepackage{kpfonts}
+\lstset { 
+	language=C,
+	tabsize=2,
+	backgroundcolor=\color{black!5},
+	basicstyle=\footnotesize,
+}
 
@@
 \affiliation{EricNNilsson@gmail.com}
-%\affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author
+%\affiliation{*\textit{Corresponding author}: john@smith.com} % Corresponding author
 \Keywords{GPGPU, GPU,  Simulation, Emulation, DirectCompute, WARP} % Keywords - if you don't want any simply remove all the text between the curly brackets
@@
 \\
-Furthermore, this study concerns inquiry into the \texttt{DirectCompute}-framework on the \texttt{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \texttt{DirectX} standard software rasterizer, and utilizing the \texttt{DirectX~11.1}-addition Microsoft~\texttt{WARP}\footnote{\texttt{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{Citation needed!}.
+Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{See Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}}.
 \\
@@
 %This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity.
-As such, Microsoft~\texttt{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
+As such, Microsoft~\textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
 Link to Microsofts page on WARP here!}.\\
@@
 \label{sec:contribution:objectofstudy}
-Considering possible precision loss caused by \texttt{WARP}, it is important that the object~of~study is measurable and deterministic.
-For the purpose of this experiment, the data computed corresponds to a square matrix~multiplication of dimension 200x200\footnote{Why 200x200?}.
-The result of such an operation can easily be verified as correct, and potential losses in computational precision may be extracted from the expected data-type.
+Considering possible precision loss caused by \textit{WARP}, it is important that the object~of~study is measurable and deterministic.
+For the purpose of this experiment, the data computed corresponds to a square matrix~multiplication of dimension $200x200$\footnote{Why 200x200?}.
+The result of such an operation can easily be verified as correct, and potential losses in computational precision may be computed from the expected data-type.
 This operation was therefore considered suitable for the purpose of the experiment.\\
-Throughout this material, the compiled data will thusly be referred to as \textbf{AB=C}\footnote{Insert math!}.
+Throughout this material, the compiled data will thusly be referred to as $AB=C$.
 
@@
 \label{sec:contribution:method}
-In order to establish the object~of~study \textbf{AB=C}, the experiment utilizes \textit{GPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
-The experiment is devised of the following approximate steps in order to compile the object~of~study \textbf{AB=C}:
+In order to establish the object~of~study $AB=C$, the experiment utilizes \textit{GPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
+The experiment is devised of the following approximate steps in order to compile the object~of~study $AB=C$:
 \begin{enumerate*}
-	\item Randomize two matrices \textbf{A} \& \textbf{B} using desired data-type.
-	\item Establish the product-matrix \textbf{AB=Ref}. The resulting matrix will be used as a reference matrix to verify the final result.
+	\item Randomize two matrices $A$ \& $B$ using desired data-type.
+	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
 	\item Start a synchronized high-precision timer.
-	\item Dispatch \textit{GPU}-kernel calculating the product matrix \textbf{A}\textbf{B}=\textbf{C}.
+	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
 	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix \textbf{C} and the previously established matrix \textbf{Ref}.
+	\item Establish possible deviation in-between resulting matrix $C$ and the previously established matrix $Ref$.
 \end{enumerate*}
@@
 % Describe these modes and what they entail:
-The \textit{GPU}-kernels described in Section~\ref{sec:contribution:method} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft~\texttt{DirectCompute}.
-These kernels are run using three types of hardware~acceleration with varying methods of \textit{GPU}-kernel emulation.
+The \textit{GPU}-kernels described in Section~\ref{sec:contribution:method} are comprised of \textit{HLSL}-syntax and are compiled \& executed using Microsoft~\textit{DirectCompute}.
+These kernels are run using three types of hardware~acceleration with varying strategies of \textit{GPU}-kernel emulation.
 These are comprised of the following:
-\paragraph{Standard~GPU~Hardware-Acceleration}
-	The execution of a \texttt{DirectCompute}-kernel on a graphics card. Thus, this case will act as a reference for the emulated subjects.\\
+\paragraph{Hardware-Acceleration~(GPU)}
+	The execution of a \textit{DirectCompute}-kernel on a graphics card. Thus, this case will act as a reference for the emulated subjects.\\
 	Expected high performance.
-\paragraph{Software~Rasterization}
-	The emulated execution of a \texttt{DirectCompute}-kernel using the \texttt{DirectX}~Reference~Device~Driver.\\
+\paragraph{Software~Rasterization~(CPU)}
+	The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX}~Reference~Device~Driver.\\
 	Expected poor performance.
-\paragraph{Windows~Advanced~Rasterization~Platform}
-	The emulated execution of a \texttt{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \texttt{DirectX}-framework.\\	
-	Expectations unclear, but expected to perform better than standard software rasterization.\\
+\paragraph{Windows~Advanced~Rasterization~Platform~(CPU)}
+	The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.\\	
+	Expectations unclear, but expected to perform better than standard software rasterization.\footnote{Insert reference to microsoft warp-msdn-page and explain what WARP promises and stuff about optimization for gpus.}\\
 
 \noindent
-These three \texttt{DirectX} driver-types make out the subjects of this study.
-% From these kernels, data entailing the execution time of said kernel may be retrieved - which will make out the main subject~of~study throughout this material.
-Additional data retrieved from the execution concerning the experiment make out precision deviations in resulting matrix \textbf{C} compared to the expected result \textbf{Ref}.\\
+These three \textit{DirectX} driver-types make out the subjects of this study.
 
-In addition to these scenarios, the performance of several kernels with varying lavel of optimization have been examined. These entail the following:
-\begin{enumerate*}
-	\item Basic un-optimized kernel.
-	\item \ldots
-\end{enumerate*}
+\subsection{Kernels}
+\label{sec:contribution:kernels}
+In addition to the subject drivers mentioned in Section~\ref{sec:contribution:subjectofstudy}, two kernels with varying lavel of optimization have been examined\footnote{Why?}.
+These kernels are presented below.
+\paragraph{Matrix~mult.~w.~Blocks}
+	A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.\\
+	The kernel is executed with one thread for each element in the square matrices, and likewize produce a lone element of the resulting matrix thread-wize.\\
+	Execution is performed in blocks of $16x16$ threads, as this number was found to be the block dimension performing optimally whilst hardware~accelerated on the \textit{GPU}\footnote{Make sure of this!}.
+\paragraph{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
+	Likewize as with the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory}\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
+	This kernel is presented as a test-case due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}.
+Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
 
-% Un-optimized basic kernel.
-% Tiled kernel basic kernel.
-% Tiled kernel utilizing shared memory.
-% Tiled kernel utilizing shared memory with memory coalescing.
-
-%Furthermore, all test-cases have been performed with both integer- and floating-point precision\footnote{Not yet!}.
+\noindent
+Furthermore, aforementioned kernels both support integer- and floating-point precision.\\
+These kernels are attached in their entirety under Appendix.
 
@@
 \label{sec:contribution:technologies}
-The experiment was subdivided into two major components, both of which use Microsoft~Visual~Studio~2012 for compilation. These are presented below.
+\subsubsection{Tools}
+\label{sec:contribution:technologies}
+The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
 
-\subsubsection*{matrixgen}
-The first, \textit{matrixgen},  was a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix \textbf{Ref} used when verifying the result returned from DirectCompute.
+\paragraph{matrixgen}
+Denotes a utility developed to generate matrices of different dimensions and data-types.
+Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from \textit{DirectCompute}.
 \\
-\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices \textbf{A} \& \textbf{B} into product matrix \textbf{Ref}.
-In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
+\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A$~\&~$B$ into product matrix $Ref$.
+In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.\\
+As \textit{matrixgen} utilizes Microsoft~\texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.
 
-\subsubsection*{experiment}
-The second, \textit{experiment}, uses DirectCompute from the Microsoft~DirectX-framwork to compile the product matrix \textbf{C} from the matrices generated by \textit{matrixgen}.
-\textit{experiment} is written in \texttt{C++} with its respective DirectCompute-kernels written in \texttt{HLSL}.
-As \textit{experiment} is developed using the Windows~8 SDK, Windows~8 is required to run the application.
+\paragraph{experiment}
+Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from the matrices generated by \textit{matrixgen}.
+The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
+\textit{experiment} is written in \texttt{C++} with its respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.\\
+As \textit{experiment} is developed using the \textit{Windows~8~SDK}, \textit{Windows~8.0} is required.
+Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
+
+\paragraph{analytics}
+\textit{analytics} is a smaller utility developed to compose data surrounding possible precisional deviations in-between matrices $C$ and $Ref$.
+\textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
+In turn, \textit{analytics} outputs this information to an intermediate file.\\
+\textit{analytics} is written in \texttt{C++}.\\
 \\
-\\
-In order to ease the experimental process, a script was developed to run both \textit{matrixgen} and \textit{experiment} consecutively a number of times with the desired configurations.
-This script, written in \texttt{Python}, then collect and present the results.
-\\
-\\
-The source code used during this study is freely available on \textit{GitHub}\footnote{Link here!}, along with a guide on how to compile and run the solution.
+\noindent
+These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
+This script, written in \textit{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
+More information surrounding how to run these programs can be found via the source repository (see Acknowledgments).
 
-\subsubsection*{Equipment}
-The experiment has been performed on a system with the following specifications:
+\subsubsection{Equipment}
+\label{sec:contribution:equipment}
+The results presented in this study is gathered from experiments performed on a system with the following specifications:
 \begin{description*}
-	\item[CPU] \hfill \\
-		Intel Q9550 Quad Core 2.83GHz
-	\item[GPU] \hfill \\
-		ATI Radeon HD 5800
-	\item[OS] \hfill \\
-		Windows 8.0
+	\item[CPU]	Intel Q9550 Quad Core 2.83GHz
+	\item[GPU]	ATI Radeon HD 5800
+	\item[OS]	Windows 8.0
 \end{description*}
@@
 \end{center}
+
+% From these kernels, data entailing the execution time of said kernel may be retrieved - which will make out the main subject~of~study throughout this material.
+Additional data retrieved from the execution concerning the experiment make out precision deviations in resulting matrix \textit{C} compared to the expected result \textit{Ref}.\\
 
@@
 I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.
+\\
+\\
+The source code used during this study is freely available on \textit{GitHub}\footnote{\textit{GitHub}~Repository:~\url{http://bit.ly/1c4wd20}.}, along with a guide on how to compile and run the solution in order to replicate the experiment.
 
@@
 % Pseudocode, or source code, or DirectCompute-kernels
+\subsection*{Matrix~mult.~w.~Blocks}
+\begin{lstlisting}
+#ifndef DV2549_FXS_MULTFLOATBASIC_FX
+#define DV2549_FXS_MULTFLOATBASIC_FX
+
+#include <CommonFloat.fx>
+
+[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
+void main(
+	uint3 tIdx : SV_GroupThreadID,
+	uint3 bIdx : SV_GroupID ) {
+	const uint row = bIdx.y * BLOCK_SIZE + tIdx.y;
+	const uint col = bIdx.x * BLOCK_SIZE + tIdx.x;
+	if( row >= cRows || col >= cCols ) {
+		return;
+	}
+
+	float sum = 0;
+	for( uint i = 0; i < aRows; i++ ) {
+		uint idxA = row * aRows + i;
+		uint idxB = col + bRows * i;
+		sum += mA[ idxA ] * mB[ idxB ];
+	}
+	mC[ row * cRows + col ] = sum;
+}
+
+#endif // DV2549_FXS_MULTFLOATBASIC_FX
+\end{lstlisting}
+
+\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
+\begin{lstlisting}
+#ifndef DV2549_FXS_MULTFLOATTILE_H
+#define DV2549_FXS_MULTFLOATTILE_H
+
+#include <CommonFloat.fx>
+
+groupshared float mAs[ BLOCK_SIZE ][ BLOCK_SIZE ];
+groupshared float mBs[ BLOCK_SIZE ][ BLOCK_SIZE ];
+
+[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
+void main(
+	uint3 tIdx : SV_GroupThreadID,
+	uint3 bIdx : SV_GroupID ) {
+	const uint row = bIdx.y * BLOCK_SIZE + tIdx.y;
+	const uint col = bIdx.x * BLOCK_SIZE + tIdx.x;
+
+	float sum = 0;
+	const uint blocks = ceil( 
+		(float)aRows / (float)BLOCK_SIZE );
+	for( uint i = 0; i < blocks; i++ ) {
+		mAs[ tIdx.y ][ tIdx.x ] = mA[ 
+			row * aRows + ( i * BLOCK_SIZE + tIdx.x ) ];
+		mBs[ tIdx.y ][ tIdx.x ] = mB[ 
+			col + bRows * ( i * BLOCK_SIZE + tIdx.y ) ];
+		GroupMemoryBarrierWithGroupSync();
+
+		for( uint j = 0; j < BLOCK_SIZE; j++ ) {
+			sum += 
+				mAs[ tIdx.y ][ j ] * mBs[ j ][ tIdx.x ];
+		}
+		GroupMemoryBarrierWithGroupSync();
+	}
+	if( row >= cRows || col >= cCols ) {
+		return;
+	}
+	mC[ row * cRows + col ] = sum;
+}
+
+#endif // DV2549_FXS_MULTFLOATTILE_H
+
+\end{lstlisting}
 
 \bibliographystyle{IEEEtranS}
-\bibliography{doc}
+\bibliography{article}
 \end{document}

### 2013-10-20 article.tex
Added outline for gnuplot->tex.
Sucessfully scaled .tex-input.
Added avg. execution time summaries.

@@
 
+\usepackage{color}
 \usepackage{float}
@@
 \usepackage{verbatim}
+\usepackage{graphicx}
 \usepackage[T1]{fontenc}
@@
 \label{sec:contribution:results}
-Preliminary results indicate a surprisingly well-performing WARP, roughly only doubling the execution time in regards to the same kernel hardware accelerated.
+
+\begin{table}
+\begin{center}
+	\begin{tabular}{|l|l|l|}
+		\hline
+		\multicolumn{3}{|c|}{Int $200x200$} \\
+		\hline
+		~    & BASIC & TILE \\	\hline
+		HARD	& 1.16    	& 0.24   	 \\	\hline
+		SOFT	& 11610.02 	& 9866.40    	\\	\hline
+		WARP & 15.31     	& 18.97   	\\	\hline
+	\end{tabular}
+	\label{tab:contribution:results:summaryint}
+	\caption{Average exectution time (ms) of a integer matrix.}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+	\begin{tabular}{|l|l|l|}
+		\hline
+		\multicolumn{3}{|c|}{Float $200x200$} \\
+		\hline
+		~    & BASIC & TILE \\	\hline
+		HARD & 0.77     	& 0.22    		\\	\hline
+		SOFT & 10247.03     & 10909.88    	\\	\hline
+		WARP & 14.08     	& 17.44    		\\	\hline
+	\end{tabular}
+	\label{tab:contribution:results:summaryfloat}
+	\caption{Average exectution time (ms) of a floating point matrix.}
+\end{center}
+\end{table}
+
+%Summary
+
+\subsubsection{WARP}
+\label{sec:contribution:results:warp}
+The \textit{GPU}-accelerated implementation show a clear improvement when utilizing memory.\footnote{Bad visualization.} According to Microsoft...
+However, the execution time of WARP-acceleration demonstrate an increase in execution time...
+\begin{figure}[htb]
+\begin{center}
+	\resizebox{ \textwidth/2 }{!}{\input{msshard}}
+	\caption{Hardware~Accelerated execution time with floating point-precision for Basic- and Tiled implementation, with visualized mean and standard deviations.
+Values outside of their respective standard deviations have been clipped for the sake of clarity.}
+	\label{fig:contribution:results:warp:msshard}
+\end{center}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+	\resizebox{ \textwidth/2 }{!}{\input{msswarp}}
+	\caption{\textit{WARP} execution time with float-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
+Values outside of their respective standard deviations have been clipped for the sake of clarity.}
+	\label{fig:contribution:results:warp:msswarp}
+\end{center}
+\end{figure}
+
+\subsubsection{Computational~Precision}
+\label{sec:contribution:results:computationalprecision}
+\begin{table}
+\begin{center}
+	\begin{tabular}{|l|l|l|}
+		\hline
+		Minimum & Maximum & Standard \\ \hline
+		0.0     & ~0.01   & ~0.0025            \\ \hline
+	\end{tabular}
+\label{tab:contribution:results:computationalprecision:avgprecision}
+\caption {Average precisional deviations in floating point operations.}
+\end{center}
+\end{table}
+
+Integer had no loss of precision whatsoever.
+All floating point experiments experienced a minimum precisional deviation of 0, a maximum precisional deviation of ~0.01 and a standard precisional deviation of ~0.0025.
+Experiments indicated no increased performance loss in-between the different driver types.
+
+%Preliminary results indicate a surprisingly well-performing WARP, roughly only doubling the execution time in regards to the same kernel hardware accelerated.
 Each configuration has been has been run using the same integer-precision 200x200-matrix.
@@
 \\
-The results gathered during preliminary testing are presented below:
-\begin{center}
-	\begin{tabular}{| l | l | l | l |}
-	\hline
-	Acceleration & Min (ms) & Max (ms) & Average (ms)	\\ \hline
-	Hardware & 25.86  & 43.12  & 26.41			\\ \hline
-	Software & 16141.6 & 16906.7 & 16390.6		\\ \hline
-	WARP & 46.18 & 64.25 & 48.47				\\
-	\hline
-	\end{tabular}
-\end{center}
+%The results gathered during preliminary testing are presented below:
+%\begin{center}
+%	\begin{tabular}{| l | l | l | l |}
+%	\hline
+%	Acceleration & Min (ms) & Max (ms) & Average (ms)	\\ \hline
+%	Hardware & 25.86  & 43.12  & 26.41			\\ \hline
+%	Software & 16141.6 & 16906.7 & 16390.6		\\ \hline
+%	WARP & 46.18 & 64.25 & 48.47				\\
+%	\hline
+%	\end{tabular}
+%\end{center}
 
@@
 \end{document}
-
-% To-be-inserted references and/or footnotes:
-% Microsoft Warp: http://msdn.microsoft.com/en-us/library/windows/desktop/gg615082%28v=vs.85%29.aspx

### 2013-10-21 article.tex
Formatting of said tables.
Table formatting.

@@
 \usepackage{graphicx}
+\usepackage{multirow}
 \usepackage[T1]{fontenc}
@@
 
+\subsection{Process~of~Study}
+\label{sec:contribution:processofstudy}
+For the purpose of this study,
+
 \subsubsection{Equipment}
@@
 
-\begin{table}
+\begin{table}[h]
 \begin{center}
-	\begin{tabular}{|l|l|l|}
-		\hline
-		\multicolumn{3}{|c|}{Int $200x200$} \\
-		\hline
-		~    & BASIC & TILE \\	\hline
-		HARD	& 1.16    	& 0.24   	 \\	\hline
-		SOFT	& 11610.02 	& 9866.40    	\\	\hline
-		WARP & 15.31     	& 18.97   	\\	\hline
+\begin{tabular}{r|r|r|r|}
+	\cline{2-3}
+							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}	\\ \hline
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$    				\\ \hline
+	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$     				\\ \hline
+	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$     				\\ \hline
 \end{tabular}
 \label{tab:contribution:results:summaryint}
-	\caption{Average exectution time (ms) of a integer matrix.}
+\caption{Average exectution time (ms) of a $200x200$ integer matrix.}
 \end{center}
@@
 
-\begin{table}
+\begin{table}[h]
 \begin{center}
-	\begin{tabular}{|l|l|l|}
-		\hline
-		\multicolumn{3}{|c|}{Float $200x200$} \\
-		\hline
-		~    & BASIC & TILE \\	\hline
-		HARD & 0.77     	& 0.22    		\\	\hline
-		SOFT & 10247.03     & 10909.88    	\\	\hline
-		WARP & 14.08     	& 17.44    		\\	\hline
+\begin{tabular}{r|r|r|r|}
+	\cline{2-3}
+							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}		\\ \hline
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$    				\\ \hline
+	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$     				\\ \hline
+	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$    				\\ \hline
 \end{tabular}
 \label{tab:contribution:results:summaryfloat}
-	\caption{Average exectution time (ms) of a floating point matrix.}
+\caption{Average exectution time (ms) of a $200x200$ floating point matrix.}
 \end{center}
@@
 \label{sec:contribution:results:warp}
+%In both int- and float-cases, warp performs worse with memory tiling, whereas ref-device is less impaired or even performs better. why?
 The \textit{GPU}-accelerated implementation show a clear improvement when utilizing memory.\footnote{Bad visualization.} According to Microsoft...
@@
 \begin{center}
-	\resizebox{ \textwidth/2 }{!}{\input{msshard}}
+	\resizebox{ \columnwidth }{!}{\input{msshard}}
 	\caption{Hardware~Accelerated execution time with floating point-precision for Basic- and Tiled implementation, with visualized mean and standard deviations.
@@
 \begin{center}
-	\resizebox{ \textwidth/2 }{!}{\input{msswarp}}
+	\resizebox{ \columnwidth }{!}{\input{msswarp}}
 	\caption{\textit{WARP} execution time with float-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.

### 2013-10-21 article.tex
Expanded section on WARP. Added footnote references.

@@
 \usepackage{multirow}
+\usepackage{footmisc}
 \usepackage[T1]{fontenc}
@@
 \\
-Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{See Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}}.
+Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{\label{lab:warpguide}Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}.
+Retrieved: 21-10-2013.}.
 \\
@@
 The \textit{GPU}-kernels described in Section~\ref{sec:contribution:method} are comprised of \textit{HLSL}-syntax and are compiled \& executed using Microsoft~\textit{DirectCompute}.
-These kernels are run using three types of hardware~acceleration with varying strategies of \textit{GPU}-kernel emulation.
+These kernels are run using three types of acceleration~technologies with varying strategies of \textit{GPU}-kernel emulation.
 These are comprised of the following:
 \paragraph{Hardware-Acceleration~(GPU)}
-	The execution of a \textit{DirectCompute}-kernel on a graphics card. Thus, this case will act as a reference for the emulated subjects.\\
-	Expected high performance.
+	The execution of a \textit{DirectCompute}-kernel on a graphics card.
+This is the common case, and involves no emulation of the kernel.
+Thus, this case will act as a reference for the emulated subjects.\\
+	During hardware~acceleration on the \textit{GPU}, one may expect high performance.
 \paragraph{Software~Rasterization~(CPU)}
 	The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX}~Reference~Device~Driver.\\
-	Expected poor performance.
+The Device~Driver was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications\footnote{\label{lab:drivertypes}Microsoft's reference on \textit{DirectX}~Driver~Types: \url{http://bit.ly/1b63NiX}.
+Retrieved: 21-10-2013.}.\\
+	As the Reference~Driver is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
 \paragraph{Windows~Advanced~Rasterization~Platform~(CPU)}
 	The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.\\
-	Expectations unclear, but expected to perform better than standard software rasterization.\footnote{Insert reference to microsoft warp-msdn-page and explain what WARP promises and stuff about optimization for gpus.}\\
+	The driver is based off the \textit{DirectX}~Reference~Driver and uses thread pooling to distribute tasks effectively on the \textit{CPU}, along with grouping execution in batches for optimum performance.
+Microsoft describes \textit{WARP} as a high-performance software~rasterizer, and recommends using the driver for retail applications, such as 'casual~games' or 'advanced rendering games'.
+For more information surrounding the \textit{WARP}-driver, see Microsoft's \textit{WARP~Guide}\footref{lab:warpguide}.\\
+As there are, as of yet, few studies performed on Microsoft~\textit{WARP} expectations are unclear, but expected to perform better than standard software rasterization.\\
+% May one encounter computational precision issues with WARP?
 
@@
 These kernels are presented below.
-\paragraph{Matrix~mult.~w.~Blocks}
+\paragraph{Matrix~mult.~w.~Thread~Blocks}
 	A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.\\
@@
 	Execution is performed in blocks of $16x16$ threads, as this number was found to be the block dimension performing optimally whilst hardware~accelerated on the \textit{GPU}\footnote{Make sure of this!}.
-\paragraph{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
+\paragraph{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
 	Likewize as with the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory}\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-	This kernel is presented as a test-case due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}.
+	This kernel is presented as a test-case due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{lab:warpguide}.
 Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
@@
 This script, written in \textit{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
-More information surrounding how to run these programs can be found via the source repository (see Acknowledgments).
+\\
+The source code manufactured for the sake of this study is freely available via \textit{GitHub}\footnote{\label{lab:github}\textit{GitHub}~Repository:~\url{http://bit.ly/1c4wd20}.
+Retrieved: 21-10-2013.}, along with a guide on how to compile and run the solution in order to replicate the experiment.
+Furthermore, the results collected and used throughout this study is also available for download, and may be acquired for further analysis.
 
@@
 \end{description*}
+The study has been performed on this system as Microsoft claims that the \textit{WARP}~driver performs best on modern quad-core \textit{CPU}s\footref{lab:warpguide}.
 
@@
 \label{tab:contribution:results:summaryint}
-\caption{Average exectution time (ms) of a $200x200$ integer matrix.}
+\caption{Average exectution time in milliseconds of a $200x200$ integer matrix.}
 \end{center}
@@
 \label{tab:contribution:results:summaryfloat}
-\caption{Average exectution time (ms) of a $200x200$ floating point matrix.}
+\caption{Average exectution time in milliseconds of a $200x200$ floating point matrix.}
 \end{center}
@@
 \begin{center}
-	\begin{tabular}{|l|l|l|}
+	\begin{tabular}{|r|r|r|}
 		\hline
-		Minimum & Maximum & Standard \\ \hline
+		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
 		0.0     			& ~0.01   			& ~0.0025            		\\ \hline
@@
 
+%http://msdn.microsoft.com/en-us/library/windows/desktop/cc308050%28v=vs.85%29.aspx
 Integer had no loss of precision whatsoever.
@@
 I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.
-\\
-\\
-The source code used during this study is freely available on \textit{GitHub}\footnote{\textit{GitHub}~Repository:~\url{http://bit.ly/1c4wd20}.}, along with a guide on how to compile and run the solution in order to replicate the experiment.
 

### 2013-10-21 article.tex
Added Process of Study-headline.

@@
 \\
-Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation in exchange for some computational precision\footnote{\label{lab:warpguide}Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}.
+Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation\footnote{\label{lab:warpguide}Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}.
 Retrieved: 21-10-2013.}.
 \\
+%...in exchange for some computational precision. Not Supported by cited source. From where did I get that idea?
 %	Vilka resultat gav studien?
@@
 	Execution is performed in blocks of $16x16$ threads, as this number was found to be the block dimension performing optimally whilst hardware~accelerated on the \textit{GPU}\footnote{Make sure of this!}.
+\\
+	This kernel will be referred to as the Basic~Kernel throughout this material.
 \paragraph{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
@@
 Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
+	This kernel will be referred to as the Tiled~Kernel throughout this material.\\
 
@@
 
-\subsection{Process~of~Study}
-\label{sec:contribution:processofstudy}
-For the purpose of this study,
-
 \subsubsection{Equipment}
@@
 \end{description*}
-The study has been performed on this system as Microsoft claims that the \textit{WARP}~driver performs best on modern quad-core \textit{CPU}s\footref{lab:warpguide}.
+This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP}~driver performs best on modern quad-core \textit{CPU}s\footref{lab:warpguide}.
+
+\subsection{Process~of~Study}
+\label{sec:contribution:processofstudy}
+For the purpose of this study, the Object~of~Study - being a $200x200$ matrices - were randomized with numbers in-between zero and ten.
+The product matrix of these matrices was then computed 100 times for each configuration.
+In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel.
+For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization.) was garnered along with precision-wize deviational data.\\
+The process described above was then repeated for Integer- and Floating~Point-precision.\\
+
+\noindent
+The measurements gathered from these executions make out the results presented in this study.
 
@@
 	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}	\\ \hline
+							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
 	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$    				\\ \hline
@@
 	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}		\\ \hline
+							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}		\\ \hline
 	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$    				\\ \hline

### 2013-10-21 article.tex
Added results-summary and removed bad visualization of Hardware Accelerated kernels.

@@
 As such, the hypothesis suggested in this proposal may be summarized as follows:
-\quote{\textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}}
+%\quote{\textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}}
+%^ Not a valid hypothesis. No sources indicate that WARP has lesser precision.
 % Background	(what)
@@
 \label{sec:contribution:results}
+Based off the average of the collected execution times described in Section~\ref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, when compared to the performance of the \textit{DirectX}~Reference~Device from which \textit{WARP} is derived.\\
+Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated subject when utilizing shared~memory amongst blocks; with varying results for the other subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
 
-\begin{table}[h]
+\begin{table}[hbt]
 \begin{center}
@@
 \end{tabular}
+\end{center}
 \label{tab:contribution:results:summaryint}
-\caption{Average exectution time in milliseconds of a $200x200$ integer matrix.}
-\end{center}
+\caption{Average execution time in milliseconds of a $200x200$ integer matrix.}
 \end{table}
 
-\begin{table}[h]
+\begin{table}[hbt]
 \begin{center}
@@
 \end{tabular}
+\end{center}
 \label{tab:contribution:results:summaryfloat}
-\caption{Average exectution time in milliseconds of a $200x200$ floating point matrix.}
-\end{center}
+\caption{Average execution time in milliseconds of a $200x200$ floating point matrix.}
 \end{table}
 
-%Summary
-
-\subsubsection{WARP}
-\label{sec:contribution:results:warp}
-%In both int- and float-cases, warp performs worse with memory tiling, whereas ref-device is less impaired or even performs better. why?
-The \textit{GPU}-accelerated implementation show a clear improvement when utilizing memory.\footnote{Bad visualization.} According to Microsoft...
-However, the execution time of WARP-acceleration demonstrate an increase in execution time...
-\begin{figure}[htb]
-\begin{center}
-	\resizebox{ \columnwidth }{!}{\input{msshard}}
-	\caption{Hardware~Accelerated execution time with floating point-precision for Basic- and Tiled implementation, with visualized mean and standard deviations.
-Values outside of their respective standard deviations have been clipped for the sake of clarity.}
-	\label{fig:contribution:results:warp:msshard}
-\end{center}
-\end{figure}
+\noindent
+Using both integer- and floating~point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared~memory according to the data presented in Table \ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.\\
+In Microsoft's guide on \textit{WARP}\footref{lab:warpguide}, the author claims that an application, if tuned to run efficiently on hardware, will run efficiently on \textit{WARP} - and vice versa.
+However, the data collected for this study rather indicates an increase in execution time of $23.9\%$ independant of precision, even though the same kernel accelerates the hardware~accelerated subject by roughly $70\%$.
+The floating~point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
 

### 2013-10-21 article.tex
Wrote draft result-section.

@@
 \subsubsection{Computational~Precision}
+Integer~precision calculation showed no sign of loss of precision whatsoever.
+Meanwhile, all floating~point-experiments experienced an equal average loss of computational precision.
+However, the data collected indicates no divergence in the precisional loss of respective subject.
+The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\ref{sec:contribution:method}, are presented in Table~\ref{tab:contribution:results:computationalprecision:avgprecision}.
+See Microsoft's documentation on Floating-point Rules\footnote{Microsoft's reference on Floating-Point~Rules:~\url{http://bit.ly/1bOQnZu}.
+Retrieved 21-10-2013.} for more information surrounding floating~point-precision in the \textit{Direct3D}-framework.
 \label{sec:contribution:results:computationalprecision}
-\begin{table}
+\begin{table}[hbt]
 \begin{center}
@@
 \label{tab:contribution:results:computationalprecision:avgprecision}
-\caption {Average precisional deviations in floating point operations.}
+\caption {Average precisional deviations in floating~point-operations.}
 \end{center}
@@
 %http://msdn.microsoft.com/en-us/library/windows/desktop/cc308050%28v=vs.85%29.aspx
-Integer had no loss of precision whatsoever.
-All floating point experiments experienced a minimum precisional deviation of 0, a maximum precisional deviation of ~0.01 and a standard precisional deviation of ~0.0025.
-Experiments indicated no increased performance loss in-between the different driver types.
 

### 2013-10-21 article.tex
Added draft of conclusion-section. Found great article by the people behind PMPP.

@@
 As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.
+\\
+%The remainder of this document presents the method of 
 %	Vilket upplägg har resterande delar av matrialet?
@@
 \label{sec:contribution:kernels}
-In addition to the subject drivers mentioned in Section~\ref{sec:contribution:subjectofstudy}, two kernels with varying lavel of optimization have been examined\footnote{Why?}.
-These kernels are presented below.
+In addition to the subject drivers mentioned in Section~\ref{sec:contribution:subjectofstudy}, two kernels with varying lavel of optimization have been examined. These kernels are presented below.
 \paragraph{Matrix~mult.~w.~Thread~Blocks}
@@
 \paragraph{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-	Likewize as with the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory}\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-	This kernel is presented as a test-case due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{lab:warpguide}.
+	Similar to the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory} in accordance to the implementation by Kirk and Hwu\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
+		Stratton et al.\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of \textit{local}- and \textit{shared}-memory approximately corresponding to a core's \textit{L1}-cache.
+Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{lab:warpguide}.
 Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
@@
 
-\subsubsection{Computational~Precision}
+\noindent
 Integer~precision calculation showed no sign of loss of precision whatsoever.
@@
 However, the data collected indicates no divergence in the precisional loss of respective subject.
-The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\ref{sec:contribution:method}, are presented in Table~\ref{tab:contribution:results:computationalprecision:avgprecision}.
+The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\ref{sec:contribution:method}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
 See Microsoft's documentation on Floating-point Rules\footnote{Microsoft's reference on Floating-Point~Rules:~\url{http://bit.ly/1bOQnZu}.
@@
 	\end{tabular}
-\label{tab:contribution:results:computationalprecision:avgprecision}
+\label{tab:contribution:results:avgprecision}
 \caption {Average precisional deviations in floating~point-operations.}
@@
 \end{table}
-
-%http://msdn.microsoft.com/en-us/library/windows/desktop/cc308050%28v=vs.85%29.aspx
-
-%Preliminary results indicate a surprisingly well-performing WARP, roughly only doubling the execution time in regards to the same kernel hardware accelerated.
-Each configuration has been has been run using the same integer-precision 200x200-matrix.
-To gather the results presented below, each scenario has been run 100 times each.
-Please observe that these are preliminary tests, and more data is to be gathered before the closing of this article.
-\\
-%The results gathered during preliminary testing are presented below:
-%\begin{center}
-%	\begin{tabular}{| l | l | l | l |}
-%	\hline
-%	Acceleration & Min (ms) & Max (ms) & Average (ms)	\\ \hline
-%	Hardware & 25.86  & 43.12  & 26.41			\\ \hline
-%	Software & 16141.6 & 16906.7 & 16390.6		\\ \hline
-%	WARP & 46.18 & 64.25 & 48.47				\\
-%	\hline
-%	\end{tabular}
-%\end{center}
-
-% From these kernels, data entailing the execution time of said kernel may be retrieved - which will make out the main subject~of~study throughout this material.
-Additional data retrieved from the execution concerning the experiment make out precision deviations in resulting matrix \textit{C} compared to the expected result \textit{Ref}.\\
 
@@
 \label{sec:conclusion}
-Conclusion left out in regards to further development and analysis.
+Based off the results presented in Section~\ref{sec:contribution:results}, it would appear as if Microsoft~\textit{WARP} is an impressive driver in comparison to the \textit{DirectX}~Reference~Device, from which it has been derived.
+Using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device in the same manner.
+If one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior for the purposes presented in this document.
+However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
+The \textit{DirectX}~Reference~Device is primarily proposed by Microsoft as a debugging/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{lab:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
+\\
+In regards to the decreased performance of \textit{WARP}-accelerated kernels when utilizing shared memory; it is probable that... \\
+\\
+In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
+
+% Speculate surrounding the hypothesis.
+% The effect shared memory has on WARP.
+
 % Summary
@@
 %	Vilka tvetydliga aspekter av studien kräver diskussion?
-% Answer and Oppertunity
-%	Vilka fortsatta studier föreslår rapportens författare?
 
@@
 \label{sec:conclusion:futurework}
-% Investigate double precision as to establish probable precision loss in terms of Microsoft WARP.
+The author suggests elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the subjects detailed in Section~\ref{sec:contribution:subjectofstudy} may have differentiating effects on computational precision.
+
+% Answer and Oppertunity
+%	Vilka fortsatta studier föreslår rapportens författare?
 
@@
 \label{sec:acknowledgments}
-I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.
+%I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.
 
@@
 \label{sec:appendix}
-% Pseudocode, or source code, or DirectCompute-kernels
 \subsection*{Matrix~mult.~w.~Blocks}

### 2013-10-22 article.tex
Made sections up until Conclusion less drafty.

@@
 %	Vilka utmaningar omfattar studien?
-When developing \textit{GPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
+When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-
 between on-chip hardware.
-Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-
-technologies.\\
+The increased utilization of complex \textit{GPGPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
+Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
 % Approach and Result
 %	Vilken ansats tillämpas i studien?
-The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from the hardware - possibly due to architectural differences in-between chip manufacturers.
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for substantial performance-losses.
-Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable.
+A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU}, such as described by Kerr et al.\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework\footnote{\label{ftn:ocelot}\textit{GPU}~Ocelot: \url{http://b.gatech.edu/1a489L1}.
+Retrieved 22-10-2013.}, often in exchange for substantial performance-losses.
+Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable\footnote{\label{ftn:warpguide}Microsoft's reference on \textit{WARP}: \url{http://bit.ly/19hiwrZ}.
+Retrieved: 21-10-2013.}.
 This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
 \\
-Furthermore, this study concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation\footnote{\label{lab:warpguide}Microsoft's \textit{WARP~Guide}: \url{http://bit.ly/19hiwrZ}.
-Retrieved: 21-10-2013.}.
+Furthermore, this material concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}\footnote{\textit{Windows~Advanced~Rasterization~Platform}.}-technology - which promises high-speed software emulation\footref{ftn:warpguide}.
+\\
 \\
@@
 %	Vilka resultat gav studien?
-%\\
-%This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity.
-As such, Microsoft~\textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft.
-Link to Microsofts page on WARP here!}.\\
+This article concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered feasable for computational use in real-time, as originally proposed by Microsoft\footref{ftn:warpguide}.
+Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics~hardware is unavailable, not sufficient, or busy.\\
 \\
@@
 \\
-%The remainder of this document presents the method of 
+The remainder of this document presents the method and process to acquire the data used,  the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future~work in the area along with propositions of further study.
 %	Vilket upplägg har resterande delar av matrialet?
@@
 \label{sec:contribution:objectofstudy}
-Considering possible precision loss caused by \textit{WARP}, it is important that the object~of~study is measurable and deterministic.
-For the purpose of this experiment, the data computed corresponds to a square matrix~multiplication of dimension $200x200$\footnote{Why 200x200?}.
-The result of such an operation can easily be verified as correct, and potential losses in computational precision may be computed from the expected data-type.
-This operation was therefore considered suitable for the purpose of the experiment.\\
-Throughout this material, the compiled data will thusly be referred to as $AB=C$.
+Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
+For the purpose of this study, the data computed corresponds to a square matrix~multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu\cite[ch.~3]{Kirk:2010:PMP:1841511}.
+Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
+This operation was therefore considered suitable for the purpose of this experiment.\\
+\\
+For the Object~of~Study, the dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware~accelerated reference case.
+\\
+Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object~of~Study for the purpose of this experiment.
 
@@
 \label{sec:contribution:method}
-In order to establish the object~of~study $AB=C$, the experiment utilizes \textit{GPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
-The experiment is devised of the following approximate steps in order to compile the object~of~study $AB=C$:
+In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
+The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
 \begin{enumerate*}
@@
 	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix $C$ and the previously established matrix $Ref$.
+	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
 \end{enumerate*}
+The process described above make out the method of this study.
 
 \subsection{Subjects~of~Study}
-\label{sec:contribution:subjectofstudy}
+\label{sec:contribution:Subjectofstudy}
 % Describe these modes and what they entail:
@@
 This is the common case, and involves no emulation of the kernel.
-Thus, this case will act as a reference for the emulated subjects.\\
+Thus, this case will act as a reference for the emulated Subjects.\\
 	During hardware~acceleration on the \textit{GPU}, one may expect high performance.
@@
 	The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX}~Reference~Device~Driver.\\
-The Device~Driver was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications\footnote{\label{lab:drivertypes}Microsoft's reference on \textit{DirectX}~Driver~Types: \url{http://bit.ly/1b63NiX}.
+The Reference~Driver was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications\footnote{\label{ftn:drivertypes}Microsoft's reference on \textit{DirectX}~Driver~Types: \url{http://bit.ly/1b63NiX}.
 Retrieved: 21-10-2013.}.\\
@@
 	The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.\\
-	The driver is based off the \textit{DirectX}~Reference~Driver and uses thread pooling to distribute tasks effectively on the \textit{CPU}, along with grouping execution in batches for optimum performance.
-Microsoft describes \textit{WARP} as a high-performance software~rasterizer, and recommends using the driver for retail applications, such as 'casual~games' or 'advanced rendering games'.
-For more information surrounding the \textit{WARP}-driver, see Microsoft's \textit{WARP~Guide}\footref{lab:warpguide}.\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP} expectations are unclear, but expected to perform better than standard software rasterization.\\
+	The driver is based off the \textit{DirectX}~Reference~Driver and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance.
+Microsoft describes \textit{WARP} as a high-performance software~rasterizer, and recommends using the driver for retail applications, such as casual~games\footref{ftn:warpguide}.\\
+As there are, as of yet, few studies performed on Microsoft~\textit{WARP} expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
 % May one encounter computational precision issues with WARP?
@@
 \noindent
-These three \textit{DirectX} driver-types make out the subjects of this study.
+These three \textit{DirectX} driver-types make out the Subjects of this study.
 
@@
 \label{sec:contribution:kernels}
-In addition to the subject drivers mentioned in Section~\ref{sec:contribution:subjectofstudy}, two kernels with varying lavel of optimization have been examined. These kernels are presented below.
+In addition to the Subject drivers mentioned in Section~\ref{sec:contribution:Subjectofstudy}, two kernels with varying lavel of optimization have been examined.
+These kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.\\
+The kernels are presented below.
 \paragraph{Matrix~mult.~w.~Thread~Blocks}
 	A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.\\
-	The kernel is executed with one thread for each element in the square matrices, and likewize produce a lone element of the resulting matrix thread-wize.\\
+	The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.\\
 	Execution is performed in blocks of $16x16$ threads, as this number was found to be the block dimension performing optimally whilst hardware~accelerated on the \textit{GPU}\footnote{Make sure of this!}.
@@
 \paragraph{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-	Similar to the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory} in accordance to the implementation by Kirk and Hwu\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
+	Similar to the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory} in accordance to the implementation by Kirk~\&~Hwu\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
 		Stratton et al.\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of \textit{local}- and \textit{shared}-memory approximately corresponding to a core's \textit{L1}-cache.
-Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{lab:warpguide}.
+Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{ftn:warpguide}.
 Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
@@
 % CONTRIBUTION - TECHNOLOGIES
-\subsection{Technologies}
-\label{sec:contribution:technologies}
-\subsubsection{Tools}
-\label{sec:contribution:technologies}
+\subsection{Tools}
+\label{sec:contribution:tools}
 The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
@@
 Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from \textit{DirectCompute}.
+Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from \textit{DirectCompute} described in the next paragraph.
 \\
@@
 \paragraph{experiment}
-Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from the matrices generated by \textit{matrixgen}.
+Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from the matrices $A$~\&~$B$ generated by \textit{matrixgen}.
 The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
-\textit{experiment} is written in \texttt{C++} with its respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.\\
-As \textit{experiment} is developed using the \textit{Windows~8~SDK}, \textit{Windows~8.0} is required.
+\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.\\
+As \textit{experiment} is developed using the \textit{Windows~8~SDK}, \textit{Windows~8.0} or later is required.
 Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
@@
 \paragraph{analytics}
-\textit{analytics} is a smaller utility developed to compose data surrounding possible precisional deviations in-between matrices $C$ and $Ref$.
+\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C$~\&~$Ref$.
 \textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
@@
 \\
-The source code manufactured for the sake of this study is freely available via \textit{GitHub}\footnote{\label{lab:github}\textit{GitHub}~Repository:~\url{http://bit.ly/1c4wd20}.
+The source code manufactured for the sake of this study is freely available via \textit{GitHub}\footnote{\label{ftn:github}\textit{GitHub}~Repository:~\url{http://bit.ly/1c4wd20}.
 Retrieved: 21-10-2013.}, along with a guide on how to compile and run the solution in order to replicate the experiment.
@@
 
-\subsubsection{Equipment}
+\subsection{Equipment}
 \label{sec:contribution:equipment}
@@
 \end{description*}
-This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP}~driver performs best on modern quad-core \textit{CPU}s\footref{lab:warpguide}.
+This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP}~driver performs best on modern quad-core \textit{CPU}s\footref{ftn:warpguide}.
 
@@
 \label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study - being a $200x200$ matrices - were randomized with numbers in-between zero and ten.
+For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten.
 The product matrix of these matrices was then computed 100 times for each configuration.
@@
 \label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\ref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, when compared to the performance of the \textit{DirectX}~Reference~Device from which \textit{WARP} is derived.\\
-Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated subject when utilizing shared~memory amongst blocks; with varying results for the other subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
+Based off the average of the collected execution times described in Section~\ref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~Reference~Device from which \textit{WARP} is derived.\\
+Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing \textit{shared~memory} amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
 
@@
 \end{center}
+\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
 \label{tab:contribution:results:summaryint}
-\caption{Average execution time in milliseconds of a $200x200$ integer matrix.}
 \end{table}
@@
 \end{center}
+\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
 \label{tab:contribution:results:summaryfloat}
-\caption{Average execution time in milliseconds of a $200x200$ floating point matrix.}
 \end{table}
@@
 \noindent
-Using both integer- and floating~point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared~memory according to the data presented in Table \ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.\\
-In Microsoft's guide on \textit{WARP}\footref{lab:warpguide}, the author claims that an application, if tuned to run efficiently on hardware, will run efficiently on \textit{WARP} - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9\%$ independant of precision, even though the same kernel accelerates the hardware~accelerated subject by roughly $70\%$.
+Using both integer- and floating~point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing \textit{shared~memory} according to the data presented in Tables \ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.\\
+In Microsoft's guide on \textit{WARP}\footref{ftn:warpguide}, the author claims that an application, if tuned to run efficiently on hardware, will run efficiently on \textit{WARP} - and vice versa.
+However, the data collected for this study rather indicates an increase in execution time of $23.9\%$ independant of precision, even though the same kernel accelerates the hardware~accelerated Subject by roughly $70\%$.
 The floating~point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
@@
 Meanwhile, all floating~point-experiments experienced an equal average loss of computational precision.
-However, the data collected indicates no divergence in the precisional loss of respective subject.
+However, the data collected indicates no divergence in the precisional loss of respective Subject.
 The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\ref{sec:contribution:method}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
-See Microsoft's documentation on Floating-point Rules\footnote{Microsoft's reference on Floating-Point~Rules:~\url{http://bit.ly/1bOQnZu}.
-Retrieved 21-10-2013.} for more information surrounding floating~point-precision in the \textit{Direct3D}-framework.
 \label{sec:contribution:results:computationalprecision}
@@
 	\end{tabular}
+\caption {Average precisional deviations in floating~point-operations for all Subjects.}
 \label{tab:contribution:results:avgprecision}
-\caption {Average precisional deviations in floating~point-operations.}
 \end{center}
 \end{table}
+
+\noindent
+These results were expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}-~and~\textit{10.1}-specification\footref{ftn:warpguide}.
+See Microsoft's documentation on Floating-point Rules\footnote{Microsoft's reference on Floating-Point~Rules:~\url{http://bit.ly/1bOQnZu}.
+Retrieved 21-10-2013.} for more information surrounding floating~point-precision in the \textit{Direct3D}-framework.
 
@@
 Using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device in the same manner.
-If one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior for the purposes presented in this document.
+If one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior for the purposes presented in this document.\\
 However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~Reference~Device is primarily proposed by Microsoft as a debugging/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{lab:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
+The \textit{DirectX}~Reference~Device is primarily proposed by Microsoft as a debugging/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{ftn:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
 \\
@@
 \label{sec:conclusion:futurework}
-The author suggests elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the subjects detailed in Section~\ref{sec:contribution:subjectofstudy} may have differentiating effects on computational precision.
+For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\ref{sec:contribution:Subjectofstudy} may have differentiating effects on computational precision.
 

### 2013-10-22 article.tex
Made entire solution less drafty.

@@
 When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-
-between on-chip hardware.
+between on-chip hardware\footnote{See Performance~Considerations by Kirk~\&~Hwu\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analyis on the volatility of \textit{GPGPU}-performance.}.
 The increased utilization of complex \textit{GPGPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
@@
 %	Vilken ansats tillämpas i studien?
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU}, such as described by Kerr et al.\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework\footnote{\label{ftn:ocelot}\textit{GPU}~Ocelot: \url{http://b.gatech.edu/1a489L1}.
+A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU}\footnote{\label{ftn:drivertypes}Microsoft's reference on \textit{DirectX}~Driver~Types: \url{http://bit.ly/1b63NiX}.
+Retrieved: 21-10-2013.}, such as described by Kerr et al.\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework\footnote{\label{ftn:ocelot}\textit{GPU}~Ocelot: \url{http://b.gatech.edu/1a489L1}.
 Retrieved 22-10-2013.}, often in exchange for substantial performance-losses.
@@
 	The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX}~Reference~Device~Driver.\\
-The Reference~Driver was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications\footnote{\label{ftn:drivertypes}Microsoft's reference on \textit{DirectX}~Driver~Types: \url{http://bit.ly/1b63NiX}.
-Retrieved: 21-10-2013.}.\\
+The Reference~Driver was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications\footref{ftn:drivertypes}.\\
 	As the Reference~Driver is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
@@
 \label{sec:conclusion}
-Based off the results presented in Section~\ref{sec:contribution:results}, it would appear as if Microsoft~\textit{WARP} is an impressive driver in comparison to the \textit{DirectX}~Reference~Device, from which it has been derived.
-Using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device in the same manner.
-If one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior for the purposes presented in this document.\\
+Based off the results presented in Section~\ref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device in the same manner.
+Hence, if one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
 However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
 The \textit{DirectX}~Reference~Device is primarily proposed by Microsoft as a debugging/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{ftn:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
-\\
-In regards to the decreased performance of \textit{WARP}-accelerated kernels when utilizing shared memory; it is probable that... \\
+This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\
 \\
 In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
+
+%In regards to the decreased performance of \textit{WARP}-accelerated kernels when utilizing shared memory; it is probable that...
 
@@
 \label{sec:conclusion:futurework}
-For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\ref{sec:contribution:Subjectofstudy} may have differentiating effects on computational precision.
+For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\ref{sec:contribution:Subjectofstudy} may have differentiating effects on computational precision.\\
+\\
+Additionally, the use of more complex kernels  in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.
 
@@
 % ACKNOWLEDGMENTS
-\section*{Acknowledgments} % The \section*{} command stops section numbering
-\addcontentsline{toc}{section}{\hspace*{-\tocsep}Acknowledgments} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
-\label{sec:acknowledgments}
+%\section*{Acknowledgments} % The \section*{} command stops section numbering
+%\addcontentsline{toc}{section}{\hspace*{-\tocsep}Acknowledgments} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
+%\label{sec:acknowledgments}
 %I wish to express my gratitude to my fellow students, colleagues and close friends Bob, Benny and no-one for their work, co-operation and positive attitude throughout the execution of this experiment.

### 2013-10-22 article.tex
Added draft for abstract.

@@
 \Abstract{
-\ldots \\
+Emulation of \textit{GPU}-kernels on the \textit{CPU} is common for the purposes of debugging or profiling, but also in situations where hardware implementations are unavailable, such as server-side applications.
+When performing such emulation, one may experience severe performance loss due to the architectural differences in-between the two target platforms.
+This study examines the performance of such emulated kernels, by analyzing three driver types from the \textit{DirectX}-framework using \textit{DirectCompute}, amongst which is the high speed software~rasterizer Microsoft~\textit{WARP}.\\
+This study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies such as Microsoft~\textit{WARP} to the degree that such emulation can be considered viable for use in retail applications.\\
 As such, the hypothesis suggested in this proposal may be summarized as follows:
-%\quote{\textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}}
+\quote{WARP is fast.}
+% \textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}
 %^ Not a valid hypothesis. No sources indicate that WARP has lesser precision.
@@
 \end{document}
+
+%\begin{table}[h]
+%\begin{center}
+%\begin{tabular}{l|r|r|}
+%\cline{2-3}
+%\multicolumn{1}{c}{\textit{INT}}    & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+%\multicolumn{1}{|l|}{\textbf{HARD}} &                                      &                                      \\ \hline
+%\multicolumn{1}{|l|}{\textbf{SOFT}} &                                      &                                      \\ \hline
+%\multicolumn{3}{l}{}                                                                                              \\ \cline{2-3} 
+%\multicolumn{1}{c}{\textit{FLOAT}}  & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+%\multicolumn{1}{|l|}{\textbf{HARD}} &                                      &                                      \\ \hline
+%\multicolumn{1}{|l|}{\textbf{SOFT}} &                                      &                                      \\ \hline
+%\end{tabular}
+%\end{center}
+%\caption{-}
+%\label{tab:conclusion:perc}
+%\end{table}

### 2013-10-22 article.tex
Second draft finished.

@@
 \Abstract{
-Emulation of \textit{GPU}-kernels on the \textit{CPU} is common for the purposes of debugging or profiling, but also in situations where hardware implementations are unavailable, such as server-side applications.
+Emulation of \textit{GPU}-kernels on the \textit{CPU} is common for the purposes of debugging or profiling, but also in situations where hardware implementations are unavailable, such as server-side applications\footref{ftn:warpguide}.
 When performing such emulation, one may experience severe performance loss due to the architectural differences in-between the two target platforms.
-This study examines the performance of such emulated kernels, by analyzing three driver types from the \textit{DirectX}-framework using \textit{DirectCompute}, amongst which is the high speed software~rasterizer Microsoft~\textit{WARP}.\\
-This study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies such as Microsoft~\textit{WARP} to the degree that such emulation can be considered viable for use in retail applications.\\
-As such, the hypothesis suggested in this proposal may be summarized as follows:
-\quote{WARP is fast.}
+This study examines the performance of such emulated kernels, by analyzing three driver types from the \textit{DirectX}-framework using \textit{DirectCompute}, amongst which is the high speed software~rasterizer Microsoft~\textit{WARP}.
+The performance of \textit{WARP} is compared to that of traditional \textit{GPU}~hardware acceleration and the standard driver for software~rasterization - the Reference~Device~Driver.\\
+Results demonstrate a major performance boost when compared to that of software~rasterization using the Reference~Device~Driver.
+Thus, this study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies such as Microsoft~\textit{WARP} to the degree that such emulation can be considered viable for use in retail applications.\\
+As such, the hypothesis suggested in this document may be summarized as follows:
+\quote{\textit{The performance-impaired emulation of a GPU-kernel may be amended by using high speed software~rasterizers, such as Microsoft~WARP.}}
 % \textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}
@@
 %	Vilka resultat gav studien?
-This article concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered feasable for computational use in real-time, as originally proposed by Microsoft\footref{ftn:warpguide}.
+This article concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered feasable for retail use, as originally proposed by Microsoft\footref{ftn:warpguide}.
 Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics~hardware is unavailable, not sufficient, or busy.\\
@@
 Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
-This operation was therefore considered suitable for the purpose of this experiment.\\
+The operation was therefore considered suitable for the purpose of this experiment.\\
 \\
@@
 \\
-Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object~of~Study for the purpose of this experiment.
+Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
 
@@
 \end{enumerate*}
-The process described above make out the method of this study.
+The process described above make out the Method of this study.
 
@@
 \label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in Section~\ref{sec:contribution:Subjectofstudy}, two kernels with varying lavel of optimization have been examined.
+In addition to the Subject drivers mentioned in Section~\ref{sec:contribution:Subjectofstudy}, two kernels with varying lavel of optimization are examined.
 These kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.\\
@@
 \paragraph{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-	Similar to the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory} in accordance to the implementation by Kirk~\&~Hwu\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
+	Similar to the previous kernel, but further optimized to utilize \textit{shared~memory} in order to reduce time-consuming reading of \textit{global~memory}, as presented by Kirk~\&~Hwu\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
 		Stratton et al.\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of \textit{local}- and \textit{shared}-memory approximately corresponding to a core's \textit{L1}-cache.
 Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP}\footref{ftn:warpguide}.
-Hence, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
+Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
 	This kernel will be referred to as the Tiled~Kernel throughout this material.\\
@@
 Furthermore, aforementioned kernels both support integer- and floating-point precision.\\
-These kernels are attached in their entirety under Appendix.
+These kernels are attached, in their entirety, under Appendix.
 
@@
 Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from \textit{DirectCompute} described in the next paragraph.
+Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.
 \\
@@
 \noindent
-The measurements gathered from these executions make out the results presented in this study.
+The measurements gathered from these executions make out the Results presented in this study.
 
@@
 \label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\ref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~Reference~Device from which \textit{WARP} is derived.\\
+Based off the average of the collected execution times described in Section~\ref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~Reference~Device~Driver from which \textit{WARP} is derived.\\
 Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing \textit{shared~memory} amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
@@
 In Microsoft's guide on \textit{WARP}\footref{ftn:warpguide}, the author claims that an application, if tuned to run efficiently on hardware, will run efficiently on \textit{WARP} - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9\%$ independant of precision, even though the same kernel accelerates the hardware~accelerated Subject by roughly $70\%$.
+However, the data collected for this study rather indicates an increase in execution time of $23.9\%$, independant of precision, even though the same kernel accelerates the hardware~accelerated Subject by roughly $70\%$.
 The floating~point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
@@
 \noindent
-Integer~precision calculation showed no sign of loss of precision whatsoever.
+Integer~precision calculation showed no sign of precisonal loss whatsoever.
 Meanwhile, all floating~point-experiments experienced an equal average loss of computational precision.
@@
 \label{sec:conclusion}
-Based off the results presented in Section~\ref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device in the same manner.
-Hence, if one were to compare the execution of \textit{WARP}~\&~the~Reference~Device side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
+Based off the results presented in Section~\ref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~Reference~Device~Driver in the same manner.
+Hence, if one were to compare the execution of \textit{WARP}~\&~the~Reference~Device~Driver side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
 However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~Reference~Device is primarily proposed by Microsoft as a debugging/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{ftn:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
+The \textit{DirectX}~Reference~Device~Driver is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense\footref{ftn:warpguide} - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.\\
 This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\

### 2013-10-22 article.tex
Grammar and formatting.

@@
 Results demonstrate a major performance boost when compared to that of software~rasterization using the Reference~Device~Driver.
-Thus, this study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies such as Microsoft~\textit{WARP} to the degree that such emulation can be considered viable for use in retail applications.\\
+Thus, this study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies, such as Microsoft~\textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.\\
 As such, the hypothesis suggested in this document may be summarized as follows:
@@
 The increased utilization of complex \textit{GPGPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
-Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
+Therefore, it may be desirable for the developer to be able to view the data being computed on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
 % Approach and Result
@@
 \\
-%...in exchange for some computational precision. Not Supported by cited source. From where did I get that idea?
 %	Vilka resultat gav studien?
@@
 The remainder of this document presents the method and process to acquire the data used,  the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future~work in the area along with propositions of further study.
-%	Vilket upplägg har resterande delar av matrialet?
 
@@
 \\
-For the Object~of~Study, the dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware~accelerated reference case.
+The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware~accelerated reference case.
 \\
@@
 \label{sec:contribution:method}
-In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel on some target platform.
+In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\ref{sec:contribution:Subjectofstudy}).
 The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
@@
 \label{sec:contribution:Subjectofstudy}
-% Describe these modes and what they entail:
 The \textit{GPU}-kernels described in Section~\ref{sec:contribution:method} are comprised of \textit{HLSL}-syntax and are compiled \& executed using Microsoft~\textit{DirectCompute}.
@@
 Microsoft describes \textit{WARP} as a high-performance software~rasterizer, and recommends using the driver for retail applications, such as casual~games\footref{ftn:warpguide}.\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP} expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
-% May one encounter computational precision issues with WARP?
+As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
 
@@
 	The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.\\
-	Execution is performed in blocks of $16x16$ threads, as this number was found to be the block dimension performing optimally whilst hardware~accelerated on the \textit{GPU}\footnote{Make sure of this!}.
+	Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware~accelerated on the system described in Section~\ref{sec:contribution:equipment}.
 \\
@@
 Retrieved: 21-10-2013.}, along with a guide on how to compile and run the solution in order to replicate the experiment.
-Furthermore, the results collected and used throughout this study is also available for download, and may be acquired for further analysis.
+Furthermore, the complete results collected and used throughout this study is also available for download, and may be acquired for further analysis.
 
@@
 
+\newpage
 \section*{Appendix}

### 2014-01-06 tex/eurosis/eurosis.tex
Made changes suggested by lecturer Martin Fredriksson for the purpose of submitting the article to the Eurosis GAME-ON ASIA 2014 conference. I wish to thank Martin for the help offered during throughout the process of writing this article.
Added foundation for Eurosis-formatted article. This commit contains certain formatting errors caused by the transition, such as erronous references caused by the lack of section numbering.

Section references now using section names rather than numbering.

Made code featured under appendix more compact to fit the more strict two-column layout by Eurosis. Un

\documentclass[a4paper,twocolumn,10pt]{article}

\usepackage{url}
\usepackage{float}
\usepackage{color}
\usepackage{tabto}
\usepackage{natbib}
\usepackage{listings}
\usepackage{eurosis}
\usepackage{mdwlist}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{footmisc}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[dvipsnames]{xcolor}

\usepackage{multibib}
\newcites{web}{WEB REFERENCES}

\lstset { 
	language=C,
	tabsize=4,
	backgroundcolor=\color{black!5},
	basicstyle=\footnotesize,
}

\bibpunct[; ]{(}{)}{,}{a}{}{;}

\begin{document}
\title{PERFORMANCE~VARIATIONS~IN~EMULATED~GPGPU~KERNELS}
\author{Eric~Nilsson and Martin~Fredriksson\\
Department~of~Creative~Technologies\\
Blekinge~Institute~of~Technology\\
37179,~Karlskrona\\
Sweden\\
email: \href{mailto:EricNNilsson@gmail.com}{ericnnilsson@gmail.com} and \href{mailto:martin.fredriksson@bth.se}{martin.fredriksson@bth.se}}
\date{}

\maketitle

\thispagestyle{empty}

\keywords{GPGPU, GPU, Simulation, Emulation, DirectCompute, WARP}

% ABSTRACT
\begin{abstract}
A convenient approach toward debugging or profiling \textit{GPU}-kernels is to emulate the kernel on a \textit{CPU}. This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}). When performing such emulation, however, one may experience severe performance loss due to computational overhead. Consequently, the subject of this study is performance variations between three different driver types from the \textit{DirectX}-framework; using \textit{DirectCompute} and the high speed software rasterizer \textit{WARP}. As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}. Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.
\end{abstract}

% INTRODUCTION
\section{INTRODUCTION}
\label{sec:introduction}
When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~\&~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of \textit{GPGPU}-performance). The increased utilization of complex \textit{GPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware. Therefore, it may be desirable for the developer to be able to view the data being computed on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}), such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance-losses. Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}). This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
\\
Furthermore, this material concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}-technology (\textit{Windows~Advanced~Rasterization~Platform}) - which promises high-speed software emulation (see Microsoft's reference on \textit{WARP}\citeweb[]{warp}).\\
\\
This paper concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered viable for retail use, as originally proposed by Microsoft (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}). Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.\\
\\
As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.\\
The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future work in the area along with propositions of further study.

% CONTRIBUTION
\section{CONTRIBUTION}
\label{sec:contribution}

% CONTRIBUTION - OBJECT OF STUDY
\subsection{Object~of~Study}
\label{sec:contribution:objectofstudy}
Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic. For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}. Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type. The operation was therefore considered suitable for the purpose of this experiment.\\
\\
The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware accelerated reference case.\\
Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.

% CONTRIBUTION - METHOD OF STUDY
\subsection{Method~of~Study}
\label{sec:contribution:methodofstudy}
In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\nameref{sec:contribution:subjectsofstudy}). The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
\begin{enumerate*}
	\item Randomize two matrices $A$ \& $B$ using desired data-type.
	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
	\item Start a synchronized high-precision timer.
	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
	\item Stop the timer once the kernel has finished execution.
	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
\end{enumerate*}
The process described above make out the Method of this study.

% CONTRIBUTION - SUBJECTS OF STUDY
\subsection{Subjects~of~Study}
\label{sec:contribution:subjectsofstudy}
The \textit{GPU}-kernels described in Section~\nameref{sec:contribution:methodofstudy} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft \textit{DirectCompute}. These kernels are run using three types of acceleration technologies with varying strategies of \textit{GPU}-kernel emulation. These are comprised of the following:
\subsubsection{Hardware-Acceleration~(GPU)}
The execution of a \textit{DirectCompute}-kernel on a graphics card. This is the common case, and involves no emulation of the kernel. Thus, this case will act as a reference for the emulated Subjects.\\
During hardware acceleration on the \textit{GPU}, one may expect high performance.
\subsubsection{Software~Rasterization~(CPU)}
The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX} \textit{Reference~Device~Driver}. The \textit{Reference~Device~Driver} was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}).\\
As the \textit{Reference~Device~Driver} is designed for the purpose of accuracy, rather than speed, one may expect poor performance.

\subsubsection{Windows~Advanced~Rasterization~Platform~(CPU)}
The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework. The driver is based off the \textit{DirectX} \textit{Reference~Device~Driver} and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance. Microsoft describes \textit{WARP} as a high-performance software rasterizer, and recommends using the driver for retail applications, such as casual games (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).\\
As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
\\
These three \textit{DirectX} driver-types make out the Subjects of this study.

% CONTRIBUTION - KERNELS
\subsection{Kernels}
\label{sec:contribution:kernels}
In addition to the Subject drivers mentioned in Section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined. The kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}. These kernels are presented below.
\subsubsection{Matrix~mult.~w.~Thread~Blocks}
A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis. The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix. Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in Section~\nameref{sec:contribution:equipment}.\\
This kernel will be referred to as the Basic~Kernel throughout this material.

\subsubsection{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
Similar to the previous kernel, but further optimized to utilize shared memory in order to reduce time-consuming reading of global memory, as presented by Kirk~\&~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to a core's \textit{L1}-cache. Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}). Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
This kernel will be referred to as the Tiled~Kernel throughout this material.\\
\\
Furthermore, aforementioned kernels both support integer- and floating-point precision. These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.

% CONTRIBUTION - TOOLS
\subsection{Tools}
\label{sec:contribution:tools}
The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.

\subsubsection{matrixgen}
Denotes a utility developed to generate matrices of different dimensions and data-types. Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.\\
\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A~\&~B$ into product matrix $Ref$. In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}. As \textit{matrixgen} utilizes Microsoft \texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.

\subsubsection{experiment}
Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from matrices $A~\&~B$ generated by \textit{matrixgen}. The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax. As \textit{experiment} is developed using the \textit{Windows~8}~SDK, \textit{Windows~8.0} or later is required. Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.

\subsubsection{analytics}
\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C~\&~Ref$. \textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation. In turn, analytics outputs this information to an intermediate file.\\
\textit{analytics} is written in \texttt{C++}.\\
\\
These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program. This script, written in \texttt{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
The source code manufactured for the sake of this study is freely available via an online \textit{Git} repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment. Furthermore, the complete results collected and used throughout this study are also available for download, and may be acquired for further analysis.

% CONTRIBUTION - EQUIPMENT
\subsection{Equipment}
\label{sec:contribution:equipment}
The results presented in this study is gathered from experiments performed on a system with the following specifications:
\begin{description*}
	\item[CPU]	Intel~Q9550~Quad~Core~$2.83$GHz
	\item[GPU]	ATI~Radeon~HD~5800
	\item[OS]	\tabto{0.35cm}\textit{Windows~8.0} % hack
\end{description*}
This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP} driver performs best on modern quad-core \textit{CPU}s (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).

% CONTRIBUTION - PROCESS OF STUDY
\subsection{Process~of~Study}
\label{sec:contribution:processofstudy}
For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten. The product matrix of these matrices was then computed $100$ times for each configuration. In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel. For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization) was garnered along with precision-wize deviational data.\\
The process described above was then repeated for integer- and floating point-precision.\\
\\
The measurements gathered from these executions make out the Results presented in this study.

% CONTRIBUTION - RESULTS
\subsection{Results}
\label{sec:contribution:results}
Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~\textit{Reference~Device~Driver} from which \textit{WARP} is derived. Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).

\begin{table}[hbt]
\begin{center}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$  					\\ \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$   					\\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$   					\\ \hline
\end{tabular}
\end{center}
\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
\label{tab:contribution:results:summaryint}
\end{table}

\begin{table}[hbt]
\begin{center}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$  				\\ \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$   				\\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$  				\\ \hline
\end{tabular}
\end{center}
\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
\label{tab:contribution:results:summaryfloat}
\end{table}

Using both integer- and floating point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}. In Microsoft's guide on \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using \textit{WARP} - and vice versa. However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%. The floating point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.

\begin{figure}[htb]
\begin{center}
	\resizebox{ \columnwidth }{!}{\input{../../msswarp}}
	\caption{\textit{WARP} execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations. Values outside of their respective standard deviations have been clipped for the sake of clarity.}
	\label{fig:contribution:results:warp:msswarp}
\end{center}
\end{figure}

Integer precision calculation showed no sign of precisonal loss whatsoever. Meanwhile, all floating point-experiments experienced an equal average loss of computational precision. However, the data collected indicates no divergence in the precisional loss of respective Subject. The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\nameref{sec:contribution:methodofstudy}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
\label{sec:contribution:results:computationalprecision}
\begin{table}[hbt]
\begin{center}
	\begin{tabular}{|r|r|r|}
		\hline
		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
		0.0   			& ~0.01  			& ~0.0025      		\\ \hline
	\end{tabular}
\caption {Average precisional deviations in floating~point-operations for all Subjects.}
\label{tab:contribution:results:avgprecision}
\end{center}
\end{table}

These results are expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}). See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.

\newpage

% CONCLUSION
\section{CONCLUSION}
\label{sec:conclusion}
Based on the results presented in Section~\nameref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{Reference~Device~Driver} in the same manner. Hence, if one were to compare the execution of \textit{WARP} \& the \textit{Reference~Device~Driver} side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes. The \textit{DirectX}~\textit{Reference~Device~Driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes. This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\
\\
In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.

% CONCLUSION - FUTURE WORK
\subsection{Future~Work}
\label{sec:conclusion:futurework}
For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
\\
Additionally, the use of more complex kernels in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.

\newpage

% BIBLIOGRAPHY
\bibliographystyle{eurosis}
\bibliographystyleweb{eurosis}

\bibliography{eurosis}
\bibliographyweb{eurosis}

\newpage

% APPENDIX
\section{APPENDIX}
\label{sec:appendix}

% APPENDIX - MATRIX MULT. W. BLOCKS
\subsection*{Matrix~mult.~w.~Blocks}
\begin{lstlisting}
#ifndef DV2549_FXS_MULTFLOATBASIC_FX
#define DV2549_FXS_MULTFLOATBASIC_FX

#include <CommonFloat.fx>

[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
void main(
	uint3 tIdx : SV_GroupThreadID,
	uint3 bIdx : SV_GroupID ) {
	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
	if( row>=cRows || col>=cCols ) {
		return;
	}

	float sum = 0;
	for( uint i = 0; i<aRows; i++ ) {
		uint idxA = row*aRows+i;
		uint idxB = col+bRows*i;
		sum += mA[idxA]*mB[idxB];
	}
	mC[row*cRows+col] = sum;
}

#endif // DV2549_FXS_MULTFLOATBASIC_FX
\end{lstlisting}

\newpage
\vspace*{0.08cm} % hack

% APPENDIX - MATRIX MULT. W. BLOCKS & SHARED MEMORY
\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
\begin{lstlisting}
#ifndef DV2549_FXS_MULTFLOATTILE_H
#define DV2549_FXS_MULTFLOATTILE_H

#include <CommonFloat.fx>

groupshared float mAs[BLOCK_SIZE][BLOCK_SIZE];
groupshared float mBs[BLOCK_SIZE][BLOCK_SIZE];

[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
void main(
	uint3 tIdx : SV_GroupThreadID,
	uint3 bIdx : SV_GroupID ) {
	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;

	float sum = 0;
	const uint blocks = ceil( 
		(float)aRows/(float)BLOCK_SIZE );
	for( uint i = 0; i<blocks; i++ ) {
		mAs[tIdx.y][tIdx.x] = mA[ 
			row*aRows+( i*BLOCK_SIZE+tIdx.x )];
		mBs[tIdx.y][tIdx.x] = mB[ 
			col+bRows*( i*BLOCK_SIZE+tIdx.y )];
		GroupMemoryBarrierWithGroupSync();

		for( uint j = 0; j<BLOCK_SIZE; j++ ) {
			sum += 
				mAs[tIdx.y][j]*mBs[j][tIdx.x];
		}
		GroupMemoryBarrierWithGroupSync();
	}
	if( row>=cRows || col>=cCols ) {
		return;
	}
	mC[row*cRows+col] = sum;
}

#endif // DV2549_FXS_MULTFLOATTILE_H

\end{lstlisting}

\end{document}

### 2014-07-02 build.py
Modified GNUplot script to accomodate for migration of data files into dat/ directory. Added new build script.

@@ -1,0 +1,15 @@
+#!/bin/python
+
+import os
+import sys
+import subprocess
+
+os.chdir('tex/eurosis')
+
+subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)
+
+subprocess.call(["bibtex", "web.aux"])
+subprocess.call(["bibtex", "eurosis.aux"])
+
+subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)
+subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)

### 2014-07-02 tex/gameon/GAME_HARD_01_CONCLUSION.tex
Added new article build for GAMEON 2014 in September.

--- 2014-01-06 tex/eurosis/eurosis.tex
@@
-\documentclass[a4paper,twocolumn,10pt]{article}
+% GAME_HARD_01_CONCLUSION.tex
 
-\usepackage{url}
-\usepackage{float}
-\usepackage{color}
-\usepackage{tabto}
-\usepackage{natbib}
-\usepackage{listings}
-\usepackage{eurosis}
-\usepackage{mdwlist}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{footmisc}
-\usepackage{hyperref}
-\usepackage{verbatim}
-\usepackage[dvipsnames]{xcolor}
-
-\usepackage{multibib}
-\newcites{web}{WEB REFERENCES}
-
-\lstset { 
-	language=C,
-	tabsize=4,
-	backgroundcolor=\color{black!5},
-	basicstyle=\footnotesize,
-}
-
-\bibpunct[; ]{(}{)}{,}{a}{}{;}
-
-\begin{document}
-\title{PERFORMANCE~VARIATIONS~IN~EMULATED~GPGPU~KERNELS}
-\author{Eric~Nilsson and Martin~Fredriksson\\
-Department~of~Creative~Technologies\\
-Blekinge~Institute~of~Technology\\
-37179,~Karlskrona\\
-Sweden\\
-email: \href{mailto:EricNNilsson@gmail.com}{ericnnilsson@gmail.com} and \href{mailto:martin.fredriksson@bth.se}{martin.fredriksson@bth.se}}
-\date{}
-
-\maketitle
-
-\thispagestyle{empty}
-
-\keywords{GPGPU, GPU, Simulation, Emulation, DirectCompute, WARP}
-
-% ABSTRACT
-\begin{abstract}
-A convenient approach toward debugging or profiling \textit{GPU}-kernels is to emulate the kernel on a \textit{CPU}.
-This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-When performing such emulation, however, one may experience severe performance loss due to computational overhead.
-Consequently, the subject of this study is performance variations between three different driver types from the \textit{DirectX}-framework; using \textit{DirectCompute} and the high speed software rasterizer \textit{WARP}.
-As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}.
-Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.
-\end{abstract}
-
-% INTRODUCTION
-\section{INTRODUCTION}
-\label{sec:introduction}
-When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~\&~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of \textit{GPGPU}-performance).
-The increased utilization of complex \textit{GPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
-Therefore, it may be desirable for the developer to be able to view the data being computed on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}), such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance-losses.
-Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
-\\
-Furthermore, this material concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}-technology (\textit{Windows~Advanced~Rasterization~Platform}) - which promises high-speed software emulation (see Microsoft's reference on \textit{WARP}\citeweb[]{warp}).\\
-\\
-This paper concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered viable for retail use, as originally proposed by Microsoft (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.\\
-\\
-As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.\\
-The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future work in the area along with propositions of further study.
-
-% CONTRIBUTION
-\section{CONTRIBUTION}
-\label{sec:contribution}
-
-% CONTRIBUTION - OBJECT OF STUDY
-\subsection{Object~of~Study}
-\label{sec:contribution:objectofstudy}
-Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
-For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
-Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
-The operation was therefore considered suitable for the purpose of this experiment.\\
-\\
-The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware accelerated reference case.\\
-Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
-
-% CONTRIBUTION - METHOD OF STUDY
-\subsection{Method~of~Study}
-\label{sec:contribution:methodofstudy}
-In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\nameref{sec:contribution:subjectsofstudy}).
-The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
-\begin{enumerate*}
-	\item Randomize two matrices $A$ \& $B$ using desired data-type.
-	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
-	\item Start a synchronized high-precision timer.
-	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
-	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
-\end{enumerate*}
-The process described above make out the Method of this study.
-
-% CONTRIBUTION - SUBJECTS OF STUDY
-\subsection{Subjects~of~Study}
-\label{sec:contribution:subjectsofstudy}
-The \textit{GPU}-kernels described in Section~\nameref{sec:contribution:methodofstudy} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft \textit{DirectCompute}.
-These kernels are run using three types of acceleration technologies with varying strategies of \textit{GPU}-kernel emulation.
-These are comprised of the following:
-\subsubsection{Hardware-Acceleration~(GPU)}
-The execution of a \textit{DirectCompute}-kernel on a graphics card.
-This is the common case, and involves no emulation of the kernel.
-Thus, this case will act as a reference for the emulated Subjects.\\
-During hardware acceleration on the \textit{GPU}, one may expect high performance.
-\subsubsection{Software~Rasterization~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX} \textit{Reference~Device~Driver}.
-The \textit{Reference~Device~Driver} was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}).\\
-As the \textit{Reference~Device~Driver} is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
-
-\subsubsection{Windows~Advanced~Rasterization~Platform~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.
-The driver is based off the \textit{DirectX} \textit{Reference~Device~Driver} and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance.
-Microsoft describes \textit{WARP} as a high-performance software rasterizer, and recommends using the driver for retail applications, such as casual games (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
-\\
-These three \textit{DirectX} driver-types make out the Subjects of this study.
-
-% CONTRIBUTION - KERNELS
-\subsection{Kernels}
-\label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in Section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
-The kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-These kernels are presented below.
-\subsubsection{Matrix~mult.~w.~Thread~Blocks}
-A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.
-The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.
-Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in Section~\nameref{sec:contribution:equipment}.\\
-This kernel will be referred to as the Basic~Kernel throughout this material.
-
-\subsubsection{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-Similar to the previous kernel, but further optimized to utilize shared memory in order to reduce time-consuming reading of global memory, as presented by Kirk~\&~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to a core's \textit{L1}-cache.
-Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
-This kernel will be referred to as the Tiled~Kernel throughout this material.\\
-\\
-Furthermore, aforementioned kernels both support integer- and floating-point precision. These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
-
-% CONTRIBUTION - TOOLS
-\subsection{Tools}
-\label{sec:contribution:tools}
-The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
-
-\subsubsection{matrixgen}
-Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.\\
-\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A~\&~B$ into product matrix $Ref$.
-In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
-As \textit{matrixgen} utilizes Microsoft \texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.
-
-\subsubsection{experiment}
-Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from matrices $A~\&~B$ generated by \textit{matrixgen}.
-The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
-\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.
-As \textit{experiment} is developed using the \textit{Windows~8}~SDK, \textit{Windows~8.0} or later is required.
-Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
-
-\subsubsection{analytics}
-\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C~\&~Ref$.
-\textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
-In turn, analytics outputs this information to an intermediate file.\\
-\textit{analytics} is written in \texttt{C++}.\\
-\\
-These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
-This script, written in \texttt{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
-The source code manufactured for the sake of this study is freely available via an online \textit{Git} repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment.
-Furthermore, the complete results collected and used throughout this study are also available for download, and may be acquired for further analysis.
-
-% CONTRIBUTION - EQUIPMENT
-\subsection{Equipment}
-\label{sec:contribution:equipment}
-The results presented in this study is gathered from experiments performed on a system with the following specifications:
-\begin{description*}
-	\item[CPU]	Intel~Q9550~Quad~Core~$2.83$GHz
-	\item[GPU]	ATI~Radeon~HD~5800
-	\item[OS]	\tabto{0.35cm}\textit{Windows~8.0} % hack
-\end{description*}
-This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP} driver performs best on modern quad-core \textit{CPU}s (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-
-% CONTRIBUTION - PROCESS OF STUDY
-\subsection{Process~of~Study}
-\label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten.
-The product matrix of these matrices was then computed $100$ times for each configuration.
-In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel.
-For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization) was garnered along with precision-wize deviational data.\\
-The process described above was then repeated for integer- and floating point-precision.\\
-\\
-The measurements gathered from these executions make out the Results presented in this study.
-
-% CONTRIBUTION - RESULTS
-\subsection{Results}
-\label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~\textit{Reference~Device~Driver} from which \textit{WARP} is derived.
-Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$  					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$   					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$   					\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
-\label{tab:contribution:results:summaryint}
-\end{table}
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$  				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$   				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$  				\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
-\label{tab:contribution:results:summaryfloat}
-\end{table}
-
-Using both integer- and floating point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.
-In Microsoft's guide on \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using \textit{WARP} - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
-The floating point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
-
-\begin{figure}[htb]
-\begin{center}
-	\resizebox{ \columnwidth }{!}{\input{../../msswarp}}
-	\caption{\textit{WARP} execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
-Values outside of their respective standard deviations have been clipped for the sake of clarity.}
-	\label{fig:contribution:results:warp:msswarp}
-\end{center}
-\end{figure}
-
-Integer precision calculation showed no sign of precisonal loss whatsoever.
-Meanwhile, all floating point-experiments experienced an equal average loss of computational precision.
-However, the data collected indicates no divergence in the precisional loss of respective Subject.
-The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\nameref{sec:contribution:methodofstudy}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
-\label{sec:contribution:results:computationalprecision}
-\begin{table}[hbt]
-\begin{center}
-	\begin{tabular}{|r|r|r|}
-		\hline
-		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
-		0.0   			& ~0.01  			& ~0.0025      		\\ \hline
-	\end{tabular}
-\caption {Average precisional deviations in floating~point-operations for all Subjects.}
-\label{tab:contribution:results:avgprecision}
-\end{center}
-\end{table}
-
-These results are expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.
-
-\newpage
-
-% CONCLUSION
 \section{CONCLUSION}
@@
 Additionally, the use of more complex kernels in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.
-
-\newpage
-
-% BIBLIOGRAPHY
-\bibliographystyle{eurosis}
-\bibliographystyleweb{eurosis}
-
-\bibliography{eurosis}
-\bibliographyweb{eurosis}
-
-\newpage
-
-% APPENDIX
-\section{APPENDIX}
-\label{sec:appendix}
-
-% APPENDIX - MATRIX MULT. W. BLOCKS
-\subsection*{Matrix~mult.~w.~Blocks}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATBASIC_FX
-#define DV2549_FXS_MULTFLOATBASIC_FX
-
-#include <CommonFloat.fx>
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-
-	float sum = 0;
-	for( uint i = 0; i<aRows; i++ ) {
-		uint idxA = row*aRows+i;
-		uint idxB = col+bRows*i;
-		sum += mA[idxA]*mB[idxB];
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATBASIC_FX
-\end{lstlisting}
-
-\newpage
-\vspace*{0.08cm} % hack
-
-% APPENDIX - MATRIX MULT. W. BLOCKS & SHARED MEMORY
-\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATTILE_H
-#define DV2549_FXS_MULTFLOATTILE_H
-
-#include <CommonFloat.fx>
-
-groupshared float mAs[BLOCK_SIZE][BLOCK_SIZE];
-groupshared float mBs[BLOCK_SIZE][BLOCK_SIZE];
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-
-	float sum = 0;
-	const uint blocks = ceil( 
-		(float)aRows/(float)BLOCK_SIZE );
-	for( uint i = 0; i<blocks; i++ ) {
-		mAs[tIdx.y][tIdx.x] = mA[ 
-			row*aRows+( i*BLOCK_SIZE+tIdx.x )];
-		mBs[tIdx.y][tIdx.x] = mB[ 
-			col+bRows*( i*BLOCK_SIZE+tIdx.y )];
-		GroupMemoryBarrierWithGroupSync();
-
-		for( uint j = 0; j<BLOCK_SIZE; j++ ) {
-			sum += 
-				mAs[tIdx.y][j]*mBs[j][tIdx.x];
-		}
-		GroupMemoryBarrierWithGroupSync();
-	}
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATTILE_H
-
-\end{lstlisting}
-
-\end{document}

### 2014-07-02 tex/gameon/GAME_HARD_01_CONTRIBUTION.tex
Added new article build for GAMEON 2014 in September.

--- 2014-01-06 tex/eurosis/eurosis.tex
@@
-\documentclass[a4paper,twocolumn,10pt]{article}
-
-\usepackage{url}
-\usepackage{float}
-\usepackage{color}
-\usepackage{tabto}
-\usepackage{natbib}
-\usepackage{listings}
-\usepackage{eurosis}
-\usepackage{mdwlist}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{footmisc}
-\usepackage{hyperref}
-\usepackage{verbatim}
-\usepackage[dvipsnames]{xcolor}
-
-\usepackage{multibib}
-\newcites{web}{WEB REFERENCES}
-
-\lstset { 
-	language=C,
-	tabsize=4,
-	backgroundcolor=\color{black!5},
-	basicstyle=\footnotesize,
-}
-
-\bibpunct[; ]{(}{)}{,}{a}{}{;}
-
-\begin{document}
-\title{PERFORMANCE~VARIATIONS~IN~EMULATED~GPGPU~KERNELS}
-\author{Eric~Nilsson and Martin~Fredriksson\\
-Department~of~Creative~Technologies\\
-Blekinge~Institute~of~Technology\\
-37179,~Karlskrona\\
-Sweden\\
-email: \href{mailto:EricNNilsson@gmail.com}{ericnnilsson@gmail.com} and \href{mailto:martin.fredriksson@bth.se}{martin.fredriksson@bth.se}}
-\date{}
-
-\maketitle
-
-\thispagestyle{empty}
-
-\keywords{GPGPU, GPU, Simulation, Emulation, DirectCompute, WARP}
-
-% ABSTRACT
-\begin{abstract}
-A convenient approach toward debugging or profiling \textit{GPU}-kernels is to emulate the kernel on a \textit{CPU}.
-This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-When performing such emulation, however, one may experience severe performance loss due to computational overhead.
-Consequently, the subject of this study is performance variations between three different driver types from the \textit{DirectX}-framework; using \textit{DirectCompute} and the high speed software rasterizer \textit{WARP}.
-As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}.
-Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.
-\end{abstract}
-
-% INTRODUCTION
-\section{INTRODUCTION}
-\label{sec:introduction}
-When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~\&~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of \textit{GPGPU}-performance).
-The increased utilization of complex \textit{GPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
-Therefore, it may be desirable for the developer to be able to view the data being computed on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}), such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance-losses.
-Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
-\\
-Furthermore, this material concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}-technology (\textit{Windows~Advanced~Rasterization~Platform}) - which promises high-speed software emulation (see Microsoft's reference on \textit{WARP}\citeweb[]{warp}).\\
-\\
-This paper concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered viable for retail use, as originally proposed by Microsoft (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.\\
-\\
-As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.\\
-The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future work in the area along with propositions of further study.
+% GAME_HARD_01_CONTRIBUTION.tex
 
@@
 \\
-Furthermore, aforementioned kernels both support integer- and floating-point precision. These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
+Furthermore, aforementioned kernels both support integer- and floating-point precision.
+These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
 
@@
 \label{sec:contribution:tools}
-The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
+The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation.
+These are presented below.
 
@@
 See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.
-
-\newpage
-
-% CONCLUSION
-\section{CONCLUSION}
-\label{sec:conclusion}
-Based on the results presented in Section~\nameref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{Reference~Device~Driver} in the same manner.
-Hence, if one were to compare the execution of \textit{WARP} \& the \textit{Reference~Device~Driver} side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
-However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~\textit{Reference~Device~Driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.
-This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\
-\\
-In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
-
-% CONCLUSION - FUTURE WORK
-\subsection{Future~Work}
-\label{sec:conclusion:futurework}
-For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
-\\
-Additionally, the use of more complex kernels in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.
-
-\newpage
-
-% BIBLIOGRAPHY
-\bibliographystyle{eurosis}
-\bibliographystyleweb{eurosis}
-
-\bibliography{eurosis}
-\bibliographyweb{eurosis}
-
-\newpage
-
-% APPENDIX
-\section{APPENDIX}
-\label{sec:appendix}
-
-% APPENDIX - MATRIX MULT. W. BLOCKS
-\subsection*{Matrix~mult.~w.~Blocks}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATBASIC_FX
-#define DV2549_FXS_MULTFLOATBASIC_FX
-
-#include <CommonFloat.fx>
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-
-	float sum = 0;
-	for( uint i = 0; i<aRows; i++ ) {
-		uint idxA = row*aRows+i;
-		uint idxB = col+bRows*i;
-		sum += mA[idxA]*mB[idxB];
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATBASIC_FX
-\end{lstlisting}
-
-\newpage
-\vspace*{0.08cm} % hack
-
-% APPENDIX - MATRIX MULT. W. BLOCKS & SHARED MEMORY
-\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATTILE_H
-#define DV2549_FXS_MULTFLOATTILE_H
-
-#include <CommonFloat.fx>
-
-groupshared float mAs[BLOCK_SIZE][BLOCK_SIZE];
-groupshared float mBs[BLOCK_SIZE][BLOCK_SIZE];
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-
-	float sum = 0;
-	const uint blocks = ceil( 
-		(float)aRows/(float)BLOCK_SIZE );
-	for( uint i = 0; i<blocks; i++ ) {
-		mAs[tIdx.y][tIdx.x] = mA[ 
-			row*aRows+( i*BLOCK_SIZE+tIdx.x )];
-		mBs[tIdx.y][tIdx.x] = mB[ 
-			col+bRows*( i*BLOCK_SIZE+tIdx.y )];
-		GroupMemoryBarrierWithGroupSync();
-
-		for( uint j = 0; j<BLOCK_SIZE; j++ ) {
-			sum += 
-				mAs[tIdx.y][j]*mBs[j][tIdx.x];
-		}
-		GroupMemoryBarrierWithGroupSync();
-	}
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATTILE_H
-
-\end{lstlisting}
-
-\end{document}

### 2014-07-02 tex/gameon/GAME_HARD_01_INTRODUCTION.tex
Added new article build for GAMEON 2014 in September.

--- 2014-01-06 tex/eurosis/eurosis.tex
@@
-\documentclass[a4paper,twocolumn,10pt]{article}
-
-\usepackage{url}
-\usepackage{float}
-\usepackage{color}
-\usepackage{tabto}
-\usepackage{natbib}
-\usepackage{listings}
-\usepackage{eurosis}
-\usepackage{mdwlist}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{footmisc}
-\usepackage{hyperref}
-\usepackage{verbatim}
-\usepackage[dvipsnames]{xcolor}
-
-\usepackage{multibib}
-\newcites{web}{WEB REFERENCES}
-
-\lstset { 
-	language=C,
-	tabsize=4,
-	backgroundcolor=\color{black!5},
-	basicstyle=\footnotesize,
-}
-
-\bibpunct[; ]{(}{)}{,}{a}{}{;}
-
-\begin{document}
-\title{PERFORMANCE~VARIATIONS~IN~EMULATED~GPGPU~KERNELS}
-\author{Eric~Nilsson and Martin~Fredriksson\\
-Department~of~Creative~Technologies\\
-Blekinge~Institute~of~Technology\\
-37179,~Karlskrona\\
-Sweden\\
-email: \href{mailto:EricNNilsson@gmail.com}{ericnnilsson@gmail.com} and \href{mailto:martin.fredriksson@bth.se}{martin.fredriksson@bth.se}}
-\date{}
-
-\maketitle
-
-\thispagestyle{empty}
-
-\keywords{GPGPU, GPU, Simulation, Emulation, DirectCompute, WARP}
-
-% ABSTRACT
-\begin{abstract}
-A convenient approach toward debugging or profiling \textit{GPU}-kernels is to emulate the kernel on a \textit{CPU}.
-This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-When performing such emulation, however, one may experience severe performance loss due to computational overhead.
-Consequently, the subject of this study is performance variations between three different driver types from the \textit{DirectX}-framework; using \textit{DirectCompute} and the high speed software rasterizer \textit{WARP}.
-As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}.
-Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.
-\end{abstract}
+% GAME_HARD_01_INTRODUCTION.tex
 
@@
 The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future work in the area along with propositions of further study.
-
-% CONTRIBUTION
-\section{CONTRIBUTION}
-\label{sec:contribution}
-
-% CONTRIBUTION - OBJECT OF STUDY
-\subsection{Object~of~Study}
-\label{sec:contribution:objectofstudy}
-Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
-For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
-Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
-The operation was therefore considered suitable for the purpose of this experiment.\\
-\\
-The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware accelerated reference case.\\
-Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
-
-% CONTRIBUTION - METHOD OF STUDY
-\subsection{Method~of~Study}
-\label{sec:contribution:methodofstudy}
-In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\nameref{sec:contribution:subjectsofstudy}).
-The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
-\begin{enumerate*}
-	\item Randomize two matrices $A$ \& $B$ using desired data-type.
-	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
-	\item Start a synchronized high-precision timer.
-	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
-	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
-\end{enumerate*}
-The process described above make out the Method of this study.
-
-% CONTRIBUTION - SUBJECTS OF STUDY
-\subsection{Subjects~of~Study}
-\label{sec:contribution:subjectsofstudy}
-The \textit{GPU}-kernels described in Section~\nameref{sec:contribution:methodofstudy} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft \textit{DirectCompute}.
-These kernels are run using three types of acceleration technologies with varying strategies of \textit{GPU}-kernel emulation.
-These are comprised of the following:
-\subsubsection{Hardware-Acceleration~(GPU)}
-The execution of a \textit{DirectCompute}-kernel on a graphics card.
-This is the common case, and involves no emulation of the kernel.
-Thus, this case will act as a reference for the emulated Subjects.\\
-During hardware acceleration on the \textit{GPU}, one may expect high performance.
-\subsubsection{Software~Rasterization~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX} \textit{Reference~Device~Driver}.
-The \textit{Reference~Device~Driver} was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}).\\
-As the \textit{Reference~Device~Driver} is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
-
-\subsubsection{Windows~Advanced~Rasterization~Platform~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.
-The driver is based off the \textit{DirectX} \textit{Reference~Device~Driver} and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance.
-Microsoft describes \textit{WARP} as a high-performance software rasterizer, and recommends using the driver for retail applications, such as casual games (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
-\\
-These three \textit{DirectX} driver-types make out the Subjects of this study.
-
-% CONTRIBUTION - KERNELS
-\subsection{Kernels}
-\label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in Section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
-The kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-These kernels are presented below.
-\subsubsection{Matrix~mult.~w.~Thread~Blocks}
-A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.
-The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.
-Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in Section~\nameref{sec:contribution:equipment}.\\
-This kernel will be referred to as the Basic~Kernel throughout this material.
-
-\subsubsection{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-Similar to the previous kernel, but further optimized to utilize shared memory in order to reduce time-consuming reading of global memory, as presented by Kirk~\&~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to a core's \textit{L1}-cache.
-Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
-This kernel will be referred to as the Tiled~Kernel throughout this material.\\
-\\
-Furthermore, aforementioned kernels both support integer- and floating-point precision. These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
-
-% CONTRIBUTION - TOOLS
-\subsection{Tools}
-\label{sec:contribution:tools}
-The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
-
-\subsubsection{matrixgen}
-Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.\\
-\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A~\&~B$ into product matrix $Ref$.
-In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
-As \textit{matrixgen} utilizes Microsoft \texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.
-
-\subsubsection{experiment}
-Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from matrices $A~\&~B$ generated by \textit{matrixgen}.
-The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
-\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.
-As \textit{experiment} is developed using the \textit{Windows~8}~SDK, \textit{Windows~8.0} or later is required.
-Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
-
-\subsubsection{analytics}
-\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C~\&~Ref$.
-\textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
-In turn, analytics outputs this information to an intermediate file.\\
-\textit{analytics} is written in \texttt{C++}.\\
-\\
-These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
-This script, written in \texttt{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
-The source code manufactured for the sake of this study is freely available via an online \textit{Git} repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment.
-Furthermore, the complete results collected and used throughout this study are also available for download, and may be acquired for further analysis.
-
-% CONTRIBUTION - EQUIPMENT
-\subsection{Equipment}
-\label{sec:contribution:equipment}
-The results presented in this study is gathered from experiments performed on a system with the following specifications:
-\begin{description*}
-	\item[CPU]	Intel~Q9550~Quad~Core~$2.83$GHz
-	\item[GPU]	ATI~Radeon~HD~5800
-	\item[OS]	\tabto{0.35cm}\textit{Windows~8.0} % hack
-\end{description*}
-This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP} driver performs best on modern quad-core \textit{CPU}s (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-
-% CONTRIBUTION - PROCESS OF STUDY
-\subsection{Process~of~Study}
-\label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten.
-The product matrix of these matrices was then computed $100$ times for each configuration.
-In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel.
-For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization) was garnered along with precision-wize deviational data.\\
-The process described above was then repeated for integer- and floating point-precision.\\
-\\
-The measurements gathered from these executions make out the Results presented in this study.
-
-% CONTRIBUTION - RESULTS
-\subsection{Results}
-\label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~\textit{Reference~Device~Driver} from which \textit{WARP} is derived.
-Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$  					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$   					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$   					\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
-\label{tab:contribution:results:summaryint}
-\end{table}
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$  				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$   				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$  				\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
-\label{tab:contribution:results:summaryfloat}
-\end{table}
-
-Using both integer- and floating point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.
-In Microsoft's guide on \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using \textit{WARP} - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
-The floating point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
-
-\begin{figure}[htb]
-\begin{center}
-	\resizebox{ \columnwidth }{!}{\input{../../msswarp}}
-	\caption{\textit{WARP} execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
-Values outside of their respective standard deviations have been clipped for the sake of clarity.}
-	\label{fig:contribution:results:warp:msswarp}
-\end{center}
-\end{figure}
-
-Integer precision calculation showed no sign of precisonal loss whatsoever.
-Meanwhile, all floating point-experiments experienced an equal average loss of computational precision.
-However, the data collected indicates no divergence in the precisional loss of respective Subject.
-The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\nameref{sec:contribution:methodofstudy}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
-\label{sec:contribution:results:computationalprecision}
-\begin{table}[hbt]
-\begin{center}
-	\begin{tabular}{|r|r|r|}
-		\hline
-		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
-		0.0   			& ~0.01  			& ~0.0025      		\\ \hline
-	\end{tabular}
-\caption {Average precisional deviations in floating~point-operations for all Subjects.}
-\label{tab:contribution:results:avgprecision}
-\end{center}
-\end{table}
-
-These results are expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.
-
-\newpage
-
-% CONCLUSION
-\section{CONCLUSION}
-\label{sec:conclusion}
-Based on the results presented in Section~\nameref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{Reference~Device~Driver} in the same manner.
-Hence, if one were to compare the execution of \textit{WARP} \& the \textit{Reference~Device~Driver} side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
-However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~\textit{Reference~Device~Driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.
-This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\
-\\
-In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
-
-% CONCLUSION - FUTURE WORK
-\subsection{Future~Work}
-\label{sec:conclusion:futurework}
-For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
-\\
-Additionally, the use of more complex kernels in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.
-
-\newpage
-
-% BIBLIOGRAPHY
-\bibliographystyle{eurosis}
-\bibliographystyleweb{eurosis}
-
-\bibliography{eurosis}
-\bibliographyweb{eurosis}
-
-\newpage
-
-% APPENDIX
-\section{APPENDIX}
-\label{sec:appendix}
-
-% APPENDIX - MATRIX MULT. W. BLOCKS
-\subsection*{Matrix~mult.~w.~Blocks}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATBASIC_FX
-#define DV2549_FXS_MULTFLOATBASIC_FX
-
-#include <CommonFloat.fx>
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-
-	float sum = 0;
-	for( uint i = 0; i<aRows; i++ ) {
-		uint idxA = row*aRows+i;
-		uint idxB = col+bRows*i;
-		sum += mA[idxA]*mB[idxB];
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATBASIC_FX
-\end{lstlisting}
-
-\newpage
-\vspace*{0.08cm} % hack
-
-% APPENDIX - MATRIX MULT. W. BLOCKS & SHARED MEMORY
-\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATTILE_H
-#define DV2549_FXS_MULTFLOATTILE_H
-
-#include <CommonFloat.fx>
-
-groupshared float mAs[BLOCK_SIZE][BLOCK_SIZE];
-groupshared float mBs[BLOCK_SIZE][BLOCK_SIZE];
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-
-	float sum = 0;
-	const uint blocks = ceil( 
-		(float)aRows/(float)BLOCK_SIZE );
-	for( uint i = 0; i<blocks; i++ ) {
-		mAs[tIdx.y][tIdx.x] = mA[ 
-			row*aRows+( i*BLOCK_SIZE+tIdx.x )];
-		mBs[tIdx.y][tIdx.x] = mB[ 
-			col+bRows*( i*BLOCK_SIZE+tIdx.y )];
-		GroupMemoryBarrierWithGroupSync();
-
-		for( uint j = 0; j<BLOCK_SIZE; j++ ) {
-			sum += 
-				mAs[tIdx.y][j]*mBs[j][tIdx.x];
-		}
-		GroupMemoryBarrierWithGroupSync();
-	}
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATTILE_H
-
-\end{lstlisting}
-
-\end{document}

### 2014-07-02 build.py

@@ -4,12 +4,12 @@ import os
 import sys
 import subprocess
 
-os.chdir('tex/eurosis')
+os.chdir('tex/gameon')
 
-subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)
+subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)
 
 subprocess.call(["bibtex", "web.aux"])
-subprocess.call(["bibtex", "eurosis.aux"])
+subprocess.call(["bibtex", "GAME_HARD_01.aux"])
 
-subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)
-subprocess.call("pdflatex -shell-escape eurosis.tex", shell=True)
+subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)
+subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)

### 2014-07-12 dv2549.py
Corrected bug leading result- and reference matrices to be written, as with the original subject matrices, to text files - causing floating point precision to suffer a great deal. This is important due to comparison being performed in the analytics tool, in which we try to establish any deviation in-between DirectCompute and C++ AMP results. Problem was corrected by outputting floating point values (the result and reference matrices) to binary files rather than in plain text. Subject matrices are kept in plain text however, as these ought be revisioned controlled (since they are the subjects o

@@ -9,9 +9,9 @@ import subprocess
 PATH_TO_EXPERIMENT	= "experiment.exe"
 PATH_TO_MATRIXGEN	= "../../matrixgen/Release/matrixgen.exe"
 PATH_TO_ANALYTICS	= "../../analytics/Release/analytics.exe"
-PATH_TO_RESEXP		= "../../" + "resExperiment.res"
-PATH_TO_RESANA		= "../../" + "resAnalytics.res"
-PATH_TO_EXPRES		= "../../../"
+PATH_TO_RESEXP		= "../../../res/" + "resExperiment.res"
+PATH_TO_RESANA		= "../../../res/" + "resAnalytics.res"
+PATH_TO_EXPRES		= "../../../res/"
 def GetPath( rel ): # Relative to absolute path.
 	return os.path.abspath( rel )
 
@@ -99,8 +99,9 @@ def run( cmd ):
 	p = subprocess.Popen( cmd, shell=True, stdout=subprocess.PIPE, stderr=subprocess.STDOUT )
 	return p.communicate()
 def matrixgen( desc ):
-	print( "\nGenerating matrices with properties:\n\tPrecision:\t" + desc.prec + "\n\tDimension:\t" + desc.dim + "\n\tMax:\t\t" + desc.max + "\n\tMin:\t\t" + desc.min + "\n" )
-	run( GetPath( PATH_TO_MATRIXGEN ) + " " + desc.prec + " " + desc.dim + " " + desc.min + " " + desc.max )
+	generateNewMatrices = "0";
+	print( "\nGenerating matrices with properties:\n\tPrecision:\t" + desc.prec + "\n\tDimension:\t" + desc.dim + "\n\tMax:\t\t" + desc.max + "\n\tMin:\t\t" + desc.min + " " + generateNewMatrices + "\n" )
+	run( GetPath( PATH_TO_MATRIXGEN ) + " " + desc.prec + " " + desc.dim + " " + desc.min + " " + desc.max + " 1" )
 def experiment( desc ):
 	expResMss = []
 	expResDMin = []
@@ -126,15 +127,15 @@ def experiment( desc ):
 print( "---\ndv2549\n---" )
 
 # Generate a viable integer matrix:
-matrixgen( factoryDescMat( "INT", "200", "0", "10" ) )
+#matrixgen( factoryDescMat( "INT", "200", "0", "10" ) )
 
 tasksI = []
[…]

### 2014-07-12 src/analytics/FloatList.h

@@ -1,0 +1,9 @@
+#ifndef DV2549_ANALYTICS_DOUBLELIST_H
+#define DV2549_ANALYTICS_DOUBLELIST_H
+
+struct FloatList {
+	float* list;
+	unsigned num;
+};
+
+#endif // DV2549_ANALYTICS_DOUBLELIST_H

### 2014-07-12 src/matrixgen/Matrixgen.h

@@ -4,21 +4,19 @@
 enum MatrixgenPrecisions;
 
 #include <Matrix.h>
+#include <Reader.h>
 #include <Printer.h>
 #include <Ampersand.h>
 
 template < class T >
 class Matrixgen {
 public:
-	Matrixgen( MatrixgenPrecisions p_precision, unsigned p_dim, unsigned p_min, unsigned p_max ) {
+	Matrixgen( MatrixgenPrecisions p_precision, unsigned p_dim, unsigned p_min, unsigned p_max, bool p_pop ) {
 		m_precision = p_precision;
 		m_dim = p_dim;
 		m_min = p_min;
 		m_max = p_max;
-
-		m_a = new Matrix< T >( m_dim, m_dim );
-		m_b = new Matrix< T >( m_dim, m_dim );
-		m_c = new Matrix< T >( m_dim, m_dim );
+		m_pop = p_pop;
 	}
 	~Matrixgen() {
 		assert( m_a ); delete m_a;
@@ -29,16 +27,33 @@ public:
 	bool run() {
 		bool success = true;
 
-		Ampersand< T >* m_amp = new Ampersand< T >();
-		m_amp->matrixPopulate( m_a, m_min, m_max );
-		m_amp->matrixPopulate( m_b, m_min, m_max );
-		m_amp->matrixMultiply( m_c, m_a, m_b );
+		Ampersand< T >* amp = new Ampersand< T >();
+		if( m_pop==true ) { // if instructed to populate matrices
+			m_a = new Matrix< T >( m_dim, m_dim );
+			m_b = new Matrix< T >( m_dim, m_dim );
 
-		Printer< T >* m_printer = new Printer< T >( m_precision, m_a, m_b, m_c );
-		success = m_printer->print();
+			amp->matrixPopulate( m_a, m_min, m_max );
+			amp->matrixPopulate( m_b, m_min, m_max );
+		} else { // load from file
+			m_a = Reader< T >::loadMatrix( g_mxgPath + "a.mxg" );
+			m_b = Reader< T >::loadMatrix( g_mxgPath + "b.mxg" );
+			assert( m_a!=nullptr );
+			assert( m_a!=nullptr );
+		}
 
-		delete m_amp;
-		delete m_printer;
+		m_c = new Matrix< T >( m_dim, m_dim );
+		amp->matrixMultiply( m_c, m_a, m_b );
+
+		Printer< T >* printer = nullptr;
+		if( m_pop==true ) {
[…]

### 2014-07-12 src/matrixgen/Reader.h

@@ -1,0 +1,40 @@
+#ifndef DV2549_MATRIXGEN_READER_H
+#define DV2549_MATRIXGEN_READER_H
+
+#include <Matrix.h>
+
+template < class T >
+class Reader {
+public:
+	Reader() {
+	}
+	~Reader() {
+		// Do nothing.
+	}
+
+	static Matrix< T >* loadMatrix( std::string p_filename ) {
+		std::string temp;
+		int precision;
+		unsigned rows, cols;
+		Matrix< T >* matrix = nullptr;
+
+		std::ifstream mxg( p_filename );
+		if( mxg.is_open() ) {
+			mxg >> temp >> precision >> temp >> rows >> temp >> cols;
+
+			unsigned i = 0;
+			matrix = new Matrix< T >( rows, cols );
+			T* m = matrix->get();
+			while( mxg.eof()==false ) {
+				mxg >> m[ i ];
+				i++;
+			}
+		}
+
+		return matrix;
+	}
+protected:
+private:
+};
+
+#endif // DV2549_MATRIXGEN_READER_H

### 2014-07-12 src/matrixgen/main.cpp

@@ -13,26 +13,30 @@ int main( int argc, char* argv[] ) {
 	std::cout << "\n" << "---" << "\n" << "Matrixgen Utility" << "\n" << "---" << "\n";
 
 	int result = 1;
-	unsigned numExpectedArgs = 5; // First argument is the command invoking application.
+	unsigned numExpectedArgs = 6; // First argument is the command invoking application.
 	if( argc==numExpectedArgs ) {
 		std::string precision( argv[ 1 ] );
 		unsigned dim = atoi( argv[ 2 ] );
 		unsigned min = atoi( argv[ 3 ] );
 		unsigned max = atoi( argv[ 4 ] );
+		bool pop = (atoi( argv[ 5 ] )!=0);
+		if( pop==true ) {
+			std::cout << "Populate flag specified as true. Will populate matrices a & b.\n";
+		} else {
+			std::cout << "Populate flag specified as false. Will only compile reference matrix ref.mxgb.\n";
+		}
 
 		if( precision=="INT" ) {
-			// Generate matrix with integer precision.
-			Matrixgen< int > mgen( MatrixgenPrecisions_INT, dim, min, max );
+			Matrixgen< int > mgen( MatrixgenPrecisions_INT, dim, min, max, pop );
 			result = (int)!mgen.run();
 		} else if( precision=="FLOAT" ) {
-			Matrixgen< float > mgen( MatrixgenPrecisions_FLOAT, dim, min, max );
+			Matrixgen< float > mgen( MatrixgenPrecisions_FLOAT, dim, min, max, pop );
 			result = (int)!mgen.run();
-			// Generate matrix with float precision.
 		} else {
 			std::cerr << "Unsupported precision: " << precision;
 		}
 	} else {
-		std::cerr << "Usage: " << argv[ 0 ] << " PRECISION [ INT FLOAT ] DIM MIN MAX" << std::endl;
+		std::cerr << "Usage: " << argv[ 0 ] << " PRECISION [ INT FLOAT ] DIM MIN MAX POPULATE" << std::endl;
 	}
 
 	if( result==0 ) {

### 2014-07-12 tex/GAME_HARD_01_ABSTRACT.tex
Moved paper LaTeX code out of subdirectory and added GNUplot compilation into the build process. Build script now copies the compiled paper into the main directory.

--- 2014-01-06 tex/eurosis/eurosis.tex
@@
-\documentclass[a4paper,twocolumn,10pt]{article}
-
-\usepackage{url}
-\usepackage{float}
-\usepackage{color}
-\usepackage{tabto}
-\usepackage{natbib}
-\usepackage{listings}
-\usepackage{eurosis}
-\usepackage{mdwlist}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{footmisc}
-\usepackage{hyperref}
-\usepackage{verbatim}
-\usepackage[dvipsnames]{xcolor}
-
-\usepackage{multibib}
-\newcites{web}{WEB REFERENCES}
-
-\lstset { 
-	language=C,
-	tabsize=4,
-	backgroundcolor=\color{black!5},
-	basicstyle=\footnotesize,
-}
-
-\bibpunct[; ]{(}{)}{,}{a}{}{;}
-
-\begin{document}
-\title{PERFORMANCE~VARIATIONS~IN~EMULATED~GPGPU~KERNELS}
-\author{Eric~Nilsson and Martin~Fredriksson\\
-Department~of~Creative~Technologies\\
-Blekinge~Institute~of~Technology\\
-37179,~Karlskrona\\
-Sweden\\
-email: \href{mailto:EricNNilsson@gmail.com}{ericnnilsson@gmail.com} and \href{mailto:martin.fredriksson@bth.se}{martin.fredriksson@bth.se}}
-\date{}
-
-\maketitle
-
-\thispagestyle{empty}
-
-\keywords{GPGPU, GPU, Simulation, Emulation, DirectCompute, WARP}
+% GAME_HARD_01_ABSTRACT.tex
 
@@
 \end{abstract}
-
-% INTRODUCTION
-\section{INTRODUCTION}
-\label{sec:introduction}
-When developing \textit{GPU}-kernels, relatively small modifications in code may induce large deviations in performance due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~\&~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of \textit{GPGPU}-performance).
-The increased utilization of complex \textit{GPU}-kernels has brought forth the need of more extensive debugging- and profiling-possibilities involving access of data that may be hard to retrieve from hardware.
-Therefore, it may be desirable for the developer to be able to view the data being computed on the graphics card - a possibility often limited in terms of \textit{GPGPU}-technologies, possibly due to architectural differences in-between chip manufacturers.\\
-A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}), such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the \textit{GPU~Ocelot} compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance-losses.
-Other resons to emulate \textit{GPU}-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPGPU}-kernels, by the means of analyzing several software rasterizers.\\
-\\
-Furthermore, this material concerns inquiry into the \textit{DirectCompute}-framework on the \textit{Windows}-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the \textit{DirectX} standard software rasterizer, and utilizing the \textit{DirectX~11.1}-addition Microsoft~\textit{WARP}-technology (\textit{Windows~Advanced~Rasterization~Platform}) - which promises high-speed software emulation (see Microsoft's reference on \textit{WARP}\citeweb[]{warp}).\\
-\\
-This paper concludes that the performance losses inflicted by such emulation may be reduced enough for that emulation to be considered viable for retail use, as originally proposed by Microsoft (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, this study proposes use of Microsoft~\textit{WARP}-technology in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.\\
-\\
-As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.\\
-The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; the author's personal reflections surrounding future work in the area along with propositions of further study.
-
-% CONTRIBUTION
-\section{CONTRIBUTION}
-\label{sec:contribution}
-
-% CONTRIBUTION - OBJECT OF STUDY
-\subsection{Object~of~Study}
-\label{sec:contribution:objectofstudy}
-Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
-For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
-Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
-The operation was therefore considered suitable for the purpose of this experiment.\\
-\\
-The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware accelerated reference case.\\
-Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
-
-% CONTRIBUTION - METHOD OF STUDY
-\subsection{Method~of~Study}
-\label{sec:contribution:methodofstudy}
-In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\nameref{sec:contribution:subjectsofstudy}).
-The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
-\begin{enumerate*}
-	\item Randomize two matrices $A$ \& $B$ using desired data-type.
-	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
-	\item Start a synchronized high-precision timer.
-	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
-	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
-\end{enumerate*}
-The process described above make out the Method of this study.
-
-% CONTRIBUTION - SUBJECTS OF STUDY
-\subsection{Subjects~of~Study}
-\label{sec:contribution:subjectsofstudy}
-The \textit{GPU}-kernels described in Section~\nameref{sec:contribution:methodofstudy} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft \textit{DirectCompute}.
-These kernels are run using three types of acceleration technologies with varying strategies of \textit{GPU}-kernel emulation.
-These are comprised of the following:
-\subsubsection{Hardware-Acceleration~(GPU)}
-The execution of a \textit{DirectCompute}-kernel on a graphics card.
-This is the common case, and involves no emulation of the kernel.
-Thus, this case will act as a reference for the emulated Subjects.\\
-During hardware acceleration on the \textit{GPU}, one may expect high performance.
-\subsubsection{Software~Rasterization~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX} \textit{Reference~Device~Driver}.
-The \textit{Reference~Device~Driver} was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}).\\
-As the \textit{Reference~Device~Driver} is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
-
-\subsubsection{Windows~Advanced~Rasterization~Platform~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.
-The driver is based off the \textit{DirectX} \textit{Reference~Device~Driver} and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance.
-Microsoft describes \textit{WARP} as a high-performance software rasterizer, and recommends using the driver for retail applications, such as casual games (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
-\\
-These three \textit{DirectX} driver-types make out the Subjects of this study.
-
-% CONTRIBUTION - KERNELS
-\subsection{Kernels}
-\label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in Section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
-The kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-These kernels are presented below.
-\subsubsection{Matrix~mult.~w.~Thread~Blocks}
-A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.
-The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.
-Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in Section~\nameref{sec:contribution:equipment}.\\
-This kernel will be referred to as the Basic~Kernel throughout this material.
-
-\subsubsection{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-Similar to the previous kernel, but further optimized to utilize shared memory in order to reduce time-consuming reading of global memory, as presented by Kirk~\&~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to a core's \textit{L1}-cache.
-Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
-This kernel will be referred to as the Tiled~Kernel throughout this material.\\
-\\
-Furthermore, aforementioned kernels both support integer- and floating-point precision. These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
-
-% CONTRIBUTION - TOOLS
-\subsection{Tools}
-\label{sec:contribution:tools}
-The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation. These are presented below.
-
-\subsubsection{matrixgen}
-Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.\\
-\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A~\&~B$ into product matrix $Ref$.
-In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
-As \textit{matrixgen} utilizes Microsoft \texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.
-
-\subsubsection{experiment}
-Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from matrices $A~\&~B$ generated by \textit{matrixgen}.
-The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
-\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.
-As \textit{experiment} is developed using the \textit{Windows~8}~SDK, \textit{Windows~8.0} or later is required.
-Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
-
-\subsubsection{analytics}
-\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C~\&~Ref$.
-\textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
-In turn, analytics outputs this information to an intermediate file.\\
-\textit{analytics} is written in \texttt{C++}.\\
-\\
-These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
-This script, written in \texttt{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
-The source code manufactured for the sake of this study is freely available via an online \textit{Git} repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment.
-Furthermore, the complete results collected and used throughout this study are also available for download, and may be acquired for further analysis.
-
-% CONTRIBUTION - EQUIPMENT
-\subsection{Equipment}
-\label{sec:contribution:equipment}
-The results presented in this study is gathered from experiments performed on a system with the following specifications:
-\begin{description*}
-	\item[CPU]	Intel~Q9550~Quad~Core~$2.83$GHz
-	\item[GPU]	ATI~Radeon~HD~5800
-	\item[OS]	\tabto{0.35cm}\textit{Windows~8.0} % hack
-\end{description*}
-This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP} driver performs best on modern quad-core \textit{CPU}s (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-
-% CONTRIBUTION - PROCESS OF STUDY
-\subsection{Process~of~Study}
-\label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten.
-The product matrix of these matrices was then computed $100$ times for each configuration.
-In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel.
-For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization) was garnered along with precision-wize deviational data.\\
-The process described above was then repeated for integer- and floating point-precision.\\
-\\
-The measurements gathered from these executions make out the Results presented in this study.
-
-% CONTRIBUTION - RESULTS
-\subsection{Results}
-\label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~\textit{Reference~Device~Driver} from which \textit{WARP} is derived.
-Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$  					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$   					\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$   					\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
-\label{tab:contribution:results:summaryint}
-\end{table}
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{r|r|r|r|}
-	\cline{2-3}
-							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}}	\\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$  				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$   				\\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$  				\\ \hline
-\end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
-\label{tab:contribution:results:summaryfloat}
-\end{table}
-
-Using both integer- and floating point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.
-In Microsoft's guide on \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using \textit{WARP} - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
-The floating point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
-
-\begin{figure}[htb]
-\begin{center}
-	\resizebox{ \columnwidth }{!}{\input{../../msswarp}}
-	\caption{\textit{WARP} execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
-Values outside of their respective standard deviations have been clipped for the sake of clarity.}
-	\label{fig:contribution:results:warp:msswarp}
-\end{center}
-\end{figure}
-
-Integer precision calculation showed no sign of precisonal loss whatsoever.
-Meanwhile, all floating point-experiments experienced an equal average loss of computational precision.
-However, the data collected indicates no divergence in the precisional loss of respective Subject.
-The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\nameref{sec:contribution:methodofstudy}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
-\label{sec:contribution:results:computationalprecision}
-\begin{table}[hbt]
-\begin{center}
-	\begin{tabular}{|r|r|r|}
-		\hline
-		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
-		0.0   			& ~0.01  			& ~0.0025      		\\ \hline
-	\end{tabular}
-\caption {Average precisional deviations in floating~point-operations for all Subjects.}
-\label{tab:contribution:results:avgprecision}
-\end{center}
-\end{table}
-
-These results are expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.
-
-\newpage
-
-% CONCLUSION
-\section{CONCLUSION}
-\label{sec:conclusion}
-Based on the results presented in Section~\nameref{sec:contribution:results}, using \textit{WARP} to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{Reference~Device~Driver} in the same manner.
-Hence, if one were to compare the execution of \textit{WARP} \& the \textit{Reference~Device~Driver} side-by-side, and assume the same area of application, \textit{WARP} is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
-However, keeping in mind the major performance improvements offered by Microsoft~\textit{WARP}, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~\textit{Reference~Device~Driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas \textit{WARP} is intended for use in a broader sense (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.
-This calls for further inquiry into what the flaws of using Microsoft~\textit{WARP} may be.\\
-\\
-In conclusion; this study proposes, pursuant to the established performance of Microsoft~\textit{WARP}, that \textit{WARP}-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
-
-% CONCLUSION - FUTURE WORK
-\subsection{Future~Work}
-\label{sec:conclusion:futurework}
-For the sake of brevity, the author suggests complementary elaboration into double precision calculations in \textit{DirectCompute}-kernels, with the intent of examining whether or not the Subjects detailed in Section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
-\\
-Additionally, the use of more complex kernels in coagency with the \textit{WARP}-driver should be examined in order to study the effects of more demanding emulation on the \textit{CPU}.
-
-\newpage
-
-% BIBLIOGRAPHY
-\bibliographystyle{eurosis}
-\bibliographystyleweb{eurosis}
-
-\bibliography{eurosis}
-\bibliographyweb{eurosis}
-
-\newpage
-
-% APPENDIX
-\section{APPENDIX}
-\label{sec:appendix}
-
-% APPENDIX - MATRIX MULT. W. BLOCKS
-\subsection*{Matrix~mult.~w.~Blocks}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATBASIC_FX
-#define DV2549_FXS_MULTFLOATBASIC_FX
-
-#include <CommonFloat.fx>
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-
-	float sum = 0;
-	for( uint i = 0; i<aRows; i++ ) {
-		uint idxA = row*aRows+i;
-		uint idxB = col+bRows*i;
-		sum += mA[idxA]*mB[idxB];
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATBASIC_FX
-\end{lstlisting}
-
-\newpage
-\vspace*{0.08cm} % hack
-
-% APPENDIX - MATRIX MULT. W. BLOCKS & SHARED MEMORY
-\subsection*{Matrix~mult.~w.~Blocks~\&~Shared~Memory}
-\begin{lstlisting}
-#ifndef DV2549_FXS_MULTFLOATTILE_H
-#define DV2549_FXS_MULTFLOATTILE_H
-
-#include <CommonFloat.fx>
-
-groupshared float mAs[BLOCK_SIZE][BLOCK_SIZE];
-groupshared float mBs[BLOCK_SIZE][BLOCK_SIZE];
-
-[ numthreads( BLOCK_SIZE, BLOCK_SIZE, 1 ) ]
-void main(
-	uint3 tIdx : SV_GroupThreadID,
-	uint3 bIdx : SV_GroupID ) {
-	const uint row = bIdx.y*BLOCK_SIZE+tIdx.y;
-	const uint col = bIdx.x*BLOCK_SIZE+tIdx.x;
-
-	float sum = 0;
-	const uint blocks = ceil( 
-		(float)aRows/(float)BLOCK_SIZE );
-	for( uint i = 0; i<blocks; i++ ) {
-		mAs[tIdx.y][tIdx.x] = mA[ 
-			row*aRows+( i*BLOCK_SIZE+tIdx.x )];
-		mBs[tIdx.y][tIdx.x] = mB[ 
-			col+bRows*( i*BLOCK_SIZE+tIdx.y )];
-		GroupMemoryBarrierWithGroupSync();
-
-		for( uint j = 0; j<BLOCK_SIZE; j++ ) {
-			sum += 
-				mAs[tIdx.y][j]*mBs[j][tIdx.x];
-		}
-		GroupMemoryBarrierWithGroupSync();
-	}
-	if( row>=cRows || col>=cCols ) {
-		return;
-	}
-	mC[row*cRows+col] = sum;
-}
-
-#endif // DV2549_FXS_MULTFLOATTILE_H
-
-\end{lstlisting}
-
-\end{document}

### 2014-07-13 tex/GAME_HARD_01_ABSTRACT.tex

@@
 \begin{abstract}
-A convenient approach toward debugging or profiling \textit{GPU}-kernels is to emulate the kernel on a \textit{CPU}.
-This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
+A convenient approach toward more transparent debugging and profiling of \textit{GPU}-kernels is to simulate \textit{GPU}-bound workloads on \textit{CPU}s.
+This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications, or would require too many system resources to initialize.
 When performing such emulation, however, one may experience severe performance loss due to computational overhead.
@@
 As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}.
-Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such emulation can be considered viable for use in retail applications.
+Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on \textit{CPU}s may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such simulation may be considered viable for use in retail applications.
 \end{abstract}

### 2014-07-13 tex/GAME_HARD_01_ABSTRACT.tex
Various corrections in phrasing, grammar, and asome additions of concepts up to section Results.

@@
 \begin{abstract}
-A convenient approach toward more transparent debugging and profiling of \textit{GPU}-kernels is to simulate \textit{GPU}-bound workloads on \textit{CPU}s.
+A convenient approach toward more transparent debugging and profiling of GPU-kernels is to simulate GPU-bound workloads on CPUs.
 This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications, or would require too many system resources to initialize.
-When performing such emulation, however, one may experience severe performance loss due to computational overhead.
-Consequently, the subject of this study is performance variations between three different driver types from the \textit{DirectX}-framework; using \textit{DirectCompute} and the high speed software rasterizer \textit{WARP}.
-As such, the performance of \textit{WARP} is compared to that of traditional \textit{GPU} hardware acceleration and the standard driver for software rasterization - the \textit{Reference~Device~Driver}.
-Our experimental results show a major performance boost when compared to that of software rasterization using the \textit{Reference~Device~Driver}, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on \textit{CPU}s may be sufficiently amended by technologies, such as \textit{WARP}, to the degree that such simulation may be considered viable for use in retail applications.
+However, when simulating GPU-bound workloads on CPUs, one may experience severe performance losses due to computational overhead.
+Consequently, the subject of this study is performance variations between three different driver types from the DirectX framework; using DirectCompute and the high speed software rasterizer WARP (Windows~Advanced~Rasterization~Platform).
+As such, the performance of WARP is compared to that of traditional GPU hardware acceleration and the standard driver for software rasterization - the Reference~Device~Driver.
+Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that such simulation may be considered viable for extended use above and beyond that of in-development utilities.
 \end{abstract}
+% 'in-development utilities' - possibly poor phrasing

### 2014-07-13 tex/GAME_HARD_01_CONCLUSION.tex
Various corrections in phrasing, grammar, and asome additions of concepts up to section Results.

% GAME_HARD_01_CONCLUSION.tex

\section{CONCLUSION}
\label{sec:conclusion}
Based on the results presented in section~\nameref{sec:contribution:results}, using WARP to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{reference~device~driver} in the same manner.
Hence, if one were to compare the execution of WARP and the \textit{reference~device~driver} side-by-side, and assume the same area of application, WARP is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
However, keeping in mind the major performance improvements offered by Microsoft~WARP, it is important to consider that the two may be appropriate for different purposes.
The \textit{DirectX}~\textit{reference~device~driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas WARP is intended for use in a broader sense (see Microsoft's reference on WARP~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.
This calls for further inquiry into what the flaws of using Microsoft~WARP may be.\\
\\
In conclusion; this study proposes, pursuant to the established performance of Microsoft~WARP, that WARP-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.

% CONCLUSION - FUTURE WORK
\subsection{Future~Work}
\label{sec:conclusion:futurework}
For the sake of brevity, the author suggests complementary elaboration into double precision calculations in DirectCompute-kernels, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
\\
Additionally, the use of more complex kernels in coagency with the WARP-driver should be examined in order to study the effects of more demanding emulation on the CPU.

### 2014-07-13 tex/GAME_HARD_01_CONTRIBUTION.tex
Moved paper LaTeX code out of subdirectory and added GNUplot compilation into the build process. Build script now copies the compiled paper into the main directory.
Various corrections in phrasing, grammar, and asome additions of concepts up to section Results.

--- 2014-07-02 tex/gameon/GAME_HARD_01_CONTRIBUTION.tex
@@
 % CONTRIBUTION - OBJECT OF STUDY
-\subsection{Object~of~Study}
+\subsection{Object of Study}
 \label{sec:contribution:objectofstudy}
 Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
-For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~\&~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
-Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be computed from the expected data-type.
-The operation was therefore considered suitable for the purpose of this experiment.\\
-\\
-The dimension $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the \textit{GPU}, but yet reasonably sized to keep measurements collected by the means of emulation comparable to the hardware accelerated reference case.\\
+For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~and~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
+Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be easily established.
+The operation was therefore considered suitable for the purpose of this experiment.
+Furthermore, the matrix dimension of $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
 Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
@@
 % CONTRIBUTION - METHOD OF STUDY
-\subsection{Method~of~Study}
+\subsection{Method of Study}
 \label{sec:contribution:methodofstudy}
-In order to establish the Object~of~Study, $AB=C$, the experiment utilizes \textit{GPGPU}-kernels using which the result is calculated, in it’s entirety, in aforementioned kernel using some target Subject (see Section~\nameref{sec:contribution:subjectsofstudy}).
+In order to establish the Object~of~Study, $AB=C$, the experiment utilizes DirectCompute HLSL kernels using which the result matrix is calculated, in its entirety, using some device driver, or Subject (see section \nameref{sec:contribution:subjectsofstudy}).
 The experiment is devised of the following approximate steps in order to compile the Object~of~Study $AB=C$:
 \begin{enumerate*}
-	\item Randomize two matrices $A$ \& $B$ using desired data-type.
+	\item Randomize two matrices $A$ and $B$ of desired data-type (single floating point or integer).
 	\item Establish the product-matrix $AB=Ref$. The resulting matrix will be used as a reference matrix to verify the final result.
 	\item Start a synchronized high-precision timer.
-	\item Dispatch \textit{GPU}-kernel calculating the product matrix $AB=C$.
+	\item Dispatch DirectCompute program calculating the product matrix $AB=C$.
 	\item Stop the timer once the kernel has finished execution.
-	\item Establish possible deviation in-between resulting matrix $C$ and previously established matrix $Ref$.
+	\item Establish possible deviation between resulting matrix $C$ and previously established matrix $Ref$.
 \end{enumerate*}
-The process described above make out the Method of this study.
+The above process  makes out the Method of this study.
 
 % CONTRIBUTION - SUBJECTS OF STUDY
-\subsection{Subjects~of~Study}
+\subsection{Subjects of Study}
 \label{sec:contribution:subjectsofstudy}
-The \textit{GPU}-kernels described in Section~\nameref{sec:contribution:methodofstudy} are comprised of \texttt{HLSL}-syntax and are compiled \& executed using Microsoft \textit{DirectCompute}.
-These kernels are run using three types of acceleration technologies with varying strategies of \textit{GPU}-kernel emulation.
+The kernels described in section \nameref{sec:contribution:methodofstudy} are comprised of HLSL, compiled using Microsoft FXC, and executed using DirectCompute.
+The programs are run using three types of acceleration technologies with varying strategies of simulation.
 These are comprised of the following:
-\subsubsection{Hardware-Acceleration~(GPU)}
-The execution of a \textit{DirectCompute}-kernel on a graphics card.
-This is the common case, and involves no emulation of the kernel.
-Thus, this case will act as a reference for the emulated Subjects.\\
-During hardware acceleration on the \textit{GPU}, one may expect high performance.
-\subsubsection{Software~Rasterization~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using the \textit{DirectX} \textit{Reference~Device~Driver}.
-The \textit{Reference~Device~Driver} was developed for the purpose of testing and debugging, and is - although it does support some \textit{CPU}-optimizations - not intended to be used in retail applications (see Microsoft's reference on \textit{DirectX} Driver Types~\citeweb[]{drivertypes}).\\
-As the \textit{Reference~Device~Driver} is designed for the purpose of accuracy, rather than speed, one may expect poor performance.
 
-\subsubsection{Windows~Advanced~Rasterization~Platform~(CPU)}
-The emulated execution of a \textit{DirectCompute}-kernel using a special software rasterizer devised by Microsoft in their latest revision of the \textit{DirectX}-framework.
-The driver is based off the \textit{DirectX} \textit{Reference~Device~Driver} and uses thread pooling to distribute tasks efficiently on the \textit{CPU}, along with grouping execution in batches for optimum performance.
-Microsoft describes \textit{WARP} as a high-performance software rasterizer, and recommends using the driver for retail applications, such as casual games (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).\\
-As there are, as of yet, few studies performed on Microsoft~\textit{WARP}; expectations are unclear, but the driver is expected to perform better than standard software rasterization.\\
-\\
-These three \textit{DirectX} driver-types make out the Subjects of this study.
+\subsubsection{Hardware-Acceleration (GPU)}
+The execution of a DirectCompute-kernel on a graphics card.
+By utilizing a modern graphics card, hardware acceleration allows DirectX to utilize the throughput-oriented design of modern GPUs; maximizing FLOPS (Floating-point Operations Per Second) capacity.
+Being the common case; the methodology involves no simulation.
+Thus, measurements collected using this device driver acts as a reference for the simulated Subjects.
+
+\subsubsection{Software~Rasterization (CPU)}
+The simulation of a DirectCompute-kernel on the CPU using the DirectX~reference~device~driver.
+The reference rasterizer supports every Direct3D feature and is intended to be used for debugging- and verification purposes.
+Hence, the reference~device~driver is only available on systems where the DirectX~SDK is installed.
+As such, although the reference~device~driver does feature some optimization for CPU execution, the driver is not intended for outside-development use~\citeweb[]{drivertypes}.
+As the reference~device~driver is designed for the purpose of framework functionality verification, rather than speed, one may expect poor performance.
+
+\subsubsection{Windows Advanced Rasterization Platform (CPU)}
+The simulated execution of a DirectCompute kernel using a specially devised software rasterizer devised for high performance and full framework conformance by Microsoft in their latest version of the DirectX framework.
+Being based on the reference~device~driver, WARP utilizes thread pooling to distribute tasks efficiently on the CPU, along with grouping execution in batches for optimum performance.
+Furthermore, WARP uses JIT~(Just-In-Time) compilation to generate SSE2 and SSE4.1 SIMD~(Single Instruction, Multiple Data) instructions, in addition to x86-compatible native instructions to significantly speed up simulation of GPU-bound workloads~\citeweb[]{warp}.
+Having outperformed some low-end integrated GPUs according to Microsoft, and the device driver being included in Windows~7 and 8 runtimes, Microsoft recommends using the driver for retail applications, such as casual games~\citeweb[]{warp}.
+Although Microsoft has presented some WARP comparisons to hardware acceleration, there is no performance benchmark indicative of WARP performance in relation to the traditional reference~device~driver.
+As such, expectations on the performance of WARP is unclear, but the driver is expected to perform better than standard software rasterization.\\
+
+These three DirectX driver-types make out the Subjects of this study.
 
@@
 \label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in Section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
-The kernels have been implemented in accordance to the \textit{CUDA}-kernels as described by Kirk~\&~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-These kernels are presented below.
-\subsubsection{Matrix~mult.~w.~Thread~Blocks}
-A kernel producing $AB=C$ from two given matrices, writing back $C$ for further analysis.
-The kernel is executed with one thread for each element in the square matrices, and likewize each produce a lone element of the resulting matrix.
-Execution is performed in blocks of $16x16$ threads since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in Section~\nameref{sec:contribution:equipment}.\\
-This kernel will be referred to as the Basic~Kernel throughout this material.
+In addition to the Subject drivers mentioned in section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
+The kernels are implemented in accordance to the CUDA matrix multiplication kernels as described by Kirk~and~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
+Furthermore, aforementioned kernels both support integer- and floating-point precision.
+Descriptions of these kernels is presented below, and are complemented with source code under section~\nameref{sec:appendix}.
 
-\subsubsection{Matrix~mult.~w.~Thread~Blocks~\&~Shared~Memory}
-Similar to the previous kernel, but further optimized to utilize shared memory in order to reduce time-consuming reading of global memory, as presented by Kirk~\&~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.\\
-Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the \textit{CUDA}~\textit{GPGPU}-model may be applied onto multicore \textit{CPU}s, including locality-wize execution of logical thread-blocks (all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to a core's \textit{L1}-cache.
-Hence, the kernel is presented as a scenario due to the preconditions of \textit{WARP} - stating that a kernel optimized for \textit{GPU}-execution is likewize optimized for execution with \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
-Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment.\\
-This kernel will be referred to as the Tiled~Kernel throughout this material.\\
-\\
-Furthermore, aforementioned kernels both support integer- and floating-point precision.
-These kernels are attached, in their entirety, under Section~\nameref{sec:appendix}.
+\subsubsection{Matrix mult. w. Thread Blocks}
+A kernel producing $AB=C$ from two given matrices; writing back $C$ for further analysis.
+The program is executed with one thread for each element in the resulting square matrix, and likewise each produce a lone element of the product matrix.
+Execution is performed in blocks of $16x16$ threads, since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in section~\nameref{sec:contribution:equipment}.
+The kernel will be referred to as the Basic~Kernel throughout this material.
+
+\subsubsection{Matrix mult. w. Thread Blocks and Shared Memory}
+Similar to the previously described kernel, but optimized to utilize shared memory in order to reduce time-consuming access of global memory, as presented by Kirk~and~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.
+Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the CUDA GPGPU-model may be applied onto multicore CPUs, including locality-wise execution of logical thread blocks (that is; all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to the L1-cache of a CPU core.
+Hence, the kernel is presented as a scenario due to the preconditions of WARP, stating that a kernel optimized for GPU-execution is likewize optimized for execution with WARP~\citeweb[]{warp}.
+Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment in terms of memory access.
+The kernel will be referred to as the Tiled~Kernel throughout this material.
 
@@
 \label{sec:contribution:tools}
-The experiment process has been subdivided into three major components, all of which use Microsoft~\textit{Visual~Studio~2012} for compilation.
-These are presented below.
+The experiment process is subdivided into three major components, all of which are compiled using Visual~C++~2012.
+These programs are presented in detail below.
 
@@
 Denotes a utility developed to generate matrices of different dimensions and data-types.
-Furthermore, \textit{matrixgen} compiles the reference matrix $Ref$ used when comparing the result returned from the \textit{DirectCompute}-dispatch described in the next paragraph.\\
-\textit{matrixgen} is written in \texttt{C++} and utilizes \texttt{C++~AMP} to generate and multiply matrices $A~\&~B$ into product matrix $Ref$.
-In order to achieve random values in a \texttt{C++~AMP}-kernel the solution includes the random number generator-library \texttt{C++~AMP~RNG}.
-As \textit{matrixgen} utilizes Microsoft \texttt{C++~AMP}-technology, \textit{Windows~7} or later is required.
+In addition to randomly generating matrices, matrixgen also compiles the reference matrix $Ref$; used to validate the product matrix returned from the subsequent DirectCompute dispatch.
+The utility is written in C++ and utilizes C++~AMP to generate and multiply matrices $A$~and~$B$ into product matrix $Ref$.
+In order to produce random values in a C++~AMP program, the solution includes the random number generator library C++~AMP~RNG.
+As matrixgen utilizes Microsoft C++~AMP-technology, the utility requires Windows~7 or later in order to run.
 
 \subsubsection{experiment}
-Making out the primary component of the study, \textit{experiment} uses \textit{DirectCompute} to compile the product matrix $C$ from matrices $A~\&~B$ generated by \textit{matrixgen}.
-The application outputs data surrounding the execution of said kernel, such as it's execution time in milliseconds, to an intermediate file.\\
-\textit{experiment} is written in \texttt{C++} with it's respective \textit{DirectCompute}-kernels written in \texttt{HLSL}-syntax.
-As \textit{experiment} is developed using the \textit{Windows~8}~SDK, \textit{Windows~8.0} or later is required.
-Furthermore, \textit{experiment} requires a \textit{DirectX~11.0}- or \textit{DirectX~11.1}-compatible graphics card.
+Making out the primary component of the study, experiment uses DirectCompute to compile the product matrix $C$ from matrices $A$~and~$B$ compiled by matrixgen.
+The application outputs data surrounding the execution of the kernels, such as execution time in milliseconds, to an intermediate file.
+The utility is written in C++, with its respective DirectCompute kernels written in HLSL.
+As experiment is developed using the Windows~8~SDK, Windows~8.0 or later is required to run the tool.
+Furthermore, experiment requires a DirectX~11.0- or DirectX~11.1-compatible graphics card in order to produce the hardware accelerated reference case.
 
 \subsubsection{analytics}
-\textit{analytics} is a utility developed to compose data surrounding possible precisional deviations in-between matrices $C~\&~Ref$.
-\textit{analytics} compiles the minimum- and maximum-deviation encountered, as well as to calculate the standard deviation of said precisional deviation.
+A utility devised to compose data surrounding possible precisional deviation between matrices $C$~and~$Ref$.
+The tool, written in C++, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepency in produced product matrices.
 In turn, analytics outputs this information to an intermediate file.\\
-\textit{analytics} is written in \texttt{C++}.\\
-\\
+
 These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
-This script, written in \texttt{Python}, then compiles the assorted results of these applications and outputs a range of files suitably formatted for interpretation by \textit{Gnuplot}.\\
-The source code manufactured for the sake of this study is freely available via an online \textit{Git} repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment.
-Furthermore, the complete results collected and used throughout this study are also available for download, and may be acquired for further analysis.
+This script, written in Python, compiles the assorted results of respective program and outputs a range of files suitably formatted for interpretation by Gnuplot.
+The source code manufactured for the sake of this study is freely available via an online Git repository~\citeweb[]{github}, along with a guide on how to compile and run the solution in order to replicate the experiment.
+Furthermore, the complete results presented in this material are also available for download and may be acquired for further analysis.
 
@@
 \label{sec:contribution:equipment}
-The results presented in this study is gathered from experiments performed on a system with the following specifications:
+The results presented in the paper is gathered from experiments performed on a system with the following specifications:
 \begin{description*}
-	\item[CPU]	Intel~Q9550~Quad~Core~$2.83$GHz
-	\item[GPU]	ATI~Radeon~HD~5800
-	\item[OS]	\tabto{0.35cm}\textit{Windows~8.0} % hack
+	\item[CPU]	Intel Q9550 Quad Core $2.83$GHz
+	\item[GPU]	ATI Radeon HD 5800
+	\item[OS\phantom{U}] Windows~8.0
 \end{description*}
-This system setup was selected for use, for the purpose of this study, as Microsoft claims that the \textit{WARP} driver performs best on modern quad-core \textit{CPU}s (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
+This system setup was selected for use as Microsoft claims that the WARP device performs best on modern quad-core CPUs~\citeweb[]{warp}.
 
 % CONTRIBUTION - PROCESS OF STUDY
-\subsection{Process~of~Study}
+\subsection{Process of Study}
 \label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study - being $200x200$ matrices - were randomized with numbers in-between zero and ten.
-The product matrix of these matrices was then computed $100$ times for each configuration.
-In this way, the Basic~Kernel was run with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and \textit{WARP} - respectively, likewize as with the Tiled~Kernel.
-For each execution, data surrounding the dispatch-time of each kernel (meaning the time taken to execute corresponding kernel, regardless of program initialization) was garnered along with precision-wize deviational data.\\
-The process described above was then repeated for integer- and floating point-precision.\\
-\\
-The measurements gathered from these executions make out the Results presented in this study.
+For the purpose of this study, the Object~of~Study, being $200x200$ matrices of integer or floating point precision, is randomized with numbers between zero and ten.
+The product matrix of these matrices is subsequently computed $100$ times for each configuration.
+In this way, the Basic~Kernel is executed with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and WARP - respectively, likewize as with the Tiled~Kernel.
+For each execution, data surrounding the dispatch time of each kernel (regardless of program initialization) is garnered along with precision-wise deviational data.
+This process is repeated for integer- and floating point precision, in order to establish if there is any performance-wise disrepency betwixt them.
 
@@
 \label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~\textit{WARP}, compared to the performance of the \textit{DirectX}~\textit{Reference~Device~Driver} from which \textit{WARP} is derived.
+Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~WARP, compared to the performance of the \textit{DirectX}~\textit{reference~device~driver} from which WARP is derived.
 Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
@@
 
-Using both integer- and floating point-precision, the performance of \textit{WARP} is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~\&~\ref{tab:contribution:results:summaryfloat}.
-In Microsoft's guide on \textit{WARP} (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using \textit{WARP} - and vice versa.
+Using both integer- and floating point-precision, the performance of WARP is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}.
+In Microsoft's guide on WARP (see Microsoft's reference on WARP~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using WARP - and vice versa.
 However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
@@
 \begin{center}
-	\resizebox{ \columnwidth }{!}{\input{../../msswarp}}
-	\caption{\textit{WARP} execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
+	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
+	\caption{WARP execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
 Values outside of their respective standard deviations have been clipped for the sake of clarity.}
@@
 
-These results are expected as \textit{WARP} conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on \textit{WARP}~\citeweb[]{warp}).
+These results are expected as WARP conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on WARP~\citeweb[]{warp}).
 See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.

### 2014-07-13 tex/GAME_HARD_01_INTRODUCTION.tex
Various corrections in phrasing, grammar, and asome additions of concepts up to section Results.

% GAME_HARD_01_INTRODUCTION.tex

% INTRODUCTION
\section{INTRODUCTION}
\label{sec:introduction}
When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, and memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU-performance).
The increased utilization of complex GPU-kernels has brought forth the need of more extensive debugging- and profiling-options involving access of data that may be difficult to retrieve from hardware.
Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU-technologies, possibly due to architectural differences between chip manufacturers.
A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance implications.
Other resons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable~\citeweb[]{warp}.

This paper comprises an investigation into the performance of simulated GPGPU-kernels, in relation to hardware acceleration, by the means of analyzing several software rasterizers.
Accordingly, the material concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a GPGPU-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX~11 addition Microsoft~WARP-technology which promises high-speed software simulation~\citeweb[]{warp}.
The study concludes that performance losses inflicted by software rasterization may be sufficiently amended for simulation of GPU-bound workloads to be considered viable for extended use, as originally proposed by Microsoft~\citeweb[]{warp}.
Thus, this paper proposes use of WARP-like technologies in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.
As such, the study concerns the fields of simulation and GPU-technologies, with the purpose of facilitating debugging and profiling of GPU-kernels, whilst maintaining acceptable performance.
The remainder of this document presents the method and process to acquire the data used, the technologies using which it has been acquired, the results in and of their own, the conclusions based off the results and finally; personal reflections from the author with propositions of further study.

### 2014-07-20 tex/GAME_HARD_01_CONTRIBUTION.tex
Various corrections in phrasing, grammar, and asome additions of concepts up to section Results.

@@
 The operation was therefore considered suitable for the purpose of this experiment.
-Furthermore, the matrix dimension of $200x200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
+Furthermore, the matrix dimension of $200\times 200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
 Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
@@
 \label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study, being $200x200$ matrices of integer or floating point precision, is randomized with numbers between zero and ten.
+For the purpose of this study, the Object~of~Study, being $200\times 200$ matrices of integer or floating point precision, is randomized with numbers between zero and ten.
 The product matrix of these matrices is subsequently computed $100$ times for each configuration.
@@
 \label{sec:contribution:results}
-Based off the average of the collected execution times described in Section~\nameref{sec:contribution:processofstudy}; results indicate an improvement in the performance of the kernels when using Microsoft~WARP, compared to the performance of the \textit{DirectX}~\textit{reference~device~driver} from which WARP is derived.
-Table~\ref{tab:contribution:results:summaryint} demonstrates a performance gain with the Hardware~Accelerated Subject when utilizing shared memory amongst blocks; with varying results for the other Subjects - either increasing or decreasing execution time (see Table~\ref{tab:contribution:results:summaryfloat}).
+Considering average percentage decreases in execution time of $99.8\%-99.9\%$ presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}; results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
+These improvements, accounting for well-over two orders of magnitude, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten entire seconds.
 
-\begin{table}[hbt]
-\begin{center}
+\restylefloat*{table} % Corrects some weird caption error causing one of the side-by-side captions to be lost (http://tex.stackexchange.com/questions/152626/two-figures-side-by-side-caption-issue).
+
+\begin{table*}
+\parbox{.5\linewidth}{
+\centering
+\caption{Average execution time in milliseconds\\of a $200\times 200$ integer matrix multiplication.}
+\label{tab:contribution:results:summaryint}
 \begin{tabular}{r|r|r|r|}
@@
 	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$  					\\ \hline
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$	& $0.24$ 	& $-79.3\%$ \\ \hline \hline
 	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$	& $9866.40$	& $-15.0\%$ \\ \hline
 	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$	& $18.97$	& $+23.9\%$ \\ \hline
+        & \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
 \end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ integer matrix multiplication.}
-\label{tab:contribution:results:summaryint}
-\end{table}
-
-\begin{table}[hbt]
-\begin{center}
+}
+\hfill
+\parbox{.5\linewidth}{
+\centering
+\caption{Average execution time in milliseconds\\of a $200\times 200$ floating point matrix multiplication.}
+\label{tab:contribution:results:summaryfloat}
 \begin{tabular}{r|r|r|r|}
@@
 	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$  				\\ \hline
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$	& $0.22$	& $-71.4\%$ \\ \hline \hline
 	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$	& $10909.88$	& $+6.5\%$ \\ \hline
 	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$	& $17.44$	& $+23.9\%$ \\ \hline
+& \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
 \end{tabular}
-\end{center}
-\caption{Average execution time in milliseconds of a $200x200$ floating point matrix multiplication.}
-\label{tab:contribution:results:summaryfloat}
-\end{table}
+}
+\end{table*}
 
-Using both integer- and floating point-precision, the performance of WARP is impaired by the kernel utilizing shared memory according to the data presented in Tables~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}.
-In Microsoft's guide on WARP (see Microsoft's reference on WARP~\citeweb[]{warp}), the author claims that an application, if tuned to run efficiently on hardware, will run efficiently whilst emulated using WARP - and vice versa.
-However, the data collected for this study rather indicates an increase in execution time of $23.9$\%, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
-The floating point scenario of this effect is visualized in Figure~\ref{fig:contribution:results:warp:msswarp}.
+In terms of memory latency, table~\ref{tab:contribution:results:summaryint} demonstrates performance gains with the hardware accelerated Subject (when utilizing shared memory amongst blocks), with varying results for the other Subjects; either increasing or decreasing execution time (see table~\ref{tab:contribution:results:summaryfloat}).
+As such, applicable to both integer- and floating point-precision, the performance of WARP is impaired by the kernel utilizing shared memory.
+In the Microsoft guide on WARP~\citeweb[]{warp}, the author claims that an application tuned to run efficiently on hardware will run efficiently whilst simulated using WARP as well - and vice versa.
+However, the data collected for this study rather indicates an over $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
+This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by utilization of lower-latency shared memory.
+The floating point scenario of this effect is visualized in figure~\ref{fig:contribution:results:warp:msswarp}.
 
@@
 	\caption{WARP execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
-Values outside of their respective standard deviations have been clipped for the sake of clarity.}
+Values outside of their respective standard deviations are not presented for the sake of clarity.}
 	\label{fig:contribution:results:warp:msswarp}
@@
 
-Integer precision calculation showed no sign of precisonal loss whatsoever.
-Meanwhile, all floating point-experiments experienced an equal average loss of computational precision.
-However, the data collected indicates no divergence in the precisional loss of respective Subject.
-The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\nameref{sec:contribution:methodofstudy}, are presented in Table~\ref{tab:contribution:results:avgprecision}.
-\label{sec:contribution:results:computationalprecision}
-\begin{table}[hbt]
-\begin{center}
-	\begin{tabular}{|r|r|r|}
-		\hline
-		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
-		0.0   			& ~0.01  			& ~0.0025      		\\ \hline
-	\end{tabular}
-\caption {Average precisional deviations in floating~point-operations for all Subjects.}
-\label{tab:contribution:results:avgprecision}
-\end{center}
-\end{table}
+Analysis indicates no loss in precision between reference- and product matrices.
+Neither is there any recorded divergence in results compiled by respective Subjects.
+In hindsight, this behaviour may be expected as WARP conforms to the precision requirements of the Direct3D~$10$- and $10.1$-specification~\citeweb[]{warp}.
+See the Microsoft guide on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point precision in the Direct3D-framework.
+Accordingly, albeit not being explicitly developed for the purposes of precision, WARP performs equally as with the reference~device~driver.
+Whether or not this behaviour is replicated for double floating point precision is uncertain.
 
-These results are expected as WARP conforms to the precision requirements of the \textit{Direct3D~10}- and \textit{10.1}-specification (see Microsoft's reference on WARP~\citeweb[]{warp}).
-See Microsoft's documentation on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point-precision in the \textit{Direct3D}-framework.
+%\begin{table}[hbt]
+%\begin{center}
+%\begin{tabular}{r|r|r|r|}
+%	\cline{2-3}
+%	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+%	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$	& $0.24$ 	& $-79.3\%$ \\ \hline \hline
+%	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$	& $9866.40$	& $-15.0\%$ \\ \hline
+%	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$	& $18.97$	& $+23.9\%$ \\ \hline
+%        & \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
+%\end{tabular}
+%\end{center}
+%\caption{Average execution time in milliseconds of a $200\times 200$ integer matrix multiplication.}
+%\label{tab:contribution:results:summaryint}
+%\end{table}
+%
+%\begin{table}[hbt]
+%\begin{center}
+%\begin{tabular}{r|r|r|r|}
+%	\cline{2-3}
+%	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+%	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$	& $0.22$	& $-71.4\%$ \\ \hline \hline
+%	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$	& $10909.88$	& $+6.5\%$ \\ \hline
+%	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$	& $17.44$	& $+23.9\%$ \\ \hline
+%& \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
+%\end{tabular}
+%\end{center}
+%\caption{Average execution time in milliseconds of a $200\times 200$ floating point matrix multiplication.}
+%\label{tab:contribution:results:summaryfloat}
+%\end{table}

### 2014-07-20 tex/GAME_HARD_01_CONCLUSION.tex
Various corrections in phrasing, grammar, and and some additions of concepts up to section Future Work.

@@
 \label{sec:conclusion}
-Based on the results presented in section~\nameref{sec:contribution:results}, using WARP to emulate the kernels presented in this study has magnitudes greater performance than if one were to apply the \textit{DirectX}~\textit{reference~device~driver} in the same manner.
-Hence, if one were to compare the execution of WARP and the \textit{reference~device~driver} side-by-side, and assume the same area of application, WARP is superior in terms of execution time - assuming the same preconditions as those presented in this material.\\
-However, keeping in mind the major performance improvements offered by Microsoft~WARP, it is important to consider that the two may be appropriate for different purposes.
-The \textit{DirectX}~\textit{reference~device~driver} is primarily proposed by Microsoft as a debugging-/pre-silicon-development tool, whereas WARP is intended for use in a broader sense (see Microsoft's reference on WARP~\citeweb[]{warp}) - such as to render graphics for casual games - in addition to debugging and error-profiling purposes.
-This calls for further inquiry into what the flaws of using Microsoft~WARP may be.\\
-\\
-In conclusion; this study proposes, pursuant to the established performance of Microsoft~WARP, that WARP-like technologies are feasable for extended use in applications - for purposes other than debugging and profiling.
+Based on the findings of the experiment described in this paper, using WARP to simulate the presented kernels has magnitudes greater performance than if one were to apply the reference~device~driver in the same manner.
+Hence, if one were to compare the execution of WARP and the reference~device~driver side-by-side, and assume the same area of application, WARP is superior in terms of execution time presuming the same preconditions.
+
+However, keeping in mind the major performance improvements offered by WARP, it is important to consider that the two may be appropriate for different purposes.
+The reference~device~driver is primarily proposed by Microsoft as an accurate debugging-/pre-silicon-development tool (e.g., for the purposes of driver verification).
+On the contrary, WARP is intended for use in a broader sense, such as to render graphics for casual games - in addition to error-profiling purposes~\citeweb[]{warp}.
+Accordingly, the WARP device is included in the Direct3D~11~runtime for outside-development use.
+This indicates potential for extended use above and beyond that of debugging- and profiling purposes, since the WARP device may be utilized where the reference~device~driver would otherwise be orders of magnitude too slow.
+Such an example would be the isolation of hardware or graphics driver errors in high-performance graphics applications - often encountered by game developers.
+
+In conclusion; this study proposes, pursuant to the established performance of WARP, that WARP-like technologies are feasable for use where the reference~device~driver is too slow, when hardware is not available, and for extended purposes other than debugging and profiling.
 
@@
 \label{sec:conclusion:futurework}
-For the sake of brevity, the author suggests complementary elaboration into double precision calculations in DirectCompute-kernels, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.\\
-\\
-Additionally, the use of more complex kernels in coagency with the WARP-driver should be examined in order to study the effects of more demanding emulation on the CPU.
+The performance improvements of WARP, in comparison to the reference~device~driver, calls for further inquiry into what the flaws of using WARP may be.
+Microsoft lists, amongst other limitations latency-oriented CPUs may have over throughput oriented GPU architectures, memory bandwidth as a potential bottleneck for WARP-type acceleration methods~\citeweb[]{warp}.
+In accordance to the suspicions raised by Microsoft, it may be benificial to investigate the performance of WARP when such bottlenecks are stressed.
+Furthermore, the author suggests complementary elaboration into double precision calculations, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.
+
+Additionally, the use of more complex kernels in coagency with the WARP-driver should be examined in order to study the effects of more demanding simulation on the CPU.

### 2014-07-20 tex/GAME_HARD_01_BIOGRAPHY.tex
Added draft biography.

% GAME_HARD_01_BIOGRAPHY.tex

\section{AUTHOR BIOGRAPHY}
\label{sec:authorbiography}
\textbf{ERIC NILSSON} conducted his master thesis in Computer Science on graphics acceleration in virtual platforms ('Paravirtualizing OpenGL ES in Simics') in collaboration with Intel Corporation to obtain his M.Sc.E. from Blekinge Institute of Technology, where he majored in Software~Engineering.
In addition to his interest in the sciences, he has a keen interest in horror games; an engagement he pursues to the best of his ability.
Currently, Eric is involved with system simulation at Intel where he carries out his duties as a Software Engineer.\\

\href{mailto:erne09@student.bth.se}{erne09@student.bth.se}

### 2014-07-20 tex/GAME_HARD_01_ABSTRACT.tex
Conducted quick proof-reading.

@@
 A convenient approach toward more transparent debugging and profiling of GPU-kernels is to simulate GPU-bound workloads on CPUs.
-This approach is also applicable in situations where the target hardware is simply not available, as is often the case with server-side applications, or would require too many system resources to initialize.
+This approach is also applicable in situations where target hardware is simply not available, as is often the case with server-side applications, or would require too many system resources to initialize.
 However, when simulating GPU-bound workloads on CPUs, one may experience severe performance losses due to computational overhead.
-Consequently, the subject of this study is performance variations between three different driver types from the DirectX framework; using DirectCompute and the high speed software rasterizer WARP (Windows~Advanced~Rasterization~Platform).
-As such, the performance of WARP is compared to that of traditional GPU hardware acceleration and the standard driver for software rasterization - the Reference~Device~Driver.
+Consequently, the subject of this study is performance variations between three device drivers of the DirectX framework; using DirectCompute and the high speed software rasterizer WARP (Windows~Advanced~Rasterization~Platform).
+The performance of WARP is compared to that of traditional GPU hardware acceleration and the standard driver for software rasterization - the Reference~Device~Driver.
 Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that such simulation may be considered viable for extended use above and beyond that of in-development utilities.

### 2014-07-20 tex/GAME_HARD_01_CONCLUSION.tex
Conducted quick proof-reading.

@@
 Based on the findings of the experiment described in this paper, using WARP to simulate the presented kernels has magnitudes greater performance than if one were to apply the reference~device~driver in the same manner.
-Hence, if one were to compare the execution of WARP and the reference~device~driver side-by-side, and assume the same area of application, WARP is superior in terms of execution time presuming the same preconditions.
+Hence, if one were to compare the execution of WARP and the reference~device~driver side-by-side, and assume the same area of application, WARP is superior in terms of execution time.
 
@@
 This indicates potential for extended use above and beyond that of debugging- and profiling purposes, since the WARP device may be utilized where the reference~device~driver would otherwise be orders of magnitude too slow.
-Such an example would be the isolation of hardware or graphics driver errors in high-performance graphics applications - often encountered by game developers.
+Such an example would be the isolation of hardware or graphics driver errors in high-performance graphics applications - often encountered by video game developers.
 

### 2014-07-20 tex/GAME_HARD_01_CONTRIBUTION.tex
Removed blanked out backup tables.
Moved results tables to above that of section Process of Study to achieve better placement.
Moved visualization figure to beneath that of section Results (beneath all paragraphs).
Conducted quick proof-reading.

@@
 The operation was therefore considered suitable for the purpose of this experiment.
-Furthermore, the matrix dimension of $200\times 200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
+Furthermore, the matrix dimension $200\times 200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
 Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
@@
 	\item Start a synchronized high-precision timer.
-	\item Dispatch DirectCompute program calculating the product matrix $AB=C$.
+	\item Dispatch the DirectCompute program calculating the product matrix $AB=C$.
 	\item Stop the timer once the kernel has finished execution.
@@
 The execution of a DirectCompute-kernel on a graphics card.
-By utilizing a modern graphics card, hardware acceleration allows DirectX to utilize the throughput-oriented design of modern GPUs; maximizing FLOPS (Floating-point Operations Per Second) capacity.
+By utilizing a modern video card, hardware acceleration allows DirectX to utilize the throughput-oriented design of modern GPUs; maximizing FLOPS (FLoating-point Operations Per Second) capacity.
 Being the common case; the methodology involves no simulation.
@@
 \subsubsection{Windows Advanced Rasterization Platform (CPU)}
-The simulated execution of a DirectCompute kernel using a specially devised software rasterizer devised for high performance and full framework conformance by Microsoft in their latest version of the DirectX framework.
+The simulated execution of a DirectCompute kernel using a specially devised software rasterizer devoloped for high performance and full framework conformance by Microsoft in the latest version of DirectX.
 Being based on the reference~device~driver, WARP utilizes thread pooling to distribute tasks efficiently on the CPU, along with grouping execution in batches for optimum performance.
@@
 Having outperformed some low-end integrated GPUs according to Microsoft, and the device driver being included in Windows~7 and 8 runtimes, Microsoft recommends using the driver for retail applications, such as casual games~\citeweb[]{warp}.
-Although Microsoft has presented some WARP comparisons to hardware acceleration, there is no performance benchmark indicative of WARP performance in relation to the traditional reference~device~driver.
-As such, expectations on the performance of WARP is unclear, but the driver is expected to perform better than standard software rasterization.\\
+Although Microsoft has presented some performance comparisons to hardware acceleration, there is no performance benchmark indicative of WARP performance in relation to the reference~device~driver - the device commonly used for debugging and verification purposes.
+As such, expectations on the performance of WARP is unclear, but the driver is expected to perform better than the reference~device~driver from which it is derived.\\
 
-These three DirectX driver-types make out the Subjects of this study.
+These DirectX device drivers make out the Subjects of this study.
 
@@
 The kernels are implemented in accordance to the CUDA matrix multiplication kernels as described by Kirk~and~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-Furthermore, aforementioned kernels both support integer- and floating-point precision.
+Furthermore, aforementioned kernels accomodate both integer- and floating point precision.
 Descriptions of these kernels is presented below, and are complemented with source code under section~\nameref{sec:appendix}.
@@
 The program is executed with one thread for each element in the resulting square matrix, and likewise each produce a lone element of the product matrix.
-Execution is performed in blocks of $16x16$ threads, since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described in section~\nameref{sec:contribution:equipment}.
-The kernel will be referred to as the Basic~Kernel throughout this material.
+Execution is performed in blocks of $16\times 16$ threads, since this was the block dimension, out of samples $8$, $16$, and $32$, that performed optimally whilst hardware accelerated on the system described under section~\nameref{sec:contribution:equipment}.
+This program will be referred to as the Basic~Kernel throughout the material.
 
@@
 Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the CUDA GPGPU-model may be applied onto multicore CPUs, including locality-wise execution of logical thread blocks (that is; all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to the L1-cache of a CPU core.
-Hence, the kernel is presented as a scenario due to the preconditions of WARP, stating that a kernel optimized for GPU-execution is likewize optimized for execution with WARP~\citeweb[]{warp}.
+Hence, the kernel is presented as a scenario due to the preconditions of WARP, stating that a kernel optimized for GPU-execution is likewise optimized for execution with WARP~\citeweb[]{warp}.
 Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment in terms of memory access.
-The kernel will be referred to as the Tiled~Kernel throughout this material.
+The program will be referred to as the Tiled~Kernel throughout the material.
 
@@
 \label{sec:contribution:tools}
-The experiment process is subdivided into three major components, all of which are compiled using Visual~C++~2012.
+The experiment process is subdivided into three major components, all of which are compiled using Visual~C\texttt{++}~2012.
 These programs are presented in detail below.
@@
 In addition to randomly generating matrices, matrixgen also compiles the reference matrix $Ref$; used to validate the product matrix returned from the subsequent DirectCompute dispatch.
-The utility is written in C++ and utilizes C++~AMP to generate and multiply matrices $A$~and~$B$ into product matrix $Ref$.
-In order to produce random values in a C++~AMP program, the solution includes the random number generator library C++~AMP~RNG.
-As matrixgen utilizes Microsoft C++~AMP-technology, the utility requires Windows~7 or later in order to run.
+The utility is written in C\texttt{++} and utilizes C\texttt{++}~AMP to generate and multiply matrices $A$~and~$B$ into product matrix $Ref$.
+In order to produce random values in a C\texttt{++}~AMP program, the solution includes the random number generator library C\texttt{++}~AMP~RNG.
+As matrixgen utilizes Microsoft C\texttt{++}~AMP-technology, the utility requires Windows~7 or later in order to run.
 
 \subsubsection{experiment}
-Making out the primary component of the study, experiment uses DirectCompute to compile the product matrix $C$ from matrices $A$~and~$B$ compiled by matrixgen.
+Making out the primary component of the study, experiment uses DirectCompute to compile the product matrix $C$ from matrices $A$~and~$B$ (previously generated by matrixgen).
 The application outputs data surrounding the execution of the kernels, such as execution time in milliseconds, to an intermediate file.
-The utility is written in C++, with its respective DirectCompute kernels written in HLSL.
+The utility is written in C\texttt{++}, with its respective DirectCompute kernels devised in HLSL.
 As experiment is developed using the Windows~8~SDK, Windows~8.0 or later is required to run the tool.
@@
 A utility devised to compose data surrounding possible precisional deviation between matrices $C$~and~$Ref$.
-The tool, written in C++, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepency in produced product matrices.
+The tool, written in C\texttt{++}, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepency in produced product matrices.
 In turn, analytics outputs this information to an intermediate file.\\
 
-These three applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
+These applications are, in turn, run as subprocesses in a script specifying the various configurations and number of times to run each program.
 This script, written in Python, compiles the assorted results of respective program and outputs a range of files suitably formatted for interpretation by Gnuplot.
@@
 Furthermore, the complete results presented in this material are also available for download and may be acquired for further analysis.
-
-% CONTRIBUTION - EQUIPMENT
-\subsection{Equipment}
-\label{sec:contribution:equipment}
-The results presented in the paper is gathered from experiments performed on a system with the following specifications:
-\begin{description*}
-	\item[CPU] Intel Q9550 Quad Core $2.83$GHz
-	\item[GPU] ATI Radeon HD 5800
-	\item[OS\phantom{U}] Windows~8.0
-\end{description*}
-This system setup was selected for use as Microsoft claims that the WARP device performs best on modern quad-core CPUs~\citeweb[]{warp}.
-
-% CONTRIBUTION - PROCESS OF STUDY
-\subsection{Process of Study}
-\label{sec:contribution:processofstudy}
-For the purpose of this study, the Object~of~Study, being $200\times 200$ matrices of integer or floating point precision, is randomized with numbers between zero and ten.
-The product matrix of these matrices is subsequently computed $100$ times for each configuration.
-In this way, the Basic~Kernel is executed with each Subject~of~Study - being Hardware~Acceleration, Software~Rasterization and WARP - respectively, likewize as with the Tiled~Kernel.
-For each execution, data surrounding the dispatch time of each kernel (regardless of program initialization) is garnered along with precision-wise deviational data.
-This process is repeated for integer- and floating point precision, in order to establish if there is any performance-wise disrepency betwixt them.
-
-% CONTRIBUTION - RESULTS
-\subsection{Results}
-\label{sec:contribution:results}
-Considering average percentage decreases in execution time of $99.8\%-99.9\%$ presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}; results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
-These improvements, accounting for well-over two orders of magnitude, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten entire seconds.
 
@@
 
+% CONTRIBUTION - EQUIPMENT
+\subsection{Equipment}
+\label{sec:contribution:equipment}
+The results presented in the paper is gathered from experiments performed on a system with the following specifications:
+\begin{description*}
+	\item[CPU] Intel Q9550 Quad Core $2.83$GHz
+	\item[GPU] ATI Radeon HD 5800
+	\item[OS\phantom{U}] Windows~8.0
+\end{description*}
+This system setup was selected for use as Microsoft claims that the WARP device performs best on modern quad-core CPUs~\citeweb[]{warp}.
+
+% CONTRIBUTION - PROCESS OF STUDY
+\subsection{Process of Study}
+\label{sec:contribution:processofstudy}
+For the purpose of this study, the Object~of~Study, being $200\times 200$ matrices of integer or floating point precision, is randomized with numbers between zero and ten.
+The product matrix of these matrices is subsequently computed $100$ times for each configuration.
+In this way, the Basic~Kernel is executed with each Subject~of~Study - being Hardware~Acceleration, the reference~device~driver, and WARP - respectively, as is the Tiled~Kernel.
+For each execution, data surrounding the dispatch time of each kernel (regardless of program initialization) is garnered along with precision-wise deviational data.
+This process is repeated for integer- and floating point precision, in order to establish if there is any performance-wise disrepency betwixt them.
+
+% CONTRIBUTION - RESULTS
+\subsection{Results}
+\label{sec:contribution:results}
+Considering the average percentage decreases in execution time of $99.8-99.9\%$ presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}; results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
+These improvements, accounting for well-over two orders of magnitude, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten entire seconds.
+
 In terms of memory latency, table~\ref{tab:contribution:results:summaryint} demonstrates performance gains with the hardware accelerated Subject (when utilizing shared memory amongst blocks), with varying results for the other Subjects; either increasing or decreasing execution time (see table~\ref{tab:contribution:results:summaryfloat}).
@@
 The floating point scenario of this effect is visualized in figure~\ref{fig:contribution:results:warp:msswarp}.
+
+Analysis indicates no loss in precision between reference- and product matrices.
+Neither is there any recorded divergence in results compiled by respective Subjects.
+In hindsight, this behaviour may be expected as WARP conforms to the precision requirements of the Direct3D~$10$- and $10.1$-specification~\citeweb[]{warp}.
+See the Microsoft guide on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point precision in the Direct3D-framework.
+Accordingly, albeit not being explicitly developed for the purposes of precision, WARP performs equally as with the reference~device~driver.
+Whether or not this behaviour is replicated for double floating point precision is uncertain.
 
@@
 \end{figure}
-
-Analysis indicates no loss in precision between reference- and product matrices.
-Neither is there any recorded divergence in results compiled by respective Subjects.
-In hindsight, this behaviour may be expected as WARP conforms to the precision requirements of the Direct3D~$10$- and $10.1$-specification~\citeweb[]{warp}.
-See the Microsoft guide on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point precision in the Direct3D-framework.
-Accordingly, albeit not being explicitly developed for the purposes of precision, WARP performs equally as with the reference~device~driver.
-Whether or not this behaviour is replicated for double floating point precision is uncertain.
-
-%\begin{table}[hbt]
-%\begin{center}
-%\begin{tabular}{r|r|r|r|}
-%	\cline{2-3}
-%	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-%	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$	& $0.24$ 	& $-79.3\%$ \\ \hline \hline
-%	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$	& $9866.40$	& $-15.0\%$ \\ \hline
-%	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$	& $18.97$	& $+23.9\%$ \\ \hline
-%        & \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
-%\end{tabular}
-%\end{center}
-%\caption{Average execution time in milliseconds of a $200\times 200$ integer matrix multiplication.}
-%\label{tab:contribution:results:summaryint}
-%\end{table}
-%
-%\begin{table}[hbt]
-%\begin{center}
-%\begin{tabular}{r|r|r|r|}
-%	\cline{2-3}
-%	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-%	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$	& $0.22$	& $-71.4\%$ \\ \hline \hline
-%	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$	& $10909.88$	& $+6.5\%$ \\ \hline
-%	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$	& $17.44$	& $+23.9\%$ \\ \hline
-%& \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
-%\end{tabular}
-%\end{center}
-%\caption{Average execution time in milliseconds of a $200\times 200$ floating point matrix multiplication.}
-%\label{tab:contribution:results:summaryfloat}
-%\end{table}

### 2014-07-20 tex/GAME_HARD_01_INTRODUCTION.tex
Conducted quick proof-reading.

@@
 \label{sec:introduction}
-When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, and memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU-performance).
+When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, and memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU performance).
 The increased utilization of complex GPU-kernels has brought forth the need of more extensive debugging- and profiling-options involving access of data that may be difficult to retrieve from hardware.
-Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU-technologies, possibly due to architectural differences between chip manufacturers.
+Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU technologies (General-Purpose computing on Graphics Processing Units), possibly due to architectural differences between chip manufacturers.
 A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance implications.
@@
 This paper comprises an investigation into the performance of simulated GPGPU-kernels, in relation to hardware acceleration, by the means of analyzing several software rasterizers.
-Accordingly, the material concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a GPGPU-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX~11 addition Microsoft~WARP-technology which promises high-speed software simulation~\citeweb[]{warp}.
+Accordingly, the material concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a GPGPU-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX~11 addition Microsoft~WARP which promises high-speed software simulation~\citeweb[]{warp}.
 The study concludes that performance losses inflicted by software rasterization may be sufficiently amended for simulation of GPU-bound workloads to be considered viable for extended use, as originally proposed by Microsoft~\citeweb[]{warp}.
-Thus, this paper proposes use of WARP-like technologies in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.
+Thus, this paper proposes use of WARP-like technologies if graphics hardware is unavailable, not sufficient, or busy, in addition to act as an extension of the reference~device~driver as means to verify hardware- or driver-bound errors for complex GPU programs.
 As such, the study concerns the fields of simulation and GPU-technologies, with the purpose of facilitating debugging and profiling of GPU-kernels, whilst maintaining acceptable performance.

### 2014-07-26 tex/GAME_HARD_01_ABSTRACT.tex
Corrected company and institution names in bibliography, in addition to removing artifact .bibs.

@@
 \begin{abstract}
-A convenient approach toward more transparent debugging and profiling of GPU-kernels is to simulate GPU-bound workloads on CPUs.
+A convenient approach toward more transparent debugging and profiling of GPU-accelerated applications is to simulate GPU-bound workloads on CPUs.
 This approach is also applicable in situations where target hardware is simply not available, as is often the case with server-side applications, or would require too many system resources to initialize.
@@
 The performance of WARP is compared to that of traditional GPU hardware acceleration and the standard driver for software rasterization - the Reference~Device~Driver.
-Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that such simulation may be considered viable for extended use above and beyond that of in-development utilities.
+Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that simulation may be considered viable for extended use above and beyond that of in-development utilities.
 \end{abstract}

### 2014-07-26 tex/GAME_HARD_01_CONTRIBUTION.tex
Corrected company and institution names in bibliography, in addition to removing artifact .bibs.

@@
 Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be easily established.
-The operation was therefore considered suitable for the purpose of this experiment.
-Furthermore, the matrix dimension $200\times 200$ was selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
-Throughout this material, the compiled data will be referred to as $AB=C$, and thus make out the Object of this experiment.
+The operation is therefore considered suitable for the purpose of this experiment.
+Furthermore, the matrix dimension $200\times 200$ is selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
+Throughout this material, the compiled data is referred to as $AB=C$, and thus make out the Object of this experiment.
 

### 2014-07-26 tex/GAME_HARD_01_INTRODUCTION.tex
Corrected company and institution names in bibliography, in addition to removing artifact .bibs.

--- 2014-07-13 tex/GAME_HARD_01_INTRODUCTION.tex
@@
 \label{sec:introduction}
-When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, and memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences in-between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU-performance).
+When developing GPU-bound applications, careless additions to  program execution, such as branching, register use, or memory accesses, may induce substantial performance obstacles due to massively parallelized instruction sets and architectural differences between on-chip hardware (see Performance Considerations by Kirk~and~Hwu~\cite[ch.~6]{Kirk:2010:PMP:1841511} for an analysis on the volatility of GPU performance).
 The increased utilization of complex GPU-kernels has brought forth the need of more extensive debugging- and profiling-options involving access of data that may be difficult to retrieve from hardware.
-Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU-technologies, possibly due to architectural differences between chip manufacturers.
-A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework (see GPU~Ocelot~\citeweb[]{gpuocelot}), often in exchange for substantial performance implications.
-Other resons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwize unavailable~\citeweb[]{warp}.
+Therefore, it may be desirable for developers to access data being computed on the graphics card - a possibility often limited in terms of GPGPU (General-Purpose computing on Graphics Processing Units) technologies, possibly due to architectural differences between chip manufacturers.
+A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework~\citeweb[]{gpuocelot}, often in exchange for substantial performance implications.
+Other resons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwise unavailable~\citeweb[]{warp}.
 
 This paper comprises an investigation into the performance of simulated GPGPU-kernels, in relation to hardware acceleration, by the means of analyzing several software rasterizers.
-Accordingly, the material concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a GPGPU-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX~11 addition Microsoft~WARP-technology which promises high-speed software simulation~\citeweb[]{warp}.
+Accordingly, the material concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a GPGPU-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX~11 addition Microsoft~WARP which promises high-speed software rasterization~\citeweb[]{warp}.
 The study concludes that performance losses inflicted by software rasterization may be sufficiently amended for simulation of GPU-bound workloads to be considered viable for extended use, as originally proposed by Microsoft~\citeweb[]{warp}.
-Thus, this paper proposes use of WARP-like technologies in industry rasterization if graphics hardware is unavailable, not sufficient, or busy.
+Thus, this paper proposes use of WARP-like technologies if graphics hardware is unavailable, not sufficient, or busy, and to act as an extension of the reference~device~driver as means to verify hardware- or driver-bound errors for complex GPU programs.
 As such, the study concerns the fields of simulation and GPU-technologies, with the purpose of facilitating debugging and profiling of GPU-kernels, whilst maintaining acceptable performance.

### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Added arrows to tables to improve visualization of percentage decrease- and increases.

@@
 \label{sec:contribution:objectofstudy}
-Due to the nature of the experiment, it is important that the Object~of~Study is measurable and deterministic.
-For the purpose of this study, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~and~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
+Due to the nature of the study, it is important that the experiment process is measurable and deterministic.
+For the purpose of the experiment, the data computed corresponds to a square matrix multiplication, since such an operation is highly parallelizable, as demonstrated by Kirk~and~Hwu~\cite[ch.~3]{Kirk:2010:PMP:1841511}.
 Additionally, verifying the result of such an operation is trivial, and potential losses in computational precision may be easily established.
-The operation is therefore considered suitable for the purpose of this experiment.
+The operation is therefore considered suitable for the purpose of the study.
 Furthermore, the matrix dimension $200\times 200$ is selected for the respective matrices as it is big enough to execute efficiently on the GPU, but yet reasonably sized to keep simulated measurements comparable to those of the hardware accelerated reference case.
@@
 
+% Arrowhead command. Sets a tikz node for rendering an entire arrow.
+\newcommand\ah[2]{\tikz[remember picture,baseline]\node[inner sep=2pt,outer sep=0](#1){#2};}
+% Arrow command. Draws an arrow between two tikz nodes.
+\newcommand\arrow[2]{%
+\begin{tikzpicture}[remember picture, overlay, >=stealth, shift={(0,0)}]
+\draw[->] (#1) to (#2);
+\end{tikzpicture}%
+}
+
 \restylefloat*{table} % Corrects some weird caption error causing one of the side-by-side captions to be lost (http://tex.stackexchange.com/questions/152626/two-figures-side-by-side-caption-issue).
@@
 \parbox{.5\linewidth}{
-\centering
-\caption{Average execution time in milliseconds\\of a $200\times 200$ integer matrix multiplication.}
+\centering % Consider removing?
+\caption{Average execution time in milliseconds\\of a $200\times 200$ integer matrix multiplication and\\corresponding percentage decrease- and increases.}
 \label{tab:contribution:results:summaryint}
@@
 	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$	& $0.24$ 	& $-79.3\%$ \\ \hline \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$	& $9866.40$	& $-15.0\%$ \\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$	& $18.97$	& $+23.9\%$ \\ \hline
-        & \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$1.16$}	& \ah{hf1}{\phantom{000}$0.24$}\ah{spc}{} 	& \ah{spc}{$-79.3\%$} \\ \hline \hline
+	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh2}{}\ah{hh2}{$11610.02$}	& \ah{hf2}{$9866.40$}\ah{vh1}{}	& \ah{spc}{$-15.0\%$} \\ \hline
+	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}	& \ah{hf3}{\phantom{00}$18.97$}\ah{vf1}{}	& \ah{spc}{$+23.9\%$} \\ \hline
+        & \multicolumn{1}{|c|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|c|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
 \end{tabular}
+\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+\arrow{hh2}{hf2}
+\arrow{hh3}{hf3}
+\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+\arrow{vh2}{vf2}
 }
@@
 \centering
-\caption{Average execution time in milliseconds\\of a $200\times 200$ floating point matrix multiplication.}
+\caption{Average execution time in milliseconds of\\a $200\times 200$ floating point matrix multiplication and\\ corresponding percentage decrease- and increases.}
 \label{tab:contribution:results:summaryfloat}
@@
 	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
-	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$	& $0.22$	& $-71.4\%$ \\ \hline \hline
-	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$	& $10909.88$	& $+6.5\%$ \\ \hline
-	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$	& $17.44$	& $+23.9\%$ \\ \hline
-& \multicolumn{1}{|r|}{$-99.9\%$} & \multicolumn{1}{|r|}{$-99.8\%$} \\ \cline{2-3}
+	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$0.77$}	& \ah{hf1}{\phantom{0000}$0.22$}\ah{spc}{}	& \ah{spc}{$-71.4\%$} \\ \hline \hline
+	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh1}{}\ah{hh2}{$10247.03$}	& \ah{hf2}{$10909.88$}\ah{vh2}{}	& \ah{spc}{$+6.5\%$} \\ \hline
+	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf1}{}\phantom{000}\ah{hh3}{$14.08$}	& \ah{hf3}{\phantom{000}$17.44$}\ah{vf2}{}	& \ah{spc}{$+23.9\%$} \\ \hline
+& \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
 \end{tabular}
+\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+\arrow{hh2}{hf2}
+\arrow{hh3}{hf3}
+\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+\arrow{vh2}{vf2}
 }

### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Cleaned up GNUplot script.

@@
 	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}	& \ah{hf3}{\phantom{00}$18.97$}\ah{vf1}{}	& \ah{spc}{$+23.9\%$} \\ \hline
-        & \multicolumn{1}{|c|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|c|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
+        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
 \end{tabular}

### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Improved upon visualization caption.

@@
 	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
-	\caption{WARP execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations.
-Values outside of their respective standard deviations are not presented for the sake of clarity.}
+	\caption{Execution time using WARP with floating point-precision for the Basic- and Tiled kernels, indicated by their respective mean- and seperated by standard deviation values.
+Samples outside of respective standard deviation are not presented.}
 	\label{fig:contribution:results:warp:msswarp}

### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Stylized gnuplot visualization.

@@
 	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
-	\caption{Execution time using WARP with floating point-precision for the Basic- and Tiled kernels, indicated by their respective mean- and seperated by standard deviation values.
+	\caption{Execution time using WARP with floating point-precision for the Basic and Tiled kernels, indicated by their respective mean- and seperated by standard deviation values.
 Samples outside of respective standard deviation are not presented.}

### 2014-08-03 tex/GAME_HARD_01_CONTRIBUTION.tex
Added order of magnitude comparison elaboration under section Results.

@@
 \label{sec:contribution:results}
-Considering the average percentage decreases in execution time of $99.8-99.9\%$ presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}; results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
-These improvements, accounting for well-over two orders of magnitude, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten entire seconds.
+Considering the average percentage decreases in execution time of $99.8$ to $99.9\%$ (presented in table~\ref{tab:contribution:results:summaryint}~and~\ref{tab:contribution:results:summaryfloat}); results indicate significant improvements in the performance of both kernels when using WARP, compared to that of the the reference~device~driver.
+These improvements, accounting for three orders of magnitude on average, induce an execution time spanning tenths of milliseconds; a considerable advance from that of roughly ten seconds.
+The measurements indicate that the reference~device~driver is $4$~to~$5$ orders of magnitude slower than the hardware accelerated reference case, depending on whether or not the kernel utilizes shared memory to accelerate memory accesses on the video card.
+Meanwhile, the WARP device driver performs but $1$~to~$2$ orders of magnitude worse than hardware acceleration, also depending on shared memory utilization.
 
 In terms of memory latency, table~\ref{tab:contribution:results:summaryint} demonstrates performance gains with the hardware accelerated Subject (when utilizing shared memory amongst blocks), with varying results for the other Subjects; either increasing or decreasing execution time (see table~\ref{tab:contribution:results:summaryfloat}).
-As such, applicable to both integer- and floating point-precision, the performance of WARP is impaired by the kernel utilizing shared memory.
+As such, applicable to both integer- and floating point precision, the performance of WARP is impaired by the kernel utilizing shared memory.
 In the Microsoft guide on WARP~\citeweb[]{warp}, the author claims that an application tuned to run efficiently on hardware will run efficiently whilst simulated using WARP as well - and vice versa.
-However, the data collected for this study rather indicates an over $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
-This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by utilization of lower-latency shared memory.
+However, the collected data rather indicate a roughly $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
+This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by lower-latency shared memory.
 The floating point scenario of this effect is visualized in figure~\ref{fig:contribution:results:warp:msswarp}.

### 2014-08-03 tex/GAME_HARD_01_CONCLUSION.tex
Corrected spelling throughout document.

@@
 
-In conclusion; this study proposes, pursuant to the established performance of WARP, that WARP-like technologies are feasable for use where the reference~device~driver is too slow, when hardware is not available, and for extended purposes other than debugging and profiling.
+In conclusion; this study proposes, pursuant to the established performance of WARP, that WARP-like technologies are feasible for use where the reference~device~driver is too slow, when hardware is not available, and for extended purposes other than debugging and profiling.
 
@@
 Microsoft lists, amongst other limitations latency-oriented CPUs may have over throughput oriented GPU architectures, memory bandwidth as a potential bottleneck for WARP-type acceleration methods~\citeweb[]{warp}.
-In accordance to the suspicions raised by Microsoft, it may be benificial to investigate the performance of WARP when such bottlenecks are stressed.
+In accordance to the suspicions raised by Microsoft, it may be beneficial to investigate the performance of WARP when such bottlenecks are stressed.
 Furthermore, the author suggests complementary elaboration into double precision calculations, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.

### 2014-08-03 tex/GAME_HARD_01_CONTRIBUTION.tex
Corrected spelling throughout document.

@@
 \subsubsection{Windows Advanced Rasterization Platform (CPU)}
-The simulated execution of a DirectCompute kernel using a specially devised software rasterizer devoloped for high performance and full framework conformance by Microsoft in the latest version of DirectX.
+The simulated execution of a DirectCompute kernel using a specially devised software rasterizer developed for high performance and full framework conformance by Microsoft in the latest version of DirectX.
 Being based on the reference~device~driver, WARP utilizes thread pooling to distribute tasks efficiently on the CPU, along with grouping execution in batches for optimum performance.
 Furthermore, WARP uses JIT~(Just-In-Time) compilation to generate SSE2 and SSE4.1 SIMD~(Single Instruction, Multiple Data) instructions, in addition to x86-compatible native instructions to significantly speed up simulation of GPU-bound workloads~\citeweb[]{warp}.
-Having outperformed some low-end integrated GPUs according to Microsoft, and the device driver being included in Windows~7 and 8 runtimes, Microsoft recommends using the driver for retail applications, such as casual games~\citeweb[]{warp}.
+Having outperformed some low-end integrated GPUs according to Microsoft, and the device driver being included in Windows~7 and 8 run-times, Microsoft recommends using the driver for retail applications, such as casual games~\citeweb[]{warp}.
 Although Microsoft has presented some performance comparisons to hardware acceleration, there is no performance benchmark indicative of WARP performance in relation to the reference~device~driver - the device commonly used for debugging and verification purposes.
@@
 The kernels are implemented in accordance to the CUDA matrix multiplication kernels as described by Kirk~and~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
-Furthermore, aforementioned kernels accomodate both integer- and floating point precision.
+Furthermore, aforementioned kernels accommodate both integer- and floating point precision.
 Descriptions of these kernels is presented below, and are complemented with source code under section~\nameref{sec:appendix}.
@@
 Hence, the kernel is presented as a scenario due to the preconditions of WARP, stating that a kernel optimized for GPU-execution is likewise optimized for execution with WARP~\citeweb[]{warp}.
-Thus, we investigate a more optimized kernel to see whether or not this behaviour may be replicated in the experiment in terms of memory access.
+Thus, we investigate a more optimized kernel to see whether or not this behavior may be replicated in the experiment in terms of memory access.
 The program will be referred to as the Tiled~Kernel throughout the material.
@@
 A utility devised to compose data surrounding possible precisional deviation between matrices $C$~and~$Ref$.
-The tool, written in C\texttt{++}, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepency in produced product matrices.
+The tool, written in C\texttt{++}, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepancy in produced product matrices.
 In turn, analytics outputs this information to an intermediate file.\\
@@
 In this way, the Basic~Kernel is executed with each Subject~of~Study - being Hardware~Acceleration, the reference~device~driver, and WARP - respectively, as is the Tiled~Kernel.
-For each execution, data surrounding the dispatch time of each kernel (regardless of program initialization) is garnered along with precision-wise deviational data.
-This process is repeated for integer- and floating point precision, in order to establish if there is any performance-wise disrepency betwixt them.
+For each execution, data surrounding the dispatch time of each kernel (regardless of program initialization) is garnered along with precision-wise deviation data.
+This process is repeated for integer- and floating point precision, in order to establish if there is any performance-wise discrepancy betwixt them.
 
@@
 In the Microsoft guide on WARP~\citeweb[]{warp}, the author claims that an application tuned to run efficiently on hardware will run efficiently whilst simulated using WARP as well - and vice versa.
-However, the collected data rather indicate a roughly $20\%$ percentual increase in execution time, independant of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
+However, the collected data rather indicate a roughly $20\%$ percentual increase in execution time, independent of precision, even though the same kernel accelerates the hardware accelerated Subject by roughly $70$\%.
 This demonstrates that that the capabilities of WARP do not extend to memory latency optimization by lower-latency shared memory.
@@
 Neither is there any recorded divergence in results compiled by respective Subjects.
-In hindsight, this behaviour may be expected as WARP conforms to the precision requirements of the Direct3D~$10$- and $10.1$-specification~\citeweb[]{warp}.
+In hindsight, this behavior may be expected as WARP conforms to the precision requirements of the Direct3D~$10$- and $10.1$-specification~\citeweb[]{warp}.
 See the Microsoft guide on Floating-point Rules~\citeweb[]{floatingpointrules} for more information surrounding floating point precision in the Direct3D-framework.
 Accordingly, albeit not being explicitly developed for the purposes of precision, WARP performs equally as with the reference~device~driver.
-Whether or not this behaviour is replicated for double floating point precision is uncertain.
+Whether or not this behavior is replicated for double floating point precision is uncertain.
 
@@
 	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
-	\caption{Execution time using WARP with floating point-precision for the Basic and Tiled kernels, indicated by their respective mean- and seperated by standard deviation values.
+	\caption{Execution time using WARP with floating point-precision for the Basic and Tiled kernels, indicated by their respective mean- and separated by standard deviation values.
 Samples outside of respective standard deviation are not presented.}

### 2014-08-03 tex/GAME_HARD_01_ABSTRACT.tex
Conducted proof-reading of article.

@@
 The performance of WARP is compared to that of traditional GPU hardware acceleration and the standard driver for software rasterization - the Reference~Device~Driver.
-Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that simulation may be considered viable for extended use above and beyond that of in-development utilities.
+Experimental results show a major performance boost when compared to that of software rasterization using the reference~device~driver, indicating that performance losses traditionally obstructing simulation of throughput-oriented workloads on CPUs may be sufficiently amended by technologies, such as WARP, to the degree that simulation may be considered viable for extended use above and beyond that of current in-development utilities.
 \end{abstract}
-% 'in-development utilities' - possibly poor phrasing

### 2014-08-03 tex/GAME_HARD_01_CONCLUSION.tex
Conducted proof-reading of article.

@@
 The reference~device~driver is primarily proposed by Microsoft as an accurate debugging-/pre-silicon-development tool (e.g., for the purposes of driver verification).
-On the contrary, WARP is intended for use in a broader sense, such as to render graphics for casual games - in addition to error-profiling purposes~\citeweb[]{warp}.
+On the contrary, WARP is intended for use in a broader sense, such as to render graphics for casual games, in addition to error-profiling purposes~\citeweb[]{warp}.
 Accordingly, the WARP device is included in the Direct3D~11~runtime for outside-development use.
@@
 
-In conclusion; this study proposes, pursuant to the established performance of WARP, that WARP-like technologies are feasible for use where the reference~device~driver is too slow, when hardware is not available, and for extended purposes other than debugging and profiling.
+In conclusion; this study proposes, pursuant to the established performance of WARP, that WARP-like technologies are feasible for use where the reference~device~driver is too slow, such as verification of advanced computer graphics, or when hardware is not available, such as the acceleration of graphics in virtual platforms.
 
@@
 In accordance to the suspicions raised by Microsoft, it may be beneficial to investigate the performance of WARP when such bottlenecks are stressed.
-Furthermore, the author suggests complementary elaboration into double precision calculations, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.
+Furthermore, the author suggests complementary elaboration into double floating point precision calculations, with the intent of examining whether or not the Subjects detailed in section~\nameref{sec:contribution:subjectsofstudy} may have differentiating effects on computational precision.
 
-Additionally, the use of more complex kernels in coagency with the WARP-driver should be examined in order to study the effects of more demanding simulation on the CPU.
+Additionally, the use of more complex kernels in coagency with the WARP-driver should be examined in order to study the effects of more demanding simulation on CPUs.

### 2014-08-03 tex/GAME_HARD_01_CONTRIBUTION.tex
Conducted proof-reading of article.

@@
 \label{sec:contribution:subjectsofstudy}
-The kernels described in section \nameref{sec:contribution:methodofstudy} are comprised of HLSL, compiled using Microsoft FXC, and executed using DirectCompute.
+The kernels described in section \nameref{sec:contribution:methodofstudy} are comprised of HLSL, compiled using Microsoft FXC, and executed using the Direct3D compute shader pipeline stage.
 The programs are run using three types of acceleration technologies with varying strategies of simulation.
@@
 Furthermore, WARP uses JIT~(Just-In-Time) compilation to generate SSE2 and SSE4.1 SIMD~(Single Instruction, Multiple Data) instructions, in addition to x86-compatible native instructions to significantly speed up simulation of GPU-bound workloads~\citeweb[]{warp}.
-Having outperformed some low-end integrated GPUs according to Microsoft, and the device driver being included in Windows~7 and 8 run-times, Microsoft recommends using the driver for retail applications, such as casual games~\citeweb[]{warp}.
+Having outperformed some low-end integrated GPUs, according to Microsoft, and the device driver being included in Windows~7 and 8 run-times, Microsoft recommends using the driver for retail applications such as casual games~\citeweb[]{warp}.
 Although Microsoft has presented some performance comparisons to hardware acceleration, there is no performance benchmark indicative of WARP performance in relation to the reference~device~driver - the device commonly used for debugging and verification purposes.
-As such, expectations on the performance of WARP is unclear, but the driver is expected to perform better than the reference~device~driver from which it is derived.\\
+As such, expectations on the performance of WARP is unclear but the driver is expected to perform faster than the reference~device~driver, from which it is derived, due to its promised optimizations and high-speed focus.\\
 
@@
 \label{sec:contribution:kernels}
-In addition to the Subject drivers mentioned in section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of optimization are examined.
-The kernels are implemented in accordance to the CUDA matrix multiplication kernels as described by Kirk~and~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
+In addition to the Subject drivers mentioned in section~\nameref{sec:contribution:subjectsofstudy}, two kernels with varying level of memory access optimization are examined.
+The programs are implemented in accordance to the CUDA matrix multiplication kernels as described by Kirk~and~Hwu~\cite[p.~67, p.~87]{Kirk:2010:PMP:1841511}.
 Furthermore, aforementioned kernels accommodate both integer- and floating point precision.
-Descriptions of these kernels is presented below, and are complemented with source code under section~\nameref{sec:appendix}.
+Descriptions of these kernels are presented below and complemented with source code under section~\nameref{sec:appendix}.
 
@@
 Similar to the previously described kernel, but optimized to utilize shared memory in order to reduce time-consuming access of global memory, as presented by Kirk~and~Hwu~\cite[p.~77-93]{Kirk:2010:PMP:1841511}.
-Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the CUDA GPGPU-model may be applied onto multicore CPUs, including locality-wise execution of logical thread blocks (that is; all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to the L1-cache of a CPU core.
+Stratton~et~al.~\cite[p.~1-3]{Stratton:2008:MEI:1485701.1485703} instructs that the CUDA GPGPU-model may be applied onto multicore CPUs, including locality-wise execution of logical thread blocks (that is; all threads in a block limited to a single core), with the utilization of local- and shared-memory approximately corresponding to the L1- and L2-caches of a CPU core.
 Hence, the kernel is presented as a scenario due to the preconditions of WARP, stating that a kernel optimized for GPU-execution is likewise optimized for execution with WARP~\citeweb[]{warp}.
-Thus, we investigate a more optimized kernel to see whether or not this behavior may be replicated in the experiment in terms of memory access.
-The program will be referred to as the Tiled~Kernel throughout the material.
+Thus, we investigate a more optimized kernel to see whether or not this behavior may be replicated in the experiment in terms of memory access optimization.
+The program is referred to as the Tiled~Kernel throughout this material.
 
@@
 The experiment process is subdivided into three major components, all of which are compiled using Visual~C\texttt{++}~2012.
-These programs are presented in detail below.
+These tools are presented in detail below.
 
 \subsubsection{matrixgen}
-Denotes a utility developed to generate matrices of different dimensions and data-types.
+Denotes a utility developed to generate matrices of different dimension and precision.
 In addition to randomly generating matrices, matrixgen also compiles the reference matrix $Ref$; used to validate the product matrix returned from the subsequent DirectCompute dispatch.
@@
 In order to produce random values in a C\texttt{++}~AMP program, the solution includes the random number generator library C\texttt{++}~AMP~RNG.
-As matrixgen utilizes Microsoft C\texttt{++}~AMP-technology, the utility requires Windows~7 or later in order to run.
+As the utility utilizes Microsoft C\texttt{++}~AMP-technology, the utility requires Windows~7 or later in order to run.
 
 \subsubsection{experiment}
-Making out the primary component of the study, experiment uses DirectCompute to compile the product matrix $C$ from matrices $A$~and~$B$ (previously generated by matrixgen).
+Making out the primary component of the study, experiment uses DirectCompute technology to compile the product matrix $C$ from matrices $A$~and~$B$ (previously generated by matrixgen).
 The application outputs data surrounding the execution of the kernels, such as execution time in milliseconds, to an intermediate file.
 The utility is written in C\texttt{++}, with its respective DirectCompute kernels devised in HLSL.
-As experiment is developed using the Windows~8~SDK, Windows~8.0 or later is required to run the tool.
-Furthermore, experiment requires a DirectX~11.0- or DirectX~11.1-compatible graphics card in order to produce the hardware accelerated reference case.
+Since the tool is developed using the Windows~8~SDK, Windows~8.0 or later is required to run the tool.
+Furthermore, the utility requires a DirectX~11.0- or DirectX~11.1-compatible graphics card in order to produce the hardware accelerated reference case.
 
@@
 The tool, written in C\texttt{++}, compiles the minimum- and maximum  deviation encountered, as well as to calculate the standard deviation of any precisional discrepancy in produced product matrices.
-In turn, analytics outputs this information to an intermediate file.\\
+In turn, the program outputs this information to an intermediate file.\\
 
@@
 \label{sec:contribution:equipment}
-The results presented in the paper is gathered from experiments performed on a system with the following specifications:
+The results presented in the paper are gathered from experiments performed on a system with the following specifications:
 \begin{description*}
@@
 The measurements indicate that the reference~device~driver is $4$~to~$5$ orders of magnitude slower than the hardware accelerated reference case, depending on whether or not the kernel utilizes shared memory to accelerate memory accesses on the video card.
-Meanwhile, the WARP device driver performs but $1$~to~$2$ orders of magnitude worse than hardware acceleration, also depending on shared memory utilization.
+Meanwhile, the WARP device driver performs but $1$~to~$2$ orders of magnitude worse than hardware acceleration, also depending on hardware shared memory utilization.
 
@@
 	\caption{Execution time using WARP with floating point-precision for the Basic and Tiled kernels, indicated by their respective mean- and separated by standard deviation values.
-Samples outside of respective standard deviation are not presented.}
+Samples outside of respective standard deviation are not presented in this visualization.}
 	\label{fig:contribution:results:warp:msswarp}

### 2014-08-17 dv2549.py
Removed source-code from paper fork.

@@ -1,192 +1,0 @@
-# http://bit.ly/18px6NF
-
-import os
-import sys
-import getopt
-import subprocess
-
-# Relative paths
-PATH_TO_EXPERIMENT	= "experiment.exe"
-PATH_TO_MATRIXGEN	= "../../matrixgen/Release/matrixgen.exe"
-PATH_TO_ANALYTICS	= "../../analytics/Release/analytics.exe"
-PATH_TO_RESEXP		= "../../../res/" + "resExperiment.res"
-PATH_TO_RESANA		= "../../../res/" + "resAnalytics.res"
-PATH_TO_EXPRES		= "../../../res/"
-def GetPath( rel ): # Relative to absolute path.
-	return os.path.abspath( rel )
-
-# Classes
-class ResExperiment:
-	def __init__( self ):
-		self.equal 		= True
-		self.timeMs 	= 0.0
-		self.precision 	= 0
-		self.rows		= 0
-		self.cols		= 0
-class ResAnalytics:
-	def __init__( self ):
-		self.devMax = 0.0
-		self.devMin = 0.0
-		self.devStd = 0.0
-class DescMat:
-	def __init__( self ):
-		self.prec 	= ""
-		self.dim 	= ""
-		self.min 	= ""
-		self.max 	= ""
-class DescExp:
-	def __init__( self ):
-		self.num 	= 0
-		self.acc 	= ""
-		self.prec 	= ""
-		self.kernel = ""
-
-# Factory methods
-def factoryDescMat( prec, dim, min, max ):
-	desc = DescMat()
-	desc.prec 	= prec
-	desc.dim 	= dim
-	desc.min 	= min
-	desc.max 	= max
-	return desc
-def factoryDescExp( kernel, acc, prec, num ):
-	desc = DescExp()
-	desc.num 	= num
-	desc.acc 	= acc
-	desc.prec 	= prec
-	desc.kernel	= kernel
-	return desc
-
-# IO
-def readResExperiment():
-	res = open( GetPath( PATH_TO_RESEXP ) )
-	lines = [ line.strip() for line in res ]
-	linesf = []
-	for line in lines:
-		lineSplit = line.split( "\t", 2 )
-		linesf.append( lineSplit[ 1 ] )
-	re = ResExperiment()
-	
-	re.precision 	= int( linesf[ 2 ] )
-	re.rows			= int( linesf[ 3 ] )
-	re.cols			= int( linesf[ 4 ] )
-	re.equal 		= bool( linesf[ 0 ] )
[…]

### 2014-08-17 dv2549_avg.py

@@ -1,94 +1,0 @@
-import os
-import sys
-import getopt
-import subprocess
-
-PATH_TO_EXPRES = "res/"
-
-# Relative paths
-def GetPath( rel ): # Relative to absolute path.
-        return os.path.abspath( rel )
-
-def avg( list ):
-        num = 0
-        sum = 0
-        for entry in list:
-                num += 1
-                sum += entry
-        return sum / num
-def read( filename ):
-        res = open( GetPath( filename ) )
-        lines = [ float( line.strip() ) for line in res ]
-        return lines
-def write( filename, avg ):
-        out = open( GetPath( filename + ".avg" ), "w" )
-        out.write( str( avg ) )
-        out.close()
-def readAvgWrite( filename ):
-	filename = PATH_TO_EXPRES + filename
-	write( filename, avg( read( filename ) ) )
-
-# Entry point:
-print( "---\ndv2549_avg\n---" )
-
-# BASIC
-readAvgWrite( "BASIC" + "HARD" + "FLOAT" + ".dmax" )
-readAvgWrite( "BASIC" + "HARD" + "FLOAT" + ".dmin" )
-readAvgWrite( "BASIC" + "HARD" + "FLOAT" + ".dstd" )
-readAvgWrite( "BASIC" + "HARD" + "FLOAT" + ".mss" )
-
-#readAvgWrite( "BASIC" + "HARD" + "INT" + ".dmax" )
-#readAvgWrite( "BASIC" + "HARD" + "INT" + ".dmin" )
-#readAvgWrite( "BASIC" + "HARD" + "INT" + ".dstd" )
-#readAvgWrite( "BASIC" + "HARD" + "INT" + ".mss" )
-
-readAvgWrite( "BASIC" + "SOFT" + "FLOAT" + ".dmax" )
-readAvgWrite( "BASIC" + "SOFT" + "FLOAT" + ".dmin" )
-readAvgWrite( "BASIC" + "SOFT" + "FLOAT" + ".dstd" )
-readAvgWrite( "BASIC" + "SOFT" + "FLOAT" + ".mss" )
-
[…]

### 2014-08-17 src/analytics/Analytic.h

@@ -1,10 +1,0 @@
-#ifndef DV2549_ANALYTICS_ANALYTIC_H
-#define DV2549_ANALYTICS_ANALYTIC_H
-
-struct Analytic {
-	double deviationMax;
-	double deviationMin;
-	double deviationStandard; // standard deviation
-};
-
-#endif // DV2549_ANALYTICS_ANALYTIC_H

### 2014-08-17 src/analytics/Analytics.cpp

@@ -1,53 +1,0 @@
-#include <stdafx.h>
-
-#include <Printer.h>
-#include <Deviant.h>
-#include <Analytics.h>
-
-Analytics::Analytics() {
-
-}
-Analytics::~Analytics() {
-	// Do nothing.
-}
-
-int Analytics::run() {
-	Analytic analytic;
-
-	DoubleList c, ref;
-	loadMatrix( g_pathC, c );
-	loadMatrix( g_pathRef, ref );
-
-	Deviant deviant;
-	deviant.establishDeviations( analytic, c, ref );
-
-	// Write analytic
-	Printer printer( analytic );
-	printer.init( g_pathRes );
-
-	free( c.list );
-	free( ref.list );
-
-	return 0;
-}
-
-void Analytics::loadMatrix( std::string p_filepath, DoubleList& io_list ) {
-	unsigned precision, rows, cols;
-	std::ifstream mxgb( p_filepath, std::ios_base::binary );
-	if( mxgb.is_open()==true ) {
-		mxgb.read( (char*)&precision, sizeof(unsigned) );
-		mxgb.read( (char*)&rows, sizeof(unsigned) );
-		mxgb.read( (char*)&cols, sizeof(unsigned) );
-
-		io_list.num = rows * cols;
-		io_list.list = (double*)malloc( sizeof( double ) * io_list.num );
-
-		float f;
-		for(unsigned i = 0; i<io_list.num; i++) {
-			mxgb.read((char*)&f, sizeof(float));
-			io_list.list[i] = (double)f;
-		}
-	} else {
-		throw ExceptionAnalytics( "Could not open file " + p_filepath + "!" );
-	}
-}

### 2014-08-17 src/analytics/Analytics.h

@@ -1,15 +1,0 @@
-#ifndef DV2549_ANALYTICS_ANALYTICS_H
-#define DV2549_ANALYTICS_ANALYTICS_H
-
-class Analytics {
-public:
-	Analytics();
-	~Analytics();
-
-	int run();
-protected:
-private:
-	void loadMatrix( std::string p_filepath, DoubleList& io_list );
-};
-
-#endif // DV2549_ANALYTICS_ANALYTICS_H

### 2014-08-17 src/analytics/Common.h

@@ -1,8 +1,0 @@
-#ifndef DV2549_ANALYTICS_COMMON_H
-#define DV2549_ANALYTICS_COMMON_H
-
-#include <Analytic.h>
-#include <DoubleList.h>
-#include <ExceptionAnalytics.h>
-
-#endif // DV2549_ANALYTICS_COMMON_H

### 2014-08-17 src/analytics/Conf.h

@@ -1,9 +1,0 @@
-#ifndef DV2549_ANALYTICS_CONF_H
-#define DV2549_ANALYTICS_CONF_H
-
-const static std::string g_pathRes = "../../../res/resAnalytics.res";
-
-const static std::string g_pathC	= "../../../mxg/c.mxgb";
-const static std::string g_pathRef	= "../../../mxg/ref.mxgb";
-
-#endif // DV2549_ANALYTICS_CONF_H

### 2014-08-17 src/analytics/Deviant.cpp

@@ -1,62 +1,0 @@
-#include <stdafx.h>
-
-#include <Deviant.h>
-
-Deviant::Deviant() {
-	concurrency::accelerator default_device;
-	std::wcout << std::endl << L"Initializing C++ AMP with device: " << default_device.get_description() + L".";
-	if( default_device==concurrency::accelerator( concurrency::accelerator::direct3d_ref) ) {
-		std::cout << std::endl << "Warning. Running C++ AMP using a slow emulator.";
-	}
-}
-Deviant::~Deviant() {
-	// Do nothing.
-}
-
-void Deviant::establishDeviations( Analytic& io_analytic, DoubleList p_c, DoubleList p_ref ) {
-	DoubleList devs;
-	
-	getDeviations( p_c, p_ref, devs );
-	calculateDeviations( io_analytic, devs );
-
-	free( devs.list );
-}
-
-void Deviant::calculateDeviations( Analytic& io_analytic, DoubleList p_devs ) {
-	std::vector< double > devs;
-	devs.assign( p_devs.list, p_devs.list + p_devs.num );
-
-	// Establish min- and max- deviation.
-	auto itMax = std::max_element( std::begin( devs ), std::end( devs ) );
-	auto itMin = std::min_element( std::begin( devs ), std::end( devs ) );
-	io_analytic.deviationMax = *itMax;
-	io_analytic.deviationMin = *itMin;
-
-	// Establish standard deviation in an exciting, esoteric, manner:
-	double sum = std::accumulate( devs.begin(), devs.end(), 0.0 );
-	double mean = sum / devs.size();
-	std::vector< double > diff( devs.size() );
-	std::transform( devs.begin(), devs.end(), diff.begin(), std::bind2nd( std::minus< double >(), mean ) );
-	double sqSum = std::inner_product( diff.begin(), diff.end(), diff.begin(), 0.0 );
-	double std = std::sqrt( sqSum / devs.size() );
-	io_analytic.deviationStandard = std;
-}
-void Deviant::getDeviations( DoubleList p_c, DoubleList p_ref, DoubleList& io_devs ) {
-	std::cout << std::endl << "Compiling deviations...";
-	io_devs.num = p_c.num; // hack
-	io_devs.list = (double*)malloc( sizeof( double ) * io_devs.num );
-	
-	concurrency::array_view< double > iC( p_c.num, p_c.list ); 
[…]

### 2014-08-17 src/analytics/Deviant.h

@@ -1,16 +1,0 @@
-#ifndef DV2549_ANALYTICS_DEVIANT_H
-#define DV2549_ANALYTICS_DEVIANT_H
-
-class Deviant {
-public:
-	Deviant();
-	~Deviant();
-
-	void establishDeviations( Analytic& io_analytic, DoubleList p_c, DoubleList p_ref );
-protected:
-private:
-	void calculateDeviations( Analytic& io_analytic, DoubleList p_devs );
-	void getDeviations( DoubleList p_c, DoubleList p_ref, DoubleList& io_devs );
-};
-
-#endif // DV2549_ANALYTICS_DEVIANT_H

### 2014-08-17 src/analytics/DoubleList.h

@@ -1,9 +1,0 @@
-#ifndef DV2549_ANALYTICS_DOUBLELIST_H
-#define DV2549_ANALYTICS_DOUBLELIST_H
-
-struct DoubleList {
-	double* list;
-	unsigned num;
-};
-
-#endif // DV2549_ANALYTICS_DOUBLELIST_H

### 2014-08-17 src/analytics/ExceptionAnalytics.cpp

@@ -1,15 +1,0 @@
-#include <stdafx.h>
-
-#include <ExceptionAnalytics.h>
-
-ExceptionAnalytics::ExceptionAnalytics( std::string p_func ) throw() : exception() {
-	m_func = p_func;
-}
-ExceptionAnalytics::~ExceptionAnalytics() throw() {
-	// Do nothing.
-}
-
-const char* ExceptionAnalytics::what() const throw() {
-	std::string what = "Experiment - Exception: " + m_func;
-	return what.c_str();
-}

### 2014-08-17 src/analytics/ExceptionAnalytics.h

@@ -1,14 +1,0 @@
-#ifndef DV2549_ANALYTICS_EXCEPTIONANALYTICS_H
-#define DV2549_ANALYTICS_EXCEPTIONANALYTICS_H
-
-class ExceptionAnalytics : public std::exception {
-public:
-	ExceptionAnalytics( std::string p_func ) throw();
-	virtual ~ExceptionAnalytics() throw();
-
-	virtual const char* what() const throw();
-private:
-	std::string m_func;
-};
-
-#endif // DV2549_EXPERIMENT_EXCEPTIONEXPERIMENT_H

### 2014-08-17 src/analytics/FloatList.h

@@ -1,9 +1,0 @@
-#ifndef DV2549_ANALYTICS_DOUBLELIST_H
-#define DV2549_ANALYTICS_DOUBLELIST_H
-
-struct FloatList {
-	float* list;
-	unsigned num;
-};
-
-#endif // DV2549_ANALYTICS_DOUBLELIST_H

### 2014-08-17 src/analytics/Printer.cpp

@@ -1,23 +1,0 @@
-#include <stdafx.h>
-
-#include <Printer.h>
-
-Printer::Printer( Analytic p_analytic ) {
-	m_analytic = p_analytic;
-}
-Printer::~Printer() {
-	// Do nothing.
-}
-
-void Printer::init( std::string filepath ) {
-	std::ofstream res;
-	res.open( filepath );
-	if( res.is_open()==true ) {
-		res << "DeviationMax:\t"	<< m_analytic.deviationMax	<< "\n" 
-			<< "DeviationMin:\t"	<< m_analytic.deviationMin	<< "\n" 
-			<< "DeviationStd:\t"	<< m_analytic.deviationStandard;
-		res.close();
-	} else {
-		throw ExceptionAnalytics( "Could not open " + filepath + " for writing." );
-	}
-}

### 2014-08-17 src/analytics/Printer.h

@@ -1,15 +1,0 @@
-#ifndef DV2549_ANALYTICS_PRINTER_H
-#define DV2549_ANALYTICS_PRINTER_H
-
-class Printer {
-public:
-	Printer( Analytic p_analytics );
-	~Printer();
-
-	void init( std::string filepath );
-protected:
-private:
-	Analytic m_analytic;
-};
-
-#endif // DV2549_ANALYTICS_PRINTER_H

### 2014-08-17 src/analytics/main.cpp

@@ -1,11 +1,0 @@
-#include <stdafx.h>
-
-#include <Analytics.h>
-
-int main( int argc, char* argv[] ) {
-	std::cout << "\n" << "---" << "\n" << "Analytics Utility" << "\n" << "---" << "\n";
-	Analytics analytics;
-	analytics.run();
-
-	return 0;
-}

### 2014-08-17 src/analytics/stdafx.h

@@ -1,22 +1,0 @@
-#ifndef DV2549_ANALYTICS_STDAFX_H
-#define DV2549_ANALYTICS_STDAFX_H
-
-#include <amp.h>
-#include <amp_math.h>
-
-#include <map>
-#include <string>
-#include <vector>
-#include <fstream>
-#include <cassert>
-#include <numeric>
-#include <iostream>
-#include <typeinfo>
-#include <algorithm>
-#include <windows.h>
-#include <exception>
-
-#include <Conf.h>
-#include <Common.h>
-
-#endif // DV2549_ANALYTICS_STDAFX_H

### 2014-08-17 src/experiment/Buf.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Buf.h>

### 2014-08-17 src/experiment/Buf.h

@@ -1,45 +1,0 @@
-#ifndef DV2549_EXPERIMENT_BUF_H
-#define DV2549_EXPERIMENT_BUF_H
-
-template < class T >
-class Buf {
-public:
-	Buf( unsigned p_tNum ) {
-		m_tNum = p_tNum;
-		m_tSize = sizeof( T );
-		m_buf = nullptr;
-	}
-	Buf() {
-		m_tNum = 0;
-		m_tSize = sizeof( T );
-		m_buf = nullptr;
-	}
-	virtual ~Buf() {
-		ASSERT_RELEASE( m_buf );
-	}
-
-	virtual HRESULT init( ID3D11Device* p_device ) {
-		return S_OK;
-	}
-	HRESULT initBuf( ID3D11Device* p_device, D3D11_BUFFER_DESC& p_desc ) {
-		return p_device->CreateBuffer( &p_desc, NULL, &m_buf );
-	}
-	HRESULT initBuf( ID3D11Device* p_device, D3D11_BUFFER_DESC& p_desc, D3D11_SUBRESOURCE_DATA& p_initialData ) {
-		return p_device->CreateBuffer( &p_desc, &p_initialData, &m_buf );
-	}
-
-	ID3D11Buffer* getBuf() const {
-		return m_buf;
-	}
-protected:
-	unsigned getByteWidth() const {
-		return m_tSize * m_tNum;
-	}
-
-	unsigned m_tNum;
-	unsigned m_tSize;
-	ID3D11Buffer* m_buf;
-private:
-};
-
-#endif // DV2549_EXPERIMENT_BUF_H

### 2014-08-17 src/experiment/BufSrv.cpp

@@ -1,4 +1,0 @@
-#include <stdafx.h>
-
-#include <Buf.h>
-#include <BufSrv.h>

### 2014-08-17 src/experiment/BufSrv.h

@@ -1,55 +1,0 @@
-#ifndef DV2549_EXPERIMENT_BUFSRV_H
-#define DV2549_EXPERIMENT_BUFSRV_H
-
-#include <Buf.h>
-
-template < class T >
-class BufSrv : public Buf< T > {
-public:
-	BufSrv( T* p_data, unsigned p_tNum ) : Buf( p_tNum ) {
-		m_data = p_data;
-		m_srv = nullptr;
-	}
-	virtual ~BufSrv() {
-		ASSERT_RELEASE( m_srv );
-	}
-
-	HRESULT init( ID3D11Device* p_device ) {
-		HRESULT hr = initBuf( p_device );
-		if( SUCCEEDED( hr ) ) {
-			hr = initSrv( p_device );
-		}
-		return hr;
-	}
-
-	ID3D11ShaderResourceView* getSrv() const {
-		return m_srv;
-	}
-protected:
-private:
-	HRESULT initBuf( ID3D11Device* p_device ) {
-		D3D11_BUFFER_DESC desc; ZERO_MEM( desc );
-		desc.StructureByteStride = m_tSize;
-		desc.ByteWidth			= getByteWidth();
-		desc.MiscFlags			= D3D11_RESOURCE_MISC_BUFFER_STRUCTURED;
-		desc.BindFlags			= D3D11_BIND_SHADER_RESOURCE;
-		desc.Usage				= D3D11_USAGE_IMMUTABLE;
-
-		D3D11_SUBRESOURCE_DATA srData; ZERO_MEM( srData );
-		srData.pSysMem = m_data;
-		return Buf::initBuf( p_device, desc, srData );
-	}
-	HRESULT initSrv( ID3D11Device* p_device ) {
-		D3D11_SHADER_RESOURCE_VIEW_DESC descSrv; ZERO_MEM( descSrv );
-		descSrv.Format				= DXGI_FORMAT_UNKNOWN;
-		descSrv.ViewDimension		= D3D11_SRV_DIMENSION_BUFFER;
-		descSrv.Buffer.FirstElement	= 0; // Considering the struct has been cleared with ZeroMemory, this shouldn't need setting.
-		descSrv.Buffer.NumElements	= m_tNum;
-		return p_device->CreateShaderResourceView( m_buf, &descSrv, &m_srv );
-	}
-
-	T* m_data;
-	ID3D11ShaderResourceView* m_srv;
-};
-
-#endif // DV2549_EXPERIMENT_BUFSRV_H

### 2014-08-17 src/experiment/BufUav.cpp

@@ -1,4 +1,0 @@
-#include <stdafx.h>
-
-#include <Buf.h>
-#include <BufUav.h>

### 2014-08-17 src/experiment/BufUav.h

@@ -1,60 +1,0 @@
-#ifndef DV2549_EXPERIMENT_BUFUAV_H
-#define DV2549_EXPERIMENT_BUFUAV_H
-
-template < class T >
-class BufUav : public Buf< T > {
-public:
-	BufUav( unsigned p_tNum ) : Buf( p_tNum ) {
-		m_uav = nullptr;
-	}
-	virtual ~BufUav() {
-		ASSERT_RELEASE( m_uav );
-	}
-
-	HRESULT init( ID3D11Device* p_device, DXGI_FORMAT p_format ) { // hack!
-		HRESULT hr = initBuf( p_device );
-		if( SUCCEEDED( hr ) ) {
-			hr = initUav( p_device, p_format );
-		}
-		return hr;
-	}
-
-	ID3D11UnorderedAccessView* getUav() const {
-		return m_uav;
-	}
-protected:
-private:
-	HRESULT initBuf( ID3D11Device* p_device ) {
-		D3D11_BUFFER_DESC desc; ZERO_MEM( desc );
-		desc.ByteWidth	= getByteWidth();
-		desc.BindFlags	= D3D11_BIND_UNORDERED_ACCESS;
-		desc.Usage		= D3D11_USAGE_DEFAULT;
-
-		return Buf::initBuf( p_device, desc );
-	}
-	HRESULT initUav( ID3D11Device* p_device, DXGI_FORMAT p_format ) {
-		D3D11_UNORDERED_ACCESS_VIEW_DESC desc; ZERO_MEM( desc );
-		desc.Format					= p_format;
-		desc.ViewDimension			= D3D11_UAV_DIMENSION_BUFFER;
-		desc.Buffer.FirstElement	= 0;
-		desc.Buffer.NumElements		= m_tNum;
-		return p_device->CreateUnorderedAccessView( m_buf, &desc, &m_uav );
-	}
-
-	ID3D11UnorderedAccessView* m_uav;
-};
-
-#endif // DV2549_EXPERIMENT_BUFUAV_H
-
-// Something like this?
-/*
-DXGI_FORMAT uavFormat = DXGI_FORMAT_UNKNOWN;
-switch( std::type_info( T ) ) {
-case std::type_info( int ):
-uavFormat = DXGI_FORMAT_R32_SINT;
-break;
-case std::type_info( float ):
-uavFormat = DXGI_FORMAT_R32_FLOAT;
-break;
-}
-*/

### 2014-08-17 src/experiment/Case.h

@@ -1,29 +1,0 @@
-#ifndef DV2549_EXPERIMENT_CASE_H
-#define DV2549_EXPERIMENT_CASE_H
-
-#include <Matrix.h>
-
-template < class T >
-struct Case {
-	Case() {
-		a = b = c = ref = nullptr;
-		ms = -1;
-		equalToRef = false;
-	}
-	~Case() {
-		ASSERT_DELETE( a );
-		ASSERT_DELETE( b );
-		ASSERT_DELETE( c );
-		ASSERT_DELETE( ref );
-	}
-
-	Matrix< T >* a;	// Matrices generated by matrixgen.
-	Matrix< T >* b;	// Matrices generated by matrixgen.
-	Matrix< T >* c;	// Result matrix calculated by experiment.
-	Matrix< T >* ref; // Result matrix generated by matrixgen.
-
-	double ms; // Execution time in ms.
-	bool equalToRef;
-};
-
-#endif // DV2549_EXPERIMENT_CASE_H

### 2014-08-17 src/experiment/Cb.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Cb.h>

### 2014-08-17 src/experiment/Cb.h

@@ -1,38 +1,0 @@
-#ifndef DV2549_EXPERIMENT_CB_H
-#define DV2549_EXPERIMENT_CB_H
-
-template < class T >
-class Cb {
-public:
-	Cb() {
-		m_buf = nullptr;
-	}
-	~Cb() {
-		ASSERT_RELEASE( m_buf );
-	}
-
-	HRESULT init( ID3D11Device* p_device ) {
-		HRESULT hr = S_FALSE;
-		unsigned cbSize = sizeof( T );
-		if( ( cbSize % 16 )!=0 ) {
-			throw ExceptionExperiment( "Constant buffer not multiple of 16!" );
-		} else {
-			D3D11_BUFFER_DESC desc; ZERO_MEM( desc );
-			desc.BindFlags		= D3D11_BIND_CONSTANT_BUFFER;
-			desc.ByteWidth		= cbSize;
-			desc.CPUAccessFlags = D3D11_CPU_ACCESS_WRITE;
-			desc.Usage			= D3D11_USAGE_DYNAMIC;
-			hr = p_device->CreateBuffer( &desc, NULL, &m_buf );
-		}
-		return hr;
-	}
-
-	ID3D11Buffer* get() const {
-		return m_buf;
-	}
-protected:
-private:
-	ID3D11Buffer* m_buf;
-};
-
-#endif // DV2549_EXPERIMENT_CB_H

### 2014-08-17 src/experiment/CbDesc.h

@@ -1,17 +1,0 @@
-#ifndef DV2549_EXPERIMENT_CBDESC_H
-#define DV2549_EXPERIMENT_CBDESC_H
-
-struct CbMatrixProperties {
-	unsigned aRows;
-	unsigned aCols;
-
-	unsigned bRows;
-	unsigned bCols;
-
-	unsigned cRows;
-	unsigned cCols;
-
-	unsigned pad[ 2 ];
-};
-
-#endif // DV2549_EXPERIMENT_CBDESC_H

### 2014-08-17 src/experiment/CogCb.cpp

@@ -1,42 +1,0 @@
-#include <stdafx.h>
-
-#include <Cb.h>
-#include <CogCb.h>
-#include <CbDesc.h>
-
-CogCb::CogCb() {
-	m_cbMatrixProps = nullptr;
-}
-CogCb::~CogCb() {
-	ASSERT_DELETE( m_cbMatrixProps );
-}
-
-HRESULT CogCb::init( ID3D11Device* p_device ) {
-	m_cbMatrixProps = new Cb< CbMatrixProperties >();
-	return m_cbMatrixProps->init( p_device );
-}
-
-HRESULT CogCb::updateMatrixProps( ID3D11DeviceContext* p_devcon, CbMatrixProperties p_new ) {
-	ID3D11Buffer* cb = m_cbMatrixProps->get();
-	
-	D3D11_MAPPED_SUBRESOURCE mapSubRsrc;
-	HRESULT hr = p_devcon->Map( cb, 0, D3D11_MAP_WRITE_DISCARD, 0, &mapSubRsrc );
-	if( SUCCEEDED( hr ) ) {
-		CbMatrixProperties* old = (CbMatrixProperties*)mapSubRsrc.pData;
-		old->aRows = p_new.aRows;
-		old->aCols = p_new.aCols;
-		old->bRows = p_new.bRows;
-		old->bCols = p_new.bCols;
-		old->cRows = p_new.cRows;
-		old->cCols = p_new.cCols;
-
-		p_devcon->Unmap( cb, 0 );
-	} else {
-		MessageboxError( "Failed to map constant buffer!" );
-	}
-	return hr;
-}
-void CogCb::setMatrixProps( ID3D11DeviceContext* p_devcon ) {
-	ID3D11Buffer* cb = m_cbMatrixProps->get();
-	p_devcon->CSSetConstantBuffers( 0, 1, &cb );
-}

### 2014-08-17 src/experiment/CogCb.h

@@ -1,23 +1,0 @@
-#ifndef DV2549_EXPERIMENT_COGCB_H
-#define DV2549_EXPERIMENT_COGCB_H
-
-template < class T >
-class Cb;
-
-#include <CbDesc.h>
-
-class CogCb {
-public:
-	CogCb();
-	~CogCb();
-
-	HRESULT init( ID3D11Device* p_device );
-
-	HRESULT updateMatrixProps( ID3D11DeviceContext* p_devcon, CbMatrixProperties p_new );
-	void setMatrixProps( ID3D11DeviceContext* p_devcon );
-protected:
-private:
-	Cb< CbMatrixProperties >* m_cbMatrixProps;
-};
-
-#endif // DV2549_EXPERIMENT_COGCB_H

### 2014-08-17 src/experiment/CogFx.cpp

@@ -1,53 +1,0 @@
-#include <stdafx.h>
-
-#include <CogFx.h>
-#include <FxCs.h>
-
-CogFx::CogFx( ExperimentConf p_conf ) {
-	m_conf = p_conf;
-	
-	m_mult = nullptr;
-}
-CogFx::~CogFx() {
-	ASSERT_DELETE( m_mult );
-}
-
-HRESULT CogFx::init( ID3D11Device* p_device ) {
-	return initMult( p_device );;
-}
-
-Fx* CogFx::getKernel() const {
-	return m_mult;
-}
-
-HRESULT CogFx::initMult( ID3D11Device* p_device ) {
-	// This method can easily be made not-so-extremely-ugly by creating a simple desc-object.
-	LPCWSTR kernel = L"UnknownFx";
-	switch( m_conf.confFx ) {
-	case ExperimentFxs_MULT_BASIC:
-		switch( m_conf.confPrecision ) {
-		case ExperimentPrecisions_INT:
-			kernel = g_fxMultIntBasic;
-			break;
-		case ExperimentPrecisions_FLOAT:
-			kernel = g_fxMultFloatBasic;
-			break;
-		}
-		break;
-	case ExperimentFxs_MULT_TILE:
-		switch( m_conf.confPrecision ) {
-		case ExperimentPrecisions_INT:
-			kernel = g_fxMultIntTile;
-			break;
-		case ExperimentPrecisions_FLOAT:
-			kernel = g_fxMultFloatTile;
-			break;
-		}
-		break;
-	default:
-		throw 0;
-		break;
-	}
-	m_mult = new FxCs( kernel );
-	return m_mult->init( p_device );
-}

### 2014-08-17 src/experiment/CogFx.h

@@ -1,23 +1,0 @@
-#ifndef DV2549_EXPERIMENT_COGFX_H
-#define DV2549_EXPERIMENT_COGFX_H
-
-struct ID3D11Device;
-class Fx;
-
-class CogFx {
-public:
-	CogFx( ExperimentConf p_conf );
-	~CogFx();
-
-	HRESULT init( ID3D11Device* p_device );
-
-	Fx* getKernel() const;
-protected:
-	HRESULT initMult( ID3D11Device* p_device );
-private:
-	ExperimentConf m_conf;
-
-	Fx* m_mult;
-};
-
-#endif // DV2549_EXPERIMENT_FX_H

### 2014-08-17 src/experiment/Common.h

@@ -1,14 +1,0 @@
-#ifndef DV2549_EXPERIMENT_COMMON_H
-#define DV2549_EXPERIMENT_COMMON_H
-
-#include <map>
-#include <string>
-#include <vector>
-#include <fstream>
-#include <cassert>
-#include <iostream>
-#include <typeinfo>
-#include <windows.h>
-#include <exception>
-
-#endif // DV2549_EXPERIMENT_COMMON_H

### 2014-08-17 src/experiment/CommonDx.h

@@ -1,9 +1,0 @@
-#ifndef DV2549_EXPERIMENT_COMMONDX_H
-#define DV2549_EXPERIMENT_COMMONDX_H
-
-#include <d3d11.h>
-#include <D3D11.h>
-#include <d3dcommon.h>
-#include <d3dcompiler.h>
-
-#endif // DV2549_EXPERIMENT_COMMONDX_H

### 2014-08-17 src/experiment/CommonWin.h

@@ -1,4 +1,0 @@
-#ifndef DV2549_EXPERIMENT_COMMONWIN_H
-#define DV2549_EXPERIMENT_COMMONWIN_H
-
-#endif // DV2549_EXPERIMENT_COMMONWIN_H

### 2014-08-17 src/experiment/Conf.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Conf.h>

### 2014-08-17 src/experiment/Conf.h

@@ -1,62 +1,0 @@
-#ifndef DV2549_EXPERIMENT_CONF_H
-#define DV2549_EXPERIMENT_CONF_H
-
-#define BLOCK_SIZE 16
-
-static const LPCWSTR g_fxMultIntBasic	= L"MultIntBasic.cso";
-static const LPCWSTR g_fxMultFloatBasic = L"MultFloatBasic.cso";
-static const LPCWSTR g_fxMultIntTile	= L"MultIntTile.cso";
-static const LPCWSTR g_fxMultFloatTile	= L"MultFloatTile.cso";
-
-static const std::string g_mxgPath = "../../../mxg/";
-static const std::string g_resPath = "../../../res/";
-static const std::string g_mxgA = "a.mxg";
-static const std::string g_mxgB = "b.mxg";
-static const std::string g_mxgC = "c.mxgb";
-static const std::string g_mxgRef = "ref.mxgb";
-
-// These three enums are hacks spread throughout the application.
-// Try to get tid of them.
-enum ExperimentPrecisions {
-	ExperimentPrecisions_INT	= 0,
-	ExperimentPrecisions_FLOAT	= 1
-};
-
-// Please note that SOFT makes use of the REFERENCE-driver, rather than the SOFTWARE-driver.
-enum ExperimentAccelerations {
-	ExperimentAccelerations_HARD	= 1, // D3D_DRIVER_TYPE_HARDWARE
-	ExperimentAccelerations_SOFT	= 2, // D3D_DRIVER_TYPE_REFERENCE
-	ExperimentAccelerations_WARP	= 5	 // D3D_DRIVER_TYPE_WARP
-};
-
-enum ExperimentFxs {
-	ExperimentFxs_MULT_BASIC	= 0,
-	ExperimentFxs_MULT_TILE		= 1
-};
-
-struct ExperimentConf {
-	ExperimentConf() { }
-	ExperimentConf( ExperimentFxs p_f, ExperimentAccelerations p_a, ExperimentPrecisions p_p ) {
-		confFx				= p_f;
-		confAcceleration	= p_a;
-		confPrecision		= p_p;
-	}
-	~ExperimentConf() { }
-
-	ExperimentPrecisions	confPrecision;
[…]

### 2014-08-17 src/experiment/Dx.cpp

@@ -1,4 +1,0 @@
-#include <stdafx.h>
-
-#include <Dx.h>
-#include <TimerDx.h>

### 2014-08-17 src/experiment/Dx.h

@@ -1,161 +1,0 @@
-#ifndef DV2549_EXPERIMENT_DX_H
-#define DV2549_EXPERIMENT_DX_H
-
-#include <Fx.h>
-#include <Cb.h>
-#include <Win.h>
-#include <Case.h>
-#include <CogFx.h>
-#include <CogCb.h>
-#include <BufSrv.h>
-#include <BufUav.h>
-#include <TimerDx.h> // These includes are ugly. Fix.
-
-template < class T >
-class Dx {
-public:
-	Dx( Case< T >& p_case, ExperimentConf p_conf ) {
-		m_case = &p_case;
-		m_conf = p_conf;
-
-		m_cogFx = nullptr;
-		m_cogCb = nullptr;
-		m_bufC	= nullptr;
-		m_srvA	= nullptr;
-		m_srvB	= nullptr;
-		m_uavC	= nullptr;
-		m_timer = nullptr;
-	}
-	~Dx() {
-		ASSERT_DELETE( m_cogFx	);
-		ASSERT_DELETE( m_cogCb	);
-		ASSERT_DELETE( m_bufC	);
-		ASSERT_DELETE( m_srvA	);
-		ASSERT_DELETE( m_srvB	);
-		ASSERT_DELETE( m_uavC	);
-		ASSERT_DELETE( m_timer	);
-	}
-
-	HRESULT init( Win* p_win ) {
-		HRESULT hr = initD3D( p_win );
-		if( SUCCEEDED( hr ) ) {
-			hr = initBuf();
-		}
-		if( SUCCEEDED( hr ) ) {
-			m_cogFx = new CogFx( m_conf );
-			hr = m_cogFx->init( m_d3d.device );
-		}
-		if( SUCCEEDED( hr ) ) {
-			m_cogCb = new CogCb();
-			hr = m_cogCb->init( m_d3d.device );
-		}
-		if( SUCCEEDED( hr ) ) {
-			m_timer = new TimerDx();
-			hr = m_timer->init( m_d3d.device );
-		}
-		return hr;
-	}
-	double run() {
-		// Set resources:
-		m_cogFx->getKernel()->set( m_d3d.devcon );
-
-		ID3D11ShaderResourceView* srvs[ 2 ] = { m_srvA->getSrv(), m_srvB->getSrv() };
-		ID3D11UnorderedAccessView* uavs[ 1 ] = { m_uavC->getUav() };
-		m_d3d.devcon->CSSetShaderResources( 0, 2, srvs );
[…]

### 2014-08-17 src/experiment/ExceptionExperiment.cpp

@@ -1,13 +1,0 @@
-#include <stdafx.h>
-
-ExceptionExperiment::ExceptionExperiment( std::string p_func ) throw() : exception() {
-	m_func = p_func;
-}
-ExceptionExperiment::~ExceptionExperiment() throw() {
-	// Do nothing.
-}
-
-const char* ExceptionExperiment::what() const throw() {
-	std::string what = "Experiment - Exception: " + m_func;
-	return what.c_str();
-}

### 2014-08-17 src/experiment/ExceptionExperiment.h

@@ -1,14 +1,0 @@
-#ifndef DV2549_EXPERIMENT_EXCEPTIONEXPERIMENT_H
-#define DV2549_EXPERIMENT_EXCEPTIONEXPERIMENT_H
-
-class ExceptionExperiment : public std::exception {
-public:
-	ExceptionExperiment( std::string p_func ) throw();
-	virtual ~ExceptionExperiment() throw();
-
-	virtual const char* what() const throw();
-private:
-	std::string m_func;
-};
-
-#endif // DV2549_EXPERIMENT_EXCEPTIONEXPERIMENT_H

### 2014-08-17 src/experiment/Experiment.cpp

@@ -1,4 +1,0 @@
-#include <stdafx.h>
-
-#include <Printer.h>
-#include <Experiment.h>

### 2014-08-17 src/experiment/Experiment.h

@@ -1,70 +1,0 @@
-#ifndef DV2549_EXPERIMENT_EXPERIMENT_H
-#define DV2549_EXPERIMENT_EXPERIMENT_H
-
-#include <Dx.h>
-#include <Win.h>
-#include <Case.h>
-#include <Reader.h>
-#include <Printer.h>
-#include <Inspector.h> // Get rid of these includes somehow.
-
-template < class T >
-class Experiment {
-public:
-	Experiment( Winfo* p_winfo, ExperimentConf p_conf ) {
-		m_winfo	= p_winfo;
-		m_conf	= p_conf;
-		
-		m_dx	= nullptr;
-		m_win	= nullptr;
-	}
-	~Experiment() {
-		ASSERT_DELETE( m_win );
-		ASSERT_DELETE( m_dx );
-	}
-	
-	HRESULT init() {
-		HRESULT hr = BOOL_TO_HRESULT( Reader< T >::loadCase( m_case ) );
-		if( SUCCEEDED( hr ) ) {
-			hr = initWin();
-		}
-		if( SUCCEEDED( hr ) ) {
-			hr = initDx();
-		}
-		return hr;
-	}
-
-	int run( int argc, char *argv[] ) {
-		// Perform matrix multiplication of specified case using DirectCompute:
-		m_case.ms = m_dx->run();
-
-		// Compare result to reference matrix compiled by C++ AMP:
-		Inspector< T > inspector( m_case );
-		bool isEqual = inspector.inspect();
-
-		Printer< T > printer( m_conf.confPrecision, m_case );
-		bool sucessfulPrint = printer.print();
-
-		return !isEqual;
-	}
-protected:
-	HRESULT initWin() {
-		m_win = new Win( m_winfo->hInstance, m_winfo->hInstancePrev, m_winfo->lpCmdLine, m_winfo->nCmdShow );
-		return m_win->init();
-	}
-	HRESULT initDx() {
-		m_dx = new Dx< T >( m_case, m_conf );
-		return m_dx->init( m_win );;
-	}
-private:
-	Win* m_win;
-	ExperimentConf m_conf;
-
-	Dx< T >* m_dx;
-	Case< T > m_case;
-
-	// Junk:
-	Winfo* m_winfo;
-};
-
-#endif // DV2549_EXPERIMENT_EXPERIMENT_H

### 2014-08-17 src/experiment/Fx.cpp

@@ -1,28 +1,0 @@
-#include <stdafx.h>
-
-#include <Fx.h>
-
-Fx::Fx( LPCWSTR p_kernelPath ) {
-	m_kernelPath = p_kernelPath;
-
-	m_blob = nullptr;
-}
-Fx::~Fx() {
-	assert( m_blob );
-	m_blob->Release();
-}
-
-HRESULT Fx::init( ID3D11Device* p_device ) {
-	HRESULT hr = S_OK;
-	hr = D3DReadFileToBlob( m_kernelPath, &m_blob );
-	if( hr!=S_OK ) {
-		// Fix this, this is terrible:
-		std::wstring location = L"Kernel::init D3DReadFileToBlob ";
-		std::wstring failed = L" Failed!";
-		std::wstring errorMsg = location + static_cast<std::wstring>( m_kernelPath ) + failed;
-		std::string std( errorMsg.begin(), errorMsg.end() );
-		MessageboxError( std );
-	}
-
-	return hr;
-}

### 2014-08-17 src/experiment/Fx.h

@@ -1,19 +1,0 @@
-#ifndef DV2549_EXPERIMENT_FX_H
-#define DV2549_EXPERIMENT_FX_H
-
-class Fx {
-public:
-	Fx( LPCWSTR p_kernelPath );
-	virtual ~Fx();
-
-	virtual HRESULT init( ID3D11Device* p_device );
-
-	virtual void set( ID3D11DeviceContext* p_devcon )	= 0;
-	virtual void unset( ID3D11DeviceContext* p_devcon ) = 0;
-protected:
-	ID3D10Blob* m_blob; // Contains compiled kernel.
-private:
-	LPCWSTR m_kernelPath; // Path to compiled shader.
-};
-
-#endif // DV2549_EXPERIMENT_FX_H

### 2014-08-17 src/experiment/FxCs.cpp

@@ -1,30 +1,0 @@
-#include <stdafx.h>
-
-#include <FxCs.h>
-
-FxCs::FxCs( LPCWSTR p_kernelPath ) : Fx( p_kernelPath ) {
-	m_cs = nullptr;
-}
-FxCs::~FxCs() {
-	assert( m_cs );
-	m_cs->Release();
-}
-
-HRESULT FxCs::init( ID3D11Device* p_device ) {
-	HRESULT hr = Fx::init( p_device );
-	if( SUCCEEDED( hr ) ) {
-		hr = p_device->CreateComputeShader( 
-			m_blob->GetBufferPointer(),
-			m_blob->GetBufferSize(),
-			nullptr,
-			&m_cs );
-	}
-	return hr;
-}
-
-void FxCs::set( ID3D11DeviceContext* p_devcon ) {
-	p_devcon->CSSetShader( m_cs, nullptr, 0 );
-}
-void FxCs::unset( ID3D11DeviceContext* p_devcon ) {
-	p_devcon->CSSetShader( nullptr, nullptr, 0 );
-}

### 2014-08-17 src/experiment/FxCs.h

@@ -1,20 +1,0 @@
-#ifndef DV2549_EXPERIMENT_FXCS_H
-#define DV2549_EXPERIMENT_FXCS_H
-
-#include <Fx.h>
-
-class FxCs : public Fx {
-public:
-	FxCs( LPCWSTR p_kernelPath );
-	virtual ~FxCs();
-
-	HRESULT init( ID3D11Device* p_device );
-
-	void set( ID3D11DeviceContext* p_devcon );
-	void unset( ID3D11DeviceContext* p_devcon );
-protected:
-private:
-	ID3D11ComputeShader* m_cs;
-};
-
-#endif // DV2549_EXPERIMENT_FXCS_H

### 2014-08-17 src/experiment/Inspector.cpp

@@ -1,4 +1,0 @@
-#include <stdafx.h>
-
-#include <Case.h>
-#include <Inspector.h>

### 2014-08-17 src/experiment/Inspector.h

@@ -1,47 +1,0 @@
-#ifndef DV2549_EXPERIMENT_INSPECTOR_H
-#define DV2549_EXPERIMENT_INSPECTOR_H
-
-template < class T >
-class Inspector {
-public:
-	Inspector( Case< T >& p_case ) {
-		m_case = &p_case;
-	}
-	~Inspector() {
-		// Do nothing.
-	}
-
-	bool inspect() {
-		bool isEqual = false;
-		
-		T* m1 = m_case->ref->get();
-		T* m2 = m_case->c->get();
-		unsigned rows = m_case->ref->getNumRows();
-		unsigned cols = m_case->ref->getNumCols();
-
-		unsigned size = rows * cols * sizeof( T );
-		int comparison = memcmp( m1, m2, size );
-		if( comparison==0 ) {
-			isEqual = true;
-		}
-		m_case->equalToRef = isEqual;
-
-		return isEqual;
-	}
-protected:
-private:
-	Case< T >* m_case;
-};
-
-#endif // DV2549_EXPERIMENT_INSPECTOR_H
-
-/*T* m1 = m_case->m_ref->get();
-T* m2 = m_case->m_c->get();
-unsigned rows = m_case->m_ref->getNumRows();
-unsigned cols = m_case->m_ref->getNumCols();
-for( unsigned row = 0; row < rows; row++ ) {
-for( unsigned col = 0; col < cols; col++ ) {
-T a = m1[];
-if(  )
-}
-}*/

### 2014-08-17 src/experiment/Matrix.h

@@ -1,38 +1,0 @@
-#ifndef DV2549_EXPERIMENT_MATRIX_H
-#define DV2549_EXPERIMENT_MATRIX_H
-
-template < class T >
-class Matrix {
-public:
-	Matrix( T* p_, unsigned p_rows, unsigned p_cols ) {
-		m_ = MatrixAlloc< T >( p_rows, p_cols );
-		unsigned size = sizeof( T ) * p_rows * p_cols;
-		memcpy( m_, p_, size );
-
-		m_rows = p_rows;
-		m_cols = p_cols;
-	}
-	~Matrix() {
-		MatrixFree( m_ );
-	}
-
-	T* get() const {
-		return m_;
-	}
-	unsigned getNumRows() const {
-		return m_rows;
-	}
-	unsigned getNumCols() const {
-		return m_cols;
-	}
-	unsigned getNum() const {
-		return m_rows * m_cols;
-	}
-protected:
-private:
-	T* m_;
-	unsigned m_rows;
-	unsigned m_cols;
-};
-
-#endif // DV2549_EXPERIMENT_MATRIX_H

### 2014-08-17 src/experiment/Printer.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Printer.h>

### 2014-08-17 src/experiment/Printer.h

@@ -1,86 +1,0 @@
-#ifndef DV2549_EXPERIMENT_PRINTER_H
-#define DV2549_EXPERIMENT_PRINTER_H
-
-#include <Case.h>
-
-template < class T >
-class Printer {
-public:
-	Printer( ExperimentPrecisions p_precision, Case< T >& p_case ) {
-		m_precision = p_precision;
-		m_case = &p_case;
-	}
-	~Printer() {
-		// Do nothing.
-	}
-
-	bool print() {
-		bool success = true;
-		success = printC();
-		if( success==true ) {
-			success = printRes();
-		}
-		return success;
-	}
-protected:
-	bool printC() {
-		std::string filename = g_mxgC;
-
-		Matrix< T >* matrix = m_case->c;
-
-		bool success = true;
-		std::ofstream mxgb( g_mxgPath + filename, std::ios_base::binary );
-		if( mxgb.is_open()==true ) {
-			unsigned precision = (int)m_precision;
-			unsigned rows = matrix->getNumRows();
-			unsigned cols = matrix->getNumCols();
-			
-			mxgb.write( (const char*)&precision, sizeof(unsigned) ); // Ignore utility text since no human will be reading this, and the format won't be portable.
-			mxgb.write( (const char*)&rows, sizeof(unsigned) );
-			mxgb.write( (const char*)&cols, sizeof(unsigned) );
-
-			unsigned numElements = rows * cols;
-			T* m = matrix->get();
-			for( unsigned i = 0; i<numElements; i++ ) {
-				mxgb.write( (const char*)&m[i], sizeof(m[i]) );
-			}
-			mxgb.close();
-		} else {
-			throw ExceptionExperiment( "Could not open " + g_mxgPath + filename + " for writing." );
-			success = false;
-		}
-
-		return success;
-	}
-	bool printRes() {
-		std::string filename = g_resPath + "resExperiment.res";
-		
-		bool success = true;
-		std::ofstream res;
-		res.open( filename );
-		if( res.is_open()==true ) {
-			unsigned rows = m_case->c->getNumRows();
-			unsigned cols = m_case->c->getNumCols();
-
-			double ms = m_case->ms;
-			unsigned precision = (int)m_precision;
-			bool equalToRef = m_case->equalToRef;
-			
-			res << "Equal:\t"		<< (int)equalToRef	<< "\n" 
-				<< "TimeMs:\t"		<< ms				<< "\n" 
[…]

### 2014-08-17 src/experiment/Reader.h

@@ -1,85 +1,0 @@
-#ifndef DV2549_EXPERIMENT_READER_H
-#define DV2549_EXPERIMENT_READER_H
-
-#include <Case.h>
-#include <Matrix.h>
-
-template < class T >
-class Reader {
-public:
-	Reader() {
-	}
-	~Reader() {
-		// Do nothing.
-	}
-
-	static bool loadCase( Case< T >& io_case ) {
-		bool validCase = false;
-
-		Matrix< T >* mA = loadMxg( g_mxgPath + g_mxgA );
-		Matrix< T >* mB = loadMxg( g_mxgPath + g_mxgB );
-		Matrix< T >* mRef = loadMxgb( g_mxgPath + g_mxgRef );
-		if( mA!=nullptr && mB!=nullptr && mRef!=nullptr ) {
-			io_case.a = mA;
-			io_case.b = mB;
-			io_case.ref = mRef;
-			validCase = true;
-		}
-		return validCase;
-	}
-protected:
-private:
-	static Matrix< T >* loadMxg( std::string p_pathMxg ) {
-		Matrix< T >* matrix = nullptr;
-
-		std::string temp;
-		int precision;
-		unsigned rows, cols;
-
-		std::ifstream mxg( p_pathMxg );
-		if( mxg.is_open() ) {
-			mxg >> temp >> precision >> temp >> rows >> temp >> cols;
-			
-			unsigned i = 0;
-			T* m = MatrixAlloc< T >( rows, cols );
-			while( mxg.eof()==false ) {
-				mxg >> m[ i ];
-				i++;
-			}
-
-			matrix = new Matrix< T >( m, rows, cols );
-			MatrixFree( m ); // Matrix copies the passed data, so be sure to free memory.
-		} else {
-			MessageboxError( p_pathMxg + " not found!" );
-		}
-
-		return matrix;
-	}
-	static Matrix< T >* loadMxgb( std::string p_pathMxgb ) {
-		Matrix< T >* matrix = nullptr;
-
-		std::ifstream mxgb( p_pathMxgb, std::ios_base::binary );
-		if( mxgb.is_open() ) {
-			unsigned preRowCol[3];
-			for( unsigned i = 0; i<3; i++ ) {
-				mxgb.read( (char*)&preRowCol[i], sizeof(unsigned) );
-			}
-
-			unsigned i = 0;
-			T* m = MatrixAlloc< T >( preRowCol[1], preRowCol[2] );
[…]

### 2014-08-17 src/experiment/TimerDx.cpp

@@ -1,56 +1,0 @@
-#include <stdafx.h>
-
-#include <TimerDx.h>
-
-TimerDx::TimerDx() {
-	m_start		= nullptr;
-	m_stop		= nullptr;
-	m_disjoint	= nullptr;
-}
-TimerDx::~TimerDx() {
-	ASSERT_RELEASE( m_start );
-	ASSERT_RELEASE( m_stop );
-	ASSERT_RELEASE( m_disjoint );
-}
-
-HRESULT TimerDx::init( ID3D11Device* p_device ) {
-	D3D11_QUERY_DESC desc; ZERO_MEM( desc );
-	desc.Query = D3D11_QUERY_TIMESTAMP_DISJOINT;
-	HRESULT hr = p_device->CreateQuery( &desc, &m_disjoint );
-
-	desc.Query = D3D11_QUERY_TIMESTAMP;
-	if( SUCCEEDED( hr ) ) {
-		p_device->CreateQuery( &desc, &m_start );
-	}
-	if( SUCCEEDED( hr ) ) {
-		p_device->CreateQuery( &desc, &m_stop );
-	}
-	return hr;
-}
-
-void TimerDx::start( ID3D11DeviceContext* p_devcon ) {
-	p_devcon->Begin( m_disjoint );
-	p_devcon->End( m_start );
-}
-void TimerDx::stop( ID3D11DeviceContext* p_devcon ) {
-	p_devcon->End( m_stop );
-	p_devcon->End( m_disjoint );
-}
-double TimerDx::time( ID3D11DeviceContext* p_devcon ) {
-	UINT64 timeStart = 0;
-	while( p_devcon->GetData( m_start, &timeStart, sizeof( timeStart ), 0 )!=S_OK );
-
-	UINT64 timeEnd = 0;
-	while( p_devcon->GetData( m_stop, &timeEnd, sizeof( timeEnd ), 0 )!=S_OK );
-
-	D3D11_QUERY_DATA_TIMESTAMP_DISJOINT disjointData;
-	while( p_devcon->GetData( m_disjoint, &disjointData, sizeof( disjointData ), 0 )!=S_OK );
-
-	double time = -1.0f;
-	if( disjointData.Disjoint==FALSE ) {
-		UINT64 timeDelta = timeEnd - timeStart;
-		double frequency = static_cast< double >( disjointData.Frequency );
-		time = ( timeDelta / frequency ) * 1000.0f;
-	}
-	return time;
-}

### 2014-08-17 src/experiment/TimerDx.h

@@ -1,25 +1,0 @@
-#ifndef DV2549_EXPERIMENT_TIMERDX_H
-#define DV2549_EXPERIMENT_TIMERDX_H
-
-struct ID3D11Query;
-struct ID3D11Device;
-struct ID3D11DeviceContext;
-
-class TimerDx {
-public:
-	TimerDx();
-	~TimerDx();
-
-	HRESULT init( ID3D11Device* p_device );
-
-	void start( ID3D11DeviceContext* p_devcon );
-	void stop( ID3D11DeviceContext* p_devcon );
-	double time( ID3D11DeviceContext* p_devcon );
-protected:
-private:
-	ID3D11Query* m_start;
-	ID3D11Query* m_stop;
-	ID3D11Query* m_disjoint;
-};
-
-#endif // DV2549_EXPERIMENT_TIMERDX_H

### 2014-08-17 src/experiment/Util.cpp

@@ -1,30 +1,0 @@
-#include <stdafx.h>
-#include <sstream>
-#include <cstdlib> // atoi
-
-void CrudeMemoryLeakDetection() {
-	_CrtSetDbgFlag( _CRTDBG_ALLOC_MEM_DF | _CRTDBG_LEAK_CHECK_DF );
-	_CrtSetReportMode( _CRT_ERROR, _CRTDBG_MODE_DEBUG );
-}
-
-std::string Util::toString( int p_int ) {
-	std::stringstream ss;
-	ss << p_int;
-	return ss.str();
-}
-std::string Util::toString( unsigned p_uint ) {
-	std::stringstream ss;
-	ss << p_uint;
-	return ss.str();
-}
-
-const char* Util::toStringC( int p_int ) {
-	return toString( p_int ).c_str();
-}
-const char* Util::toStringC( unsigned p_uint ) {
-	return toString( p_uint ).c_str();
-}
-
-int Util::toInt( std::string p_string ) {
-	return atoi( p_string.c_str() );
-}

### 2014-08-17 src/experiment/Util.h

@@ -1,34 +1,0 @@
-#ifndef DV2549_EXPERIMENT_UTIL_H
-#define DV2549_EXPERIMENT_UTIL_H
-
-#ifdef EXPERIMENT_DEBUG
-#define _CRTDBG_MAP_ALLOC
-#include <stdlib.h>
-#include <crtdbg.h>
-void CrudeMemoryLeakDetection();
-#endif // EXPERIMENT_DEBUG
-
-#define ZERO_MEM( arg ) ZeroMemory( &arg, sizeof( arg ) );
-#define ASSERT_DELETE( arg ) assert( arg ); delete arg; arg = nullptr;
-
-template < class T >
-T* MatrixAlloc( unsigned p_rows, unsigned p_cols ) {
-	return (T*)calloc( p_rows * p_cols, sizeof( T ) );
-}
-template < class T >
-void MatrixFree( T* p_matrix ) {
-	free( p_matrix );
-}
-
-class Util {
-public:
-	static std::string toString( int p_int );
-	static std::string toString( unsigned p_uint );
-
-	static const char* toStringC( int p_int );
-	static const char* toStringC( unsigned p_uint );
-
-	static int toInt( std::string p_string );
-};
-
-#endif // DV2549_EXPERIMENT_UTIL_H

### 2014-08-17 src/experiment/UtilDx.cpp

@@ -1,56 +1,0 @@
-#include <stdafx.h>
-
-D3D::D3D() {
-	device = nullptr;
-	devcon = nullptr;
-	swapChain = nullptr;
-}
-D3D::~D3D() {
-	ASSERT_RELEASE( device );
-	ASSERT_RELEASE( devcon );
-	ASSERT_RELEASE( swapChain );
-}
-
-HRESULT UtilDx::createDeviceSwapChain( DescDeviceSwapChain& p_desc ) {
-	HRESULT hr = S_OK;
-
-	UINT deviceSwapChainFlags = 0;
-#ifdef EXPERIMENT_DEBUG
-	deviceSwapChainFlags |= D3D11_CREATE_DEVICE_DEBUG;
-#endif // EXPERIMENT_DEBUG
-
-	DXGI_SWAP_CHAIN_DESC scd; ZERO_MEM( scd );
-	scd.BufferCount			= 1;
-	scd.OutputWindow		= p_desc.hWnd;
-	scd.Windowed			= TRUE;
-	scd.BufferUsage			= DXGI_USAGE_RENDER_TARGET_OUTPUT | DXGI_USAGE_UNORDERED_ACCESS;
-	scd.SampleDesc.Count	= 1;
-	scd.SampleDesc.Quality	= 0;
-	scd.BufferDesc.Width	= p_desc.hWndWidth;
-	scd.BufferDesc.Height	= p_desc.hWndHeight;
-	scd.BufferDesc.Format	= DXGI_FORMAT_R8G8B8A8_UNORM;
-	scd.BufferDesc.RefreshRate.Numerator	= 60;
-	scd.BufferDesc.RefreshRate.Denominator	= 1;
-
-	D3D_FEATURE_LEVEL validFeatureLevels[] = {
-		D3D_FEATURE_LEVEL_11_1,
-		D3D_FEATURE_LEVEL_11_0
-	};
-
-	D3D_FEATURE_LEVEL sucessfulFeatureLevel;
-	hr = D3D11CreateDeviceAndSwapChain(
-		NULL,
-		p_desc.driverType,
-		NULL,
-		deviceSwapChainFlags,
-		validFeatureLevels,
-		ARRAYSIZE( validFeatureLevels ),
-		D3D11_SDK_VERSION,
-		&scd,
-		&p_desc.swapChain,
-		&p_desc.device,
-		&sucessfulFeatureLevel,
-		&p_desc.devcon );
-
-	return hr;
-}

### 2014-08-17 src/experiment/UtilDx.h

@@ -1,37 +1,0 @@
-#ifndef DV2549_EXPERIMENT_UTILDX_H
-#define DV2549_EXPERIMENT_UTILDX_H
-
-#define ASSERT_RELEASE( arg ) assert( arg ); arg->Release(); arg = nullptr;
-
-struct D3D {
-	D3D();
-	~D3D();
-
-	ID3D11Device* device;
-	ID3D11DeviceContext* devcon;
-
-	IDXGISwapChain* swapChain;
-};
-
-class UtilDx {
-public:
-	UtilDx();
-	~UtilDx();
-
-	struct DescDeviceSwapChain {
-		HWND hWnd;
-		unsigned hWndWidth;
-		unsigned hWndHeight;
-
-		D3D_DRIVER_TYPE driverType;
-
-		ID3D11Device* device;
-		ID3D11DeviceContext* devcon;
-		IDXGISwapChain* swapChain;
-	};
-	static HRESULT createDeviceSwapChain( DescDeviceSwapChain& p_desc );
-protected:
-private:
-};
-
-#endif // DV2549_EXPERIMENT_UTILDX_H

### 2014-08-17 src/experiment/UtilWin.cpp

@@ -1,62 +1,0 @@
-#include <stdafx.h>
-
-#include <UtilWin.h>
-
-Winfo::Winfo( HINSTANCE p_hInstance, HINSTANCE p_hInstancePrev, LPWSTR p_lpCmdLine, int p_nCmdShow ) {
-	hInstance		= p_hInstance;
-	hInstancePrev	= p_hInstancePrev;
-	lpCmdLine		= p_lpCmdLine;
-	nCmdShow		= p_nCmdShow;
-}
-Winfo::~Winfo() {
-	// Do nothing.
-}
-
-void MessageboxError( std::string p_what ) {
-	MessageBoxA(
-		NULL,
-		p_what.c_str(),
-		"Experiment Error!",
-		MB_OK | MB_ICONEXCLAMATION );
-	TerminateProcess();
-}
-
-void GetLastErrorAndTerminateProcess( LPTSTR p_function ) {
-	// Retrieve the system error message for the last-error code:
-	LPVOID lpMsgBuf;
-	LPVOID lpDisplayBuf;
-	DWORD dw = GetLastError(); 
-
-	FormatMessage(
-		FORMAT_MESSAGE_ALLOCATE_BUFFER | FORMAT_MESSAGE_FROM_SYSTEM | FORMAT_MESSAGE_IGNORE_INSERTS,
-		NULL,
-		dw,
-		MAKELANGID( LANG_NEUTRAL, SUBLANG_DEFAULT ),
-		(LPTSTR)&lpMsgBuf,
-		0, 
-		NULL );
-
-	// Display the error message:
-	lpDisplayBuf = (LPVOID)LocalAlloc(
-		LMEM_ZEROINIT, 
-		( lstrlen( (LPCTSTR)lpMsgBuf) + lstrlen( (LPCTSTR)p_function) + 40 ) * sizeof(TCHAR) ); 
-	StringCchPrintf( (LPTSTR)lpDisplayBuf, 
-		LocalSize( lpDisplayBuf ) / sizeof( TCHAR ),
-		TEXT( "%s failed with error %d: %s" ),
-		p_function, 
-		dw, 
-		lpMsgBuf ); 
-	MessageBox( NULL, (LPCTSTR)lpDisplayBuf, TEXT( "Error" ), MB_OK ); 
-
-	// Don't forget to clean up:
-	LocalFree(lpMsgBuf);
-	LocalFree(lpDisplayBuf);
-
-	// Finally, exit the responsible process:
[…]

### 2014-08-17 src/experiment/UtilWin.h

@@ -1,27 +1,0 @@
-#ifndef DV2549_EXPERIMENT_UTILWIN_H
-#define DV2549_EXPERIMENT_UTILWIN_H
-
-#define HRESULT_TO_BOOL( hr ) ( SUCCEEDED( hr ) )? true : false;
-#define BOOL_TO_HRESULT( boll ) ( boll==true )?	S_OK : S_FALSE;
-
-#include <strsafe.h>
-
-struct Winfo {
-public:
-	Winfo( HINSTANCE p_hInstance, HINSTANCE p_hInstancePrev, LPWSTR p_lpCmdLine, int p_nCmdShow );
-	~Winfo();
-
-	HINSTANCE hInstance;
-	HINSTANCE hInstancePrev;
-	LPWSTR lpCmdLine;
-	int nCmdShow;
-protected:
-private:
-};
-
-void MessageboxError( std::string p_what );
-
-void GetLastErrorAndTerminateProcess( LPTSTR p_function );
-void TerminateProcess();
-
-#endif // DV2549_EXPERIMENT_UTILWIN_H

### 2014-08-17 src/experiment/Win.cpp

@@ -1,105 +1,0 @@
-#include <stdafx.h>
-
-#include <Win.h>
-#include <UtilWin.h>
-
-Win::Win( HINSTANCE	p_hInstance,
-		 HINSTANCE	p_hInstancePrev,
-		 LPWSTR		p_lpCmdLine,
-		 int		p_nCmdShow ) {
-	m_hInstance		= p_hInstance;
-	m_hInstancePrev = p_hInstancePrev;
-	m_lpCmdLine		= p_lpCmdLine;
-	m_nCmdShow		= p_nCmdShow;
-
-	m_hWnd = nullptr;
-}
-Win::~Win() {
-	// Do nothing.
-}
-
-HRESULT Win::init() {
-	HRESULT hr = initWindow();
-	return hr;
-}
-
-unsigned Win::getWidth() {
-	RECT rct; GetClientRect( m_hWnd, &rct );
-	unsigned width = rct.right - rct.left;
-	return width;
-}
-unsigned Win::getHeight() {
-	RECT rct; GetClientRect( m_hWnd, &rct );
-	unsigned height = rct.bottom - rct.top;
-	return height;
-}
-HWND Win::getHWnd() const {
-	return m_hWnd;
-}
-
-HRESULT Win::initWindow() {
-	HRESULT hr = E_FAIL;
-
-	WNDCLASSEX wcex;
-	ZeroMemory( &wcex, sizeof( wcex ) ); // Use ZeroMemory to save some lines of code, and make up for it with a redundant comment.
-	wcex.cbSize			= sizeof( WNDCLASSEX ); 
-	wcex.style          = CS_HREDRAW | CS_VREDRAW;
-	wcex.lpfnWndProc    = Win::wWinProc;
-	wcex.hInstance      = m_hInstance;
-	wcex.hCursor        = LoadCursor( NULL, IDC_ARROW );
-	wcex.hbrBackground  = (HBRUSH)( COLOR_WINDOW + 1 );
-	wcex.lpszMenuName   = NULL;
-	wcex.lpszClassName  = g_windowClassName;
-
-	LPTSTR lastMethod = "RegisterClassEx";
-	if( RegisterClassEx( &wcex )!=0 ) { // Registers a window class for subsequent use in calls to the CreateWindow or CreateWindowEx function.
-		RECT rct = { 0, 0, g_windowWidth, g_windowHeight };
[…]

### 2014-08-17 src/experiment/Win.h

@@ -1,38 +1,0 @@
-#ifndef DV2549_EXPERIMENT_WIN_H
-#define DV2549_EXPERIMENT_WIN_H
-
-// Magic numbers and bad jokes:
-static const unsigned g_windowWidth		= 800;
-static const unsigned g_windowHeight	= 800;
-
-static const LPCTSTR g_windowTitle		= "Experiment";
-static const LPCTSTR g_windowClassName	= "ExperimentWindow";
-
-class Win {
-public:
-	Win( HINSTANCE	p_hInstance,
-		HINSTANCE	p_hInstancePrev,
-		LPWSTR		p_lpCmdLine,
-		int			p_nCmdShow );
-	~Win();
-
-	HRESULT init();
-
-	unsigned getWidth();
-	unsigned getHeight();
-	HWND getHWnd() const;
-
-	// This method is totally off limits. Hands off.
-	static LRESULT CALLBACK wWinProc( HWND hWnd, UINT message, WPARAM wParam, LPARAM lParam );
-protected:
-private:
-	HRESULT initWindow();
-
-	HWND		m_hWnd;
-	HINSTANCE	m_hInstance;
-	HINSTANCE	m_hInstancePrev;
-	LPWSTR		m_lpCmdLine;
-	int			m_nCmdShow;
-};
-
-#endif // DV2549_EXPERIMENT_WIN_H

### 2014-08-17 src/experiment/main.cpp

@@ -1,97 +1,0 @@
-#include <stdafx.h>
-
-#include <Experiment.h>
-
-void MemleakDetect() {
-#ifdef EXPERIMENT_DEBUG
-	CrudeMemoryLeakDetection();
-#endif // EXPERIMENT_DEBUG
-}
-
-int runExperiment( Winfo* p_winfo, ExperimentConf p_conf ) {
-	int retVal = -1;
-	HRESULT hr = S_OK;
-	switch( p_conf.confPrecision ) {
-	case ExperimentPrecisions_INT: {
-		Experiment< int > experiment( p_winfo, p_conf );
-		HRESULT hr = experiment.init();
-		if( SUCCEEDED( hr ) ) {
-			retVal = experiment.run( 0, nullptr );
-		}
-		break;
-		}
-	case ExperimentPrecisions_FLOAT: {
-		Experiment< float > experiment( p_winfo, p_conf );
-		HRESULT hr = experiment.init();
-		if( SUCCEEDED( hr ) ) {
-			retVal = experiment.run( 0, nullptr );
-		}
-		break;
-		}
-	}
-	if( FAILED( hr ) ) {
-		retVal = (int)hr;
-	}
-	return retVal;
-}
-
-ExperimentFxs lpwstrToFx( LPWSTR p_lpwstr ) {
-	ExperimentFxs fx;
-	if( wcscmp( p_lpwstr, L"BASIC" )==0 ) {
-		fx = ExperimentFxs_MULT_BASIC;
-	} else if( wcscmp( p_lpwstr, L"TILE" )==0 ) {
-		fx = ExperimentFxs_MULT_TILE;
-	} else {
-		MessageboxError( "The specified kernel is not supported." );
-	}
-	return fx;
-}
-ExperimentAccelerations lpwstrToAcceleration( LPWSTR p_lpwstr ) {
-	ExperimentAccelerations acceleration;
-	if( wcscmp( p_lpwstr, L"HARD" )==0 ) {
-		acceleration = ExperimentAccelerations_HARD;
-	} else if( wcscmp( p_lpwstr, L"SOFT" )==0 ) {
-		acceleration = ExperimentAccelerations_SOFT;
-	} else if( wcscmp( p_lpwstr, L"WARP" )==0 ) {
-		acceleration = ExperimentAccelerations_WARP;
-	} else {
-		MessageboxError( "The specified driver acceleration is not supported." );
-	}
-	return acceleration;
-}
[…]

### 2014-08-17 src/experiment/stdafx.h

@@ -1,18 +1,0 @@
-#ifndef DV2549_EXPERIMENT_STDAFX_H
-#define DV2549_EXPERIMENT_STDAFX_H
-
-#include <string>
-#include <windows.h>
-
-#include <Common.h>
-#include <CommonDx.h>
-#include <CommonWin.h>
-
-#include <Conf.h>
-#include <Util.h>
-#include <UtilDx.h>
-#include <UtilWin.h>
-
-#include <ExceptionExperiment.h>
-
-#endif // DV2549_EXPERIMENT_STDAFX_H

### 2014-08-17 src/matrixgen/Ampersand.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Ampersand.h>

### 2014-08-17 src/matrixgen/Ampersand.h

@@ -1,59 +1,0 @@
-#ifndef DV2549_MATRIXGEN_AMPERSAND_H
-#define DV2549_MATRIXGEN_AMPERSAND_H
-
-template < class T >
-class Matrix;
-
-#include <Amphack.h>
-
-/*
-The constructor of Ampersand, as well as matrixPopulate - or any use of C++ AMP it seems - seems to cause memory leaks.
-I'm not sure what causes it, whether or not it is expected behaviour or if I've done something wrong.
-*/
-
-template < class T >
-class Ampersand {
-public:
-	Ampersand() {
-		concurrency::accelerator default_device;
-		std::wcout << std::endl << L"Initializing C++ AMP with device: " << default_device.get_description() + L".";
-		if( default_device==concurrency::accelerator( concurrency::accelerator::direct3d_ref) ) {
-			std::cout << std::endl << "Warning. Running C++ AMP using a slow emulator.";
-		}
-		srand( time( 0 ) );
-	}
-	~Ampersand() {
-		// Do nothing.
-	}
-
-	// This is ugly! Quick hack performed to get rid of obscure linker errors. Fix this! 
-	template < class T >
-	void matrixPopulate( Matrix< T >* p_matrix, int p_min, int p_max ) {
-		throw ExceptionMatrixgen( "Non-supported datatype!" );
-	}
-	template <>
-	void matrixPopulate( Matrix< int >* p_matrix, int p_min, int p_max ) {
-		Amphack::Amp_MatrixPopulate( p_matrix, p_min, p_max );
-	}
-	template <>
-	void matrixPopulate( Matrix< float >* p_matrix, int p_min, int p_max ) {
-		Amphack::Amp_MatrixPopulate( p_matrix, p_min, p_max );
-	}
-
-	template < class T >
-	void matrixMultiply( Matrix< T >* p_c, Matrix< T >* p_a, Matrix< T >* p_b ) {
-		throw ExceptionMatrixgen( "Non-supported datatype!" );
-	}
-	template <>
-	void matrixMultiply( Matrix< int >* p_c, Matrix< int >* p_a, Matrix< int >* p_b ) {
-		Amphack::Amp_MatrixMultiply( p_c, p_a, p_b );
-	}
-	template <>
-	void matrixMultiply( Matrix< float >* p_c, Matrix< float >* p_a, Matrix< float >* p_b ) {
[…]

### 2014-08-17 src/matrixgen/Amphack.cpp

@@ -1,130 +1,0 @@
-#include <stdafx.h>
-
-#include <amp_tinymt_rng.h>
-
-#include <Matrix.h>
-#include <Amphack.h>
-
-void Amphack::Amp_MatrixPopulate( Matrix< int >* p_matrix, int p_min, int p_max ) {
-	const unsigned rows = p_matrix->getNumRows();
-	const unsigned cols = p_matrix->getNumCols();
-	int* matrix = p_matrix->get();
-
-	// Initialize RNG:
-	long seed = rand();
-	concurrency::extent< 2 > e_size( rows, cols );
-	tinymt_collection< 2 > rng( e_size, seed );
-	char ref[50]; sprintf_s( ref, "%d", matrix );
-	std::cout << std::endl << "C++ AMP RNG initialized with seed: " + Util::toString( seed ) + "." << std::endl << "Proceeding to generate random numbers for matrix: " + std::string( ref ) + ".";
-
-	concurrency::array_view< int, 2 > ioMatrix( rows, cols, matrix );
-	parallel_for_each(
-		ioMatrix.extent,
-		[=]( concurrency::index< 2 > idx ) restrict( amp ) {
-			int row = idx[ 0 ];
-			int col = idx[ 1 ];
-
-			auto t = rng[ idx ];
-			float random = t.next_single(); // Gives a floating point in-between 0-1.
-			ioMatrix[ row ][ col ] = int( concurrency::precise_math::nearbyint( random * p_max + p_min ) );
-	}
-	);
-	ioMatrix.synchronize();
-}
-void Amphack::Amp_MatrixPopulate( Matrix< float >* p_matrix, int p_min, int p_max ) {
-	const unsigned rows = p_matrix->getNumRows();
-	const unsigned cols = p_matrix->getNumCols();
-	float* matrix = p_matrix->get();
-
-	// Initialize RNG:
-	long seed = rand();
-	concurrency::extent< 2 > e_size( rows, cols );
-	tinymt_collection< 2 > rng( e_size, seed );
-	char ref[50]; sprintf_s( ref, "%d", matrix );
-	std::cout << std::endl << "C++ AMP RNG initialized with seed: " + Util::toString( seed ) + "." << std::endl << "Proceeding to generate random numbers for matrix: " + std::string( ref ) + ".";
-
-	concurrency::array_view< float, 2 > ioMatrix( rows, cols, matrix );
[…]

### 2014-08-17 src/matrixgen/Amphack.h

@@ -1,27 +1,0 @@
-#ifndef DV2549_MATRIXGEN_AMPHACK_H
-#define DV2549_MATRIXGEN_AMPHACK_H
-
-template < class T >
-class Matrix;
-
-static const unsigned TileSize = 1;
-
-/* 
-Using Amphack to seperate all C++ AMP RNG-code from the include-hell caused by severe templating.
-Encountered hopeless link-errors when including C++ AMP RNG.
-Get rid of this hack!
-*/
-
-class Amphack {
-public:
-	// Tile theses implementations in order to be able to generate larger matrices:
-	static void Amp_MatrixPopulate( Matrix< int >* p_matrix, int p_min, int p_max );
-	static void Amp_MatrixPopulate( Matrix< float >* p_matrix, int p_min, int p_max );
-
-	static void Amp_MatrixMultiply( Matrix< int >* p_c, Matrix< int >* p_a, Matrix< int >* p_b );
-	static void Amp_MatrixMultiply( Matrix< float >* p_c, Matrix< float >* p_a, Matrix< float >* p_b );
-protected:
-private:
-};
-
-#endif // DV2549_MATRIXGEN_AMPHACK_H

### 2014-08-17 src/matrixgen/Common.h

@@ -1,6 +1,0 @@
-#ifndef DV2549_MATRIXGEN_COMMON_H
-#define DV2549_MATRIXGEN_COMMON_H
-
-#include <Conf.h>
-
-#endif // DV2549_MATRIXGEN_COMMON_H

### 2014-08-17 src/matrixgen/Conf.h

@@ -1,12 +1,0 @@
-#ifndef DV2549_MATRIXGEN_CONF_H
-#define DV2549_MATRIXGEN_CONF_H
-
-static const std::string g_mxgPath = "../../../mxg/";
-
-// Currently used to print precision. Can be phased out.
-enum MatrixgenPrecisions {
-	MatrixgenPrecisions_INT = 0,
-	MatrixgenPrecisions_FLOAT = 1
-};
-
-#endif // DV2549_MATRIXGEN_CONF_H

### 2014-08-17 src/matrixgen/ExceptionMatrixgen.cpp

@@ -1,13 +1,0 @@
-#include <stdafx.h>
-
-ExceptionMatrixgen::ExceptionMatrixgen( std::string p_func ) throw() : exception() {
-	m_func = p_func;
-}
-ExceptionMatrixgen::~ExceptionMatrixgen() throw() {
-	// Do nothing.
-}
-
-const char* ExceptionMatrixgen::what() const throw() {
-	std::string what = "Experiment - Exception: " + m_func;
-	return what.c_str();
-}

### 2014-08-17 src/matrixgen/ExceptionMatrixgen.h

@@ -1,14 +1,0 @@
-#ifndef DV2549_MATRIXGEN_EXCEPTIONMATRIXGEN_H
-#define DV2549_MATRIXGEN_EXCEPTIONMATRIXGEN_H
-
-class ExceptionMatrixgen : public std::exception {
-public:
-	ExceptionMatrixgen( std::string p_func ) throw();
-	virtual ~ExceptionMatrixgen() throw();
-
-	virtual const char* what() const throw();
-private:
-	std::string m_func;
-};
-
-#endif // DV2549_MATRIXGEN_EXCEPTIONMATRIXGEN_H

### 2014-08-17 src/matrixgen/Matrix.h

@@ -1,46 +1,0 @@
-#ifndef DV2549_MATRIXGEN_MATRIX_H
-#define DV2549_MATRIXGEN_MATRIX_H
-
-template < class T >
-class Matrix {
-public:
-	Matrix( unsigned p_rows, unsigned p_cols ) {
-		m_rows = p_rows;
-		m_cols = p_cols;
-
-		m_ = MatrixAlloc< T >( p_rows, p_cols );
-		std::memset( m_, 0, sizeof( T ) * m_rows * m_cols );
-	}
-	~Matrix() {
-		assert( m_ );
-		MatrixFree( m_ );
-	}
-
-	T* get() const {
-		return m_;
-	}
-	unsigned getNumRows() const {
-		return m_rows;
-	}
-	unsigned getNumCols() const {
-		return m_cols;
-	}
-
-	std::string toString() {
-		std::string string = "\n";
-		for( int row = 0; row < m_rows; row++ ) {
-			for( int col = 0; col < m_cols; col++ ) {
-				string += Util::toString( m_[ row * m_rows + col ] ) + "  ";
-			}
-			string += "\n";
-		}
-		return string;
-	}
-protected:
-private:
-	T* m_;
-	unsigned m_rows;
-	unsigned m_cols;
-};
-
-#endif // DV2549_MATRIXGEN_MATRIX_H

### 2014-08-17 src/matrixgen/Matrixgen.cpp

@@ -1,3 +1,0 @@
-#include <stdafx.h>
-
-#include <Matrixgen.h>

### 2014-08-17 src/matrixgen/Matrixgen.h

@@ -1,73 +1,0 @@
-#ifndef DV2549_MATRIXGEN_MATRIXGEN_H
-#define DV2549_MATRIXGEN_MATRIXGEN_H
-
-enum MatrixgenPrecisions;
-
-#include <Matrix.h>
-#include <Reader.h>
-#include <Printer.h>
-#include <Ampersand.h>
-
-template < class T >
-class Matrixgen {
-public:
-	Matrixgen( MatrixgenPrecisions p_precision, unsigned p_dim, unsigned p_min, unsigned p_max, bool p_pop ) {
-		m_precision = p_precision;
-		m_dim = p_dim;
-		m_min = p_min;
-		m_max = p_max;
-		m_pop = p_pop;
-	}
-	~Matrixgen() {
-		assert( m_a ); delete m_a;
-		assert( m_b ); delete m_b;
-		assert( m_c ); delete m_c;
-	}
-
-	bool run() {
-		bool success = true;
-
-		Ampersand< T >* amp = new Ampersand< T >();
-		if( m_pop==true ) { // if instructed to populate matrices
-			m_a = new Matrix< T >( m_dim, m_dim );
-			m_b = new Matrix< T >( m_dim, m_dim );
-
-			amp->matrixPopulate( m_a, m_min, m_max );
-			amp->matrixPopulate( m_b, m_min, m_max );
-		} else { // load from file
-			m_a = Reader< T >::loadMatrix( g_mxgPath + "a.mxg" );
-			m_b = Reader< T >::loadMatrix( g_mxgPath + "b.mxg" );
-			assert( m_a!=nullptr );
-			assert( m_a!=nullptr );
-		}
-
-		m_c = new Matrix< T >( m_dim, m_dim );
-		amp->matrixMultiply( m_c, m_a, m_b );
-
-		Printer< T >* printer = nullptr;
-		if( m_pop==true ) {
-			printer = new Printer< T >( m_precision, m_a, m_b, m_c );
-		} else {
-			printer = new Printer< T >( m_precision, nullptr, nullptr, m_c );
-		}
-		success = printer->print();
-
-		delete amp;
-		delete printer;
-		return success;
-	}
-protected:
-private:
-	MatrixgenPrecisions m_precision;
-	unsigned m_dim;
-	unsigned m_max;
-	unsigned m_min;
-	bool m_pop;
-
-	Matrix< T >* m_a;
-	Matrix< T >* m_b;
[…]

### 2014-08-17 src/matrixgen/Printer.h

@@ -1,90 +1,0 @@
-#ifndef DV2549_MATRIXGEN_PRINTER_H
-#define DV2549_MATRIXGEN_PRINTER_H
-
-#include <Matrix.h>
-
-template < class T >
-class Printer {
-public:
-	Printer( MatrixgenPrecisions p_precision, Matrix< T >* p_a, Matrix< T >* p_b, Matrix< T >* p_c ) {
-		m_precision = p_precision;
-		m_a = p_a;
-		m_b = p_b;
-		m_c = p_c;
-	}
-	~Printer() {
-		// Do nothing.
-	}
-
-	bool print() {
-		bool success = true;
-		if( success==true && m_a!=nullptr ) {
-			success = printToFile( "a.mxg", m_a );
-		}
-		if( success==true && m_b!=nullptr ) {
-			success = printToFile( "b.mxg", m_b );
-		}
-		if( success==true ) {
-			printToFileBinary( "ref.mxgb", m_c );
-		}
-		return success;
-	}
-protected:
-	bool printToFile( std::string p_filename, Matrix< T >* p_matrix ) {
-		std::cout << "\n" << "Printing matrix to file: " << p_filename << ".";
-
-		bool success = true;
-		std::ofstream mxg;
-		mxg.open( g_mxgPath + p_filename );
-		if( mxg.is_open()==true ) {
-			unsigned precision = (int)m_precision;
-			unsigned rows = p_matrix->getNumRows();
-			unsigned cols = p_matrix->getNumCols();
-			mxg << "Precision:\t"	<< precision	<< "\n"
-				<< "Rows:\t"		<< rows			<< "\n" 
-				<< "Columns:\t"		<< cols;
-
-			unsigned numElements = rows * cols;
-			T* matrix = p_matrix->get();
-			for( unsigned i = 0; i<numElements; i++ ) {
-				mxg << "\n" << matrix[ i ];
-			}
-		} else {
-			success = false;
-		}
-		mxg.close();
-
-		return success;
-	}
-	bool printToFileBinary( std::string p_filename, Matrix< T >* p_matrix ) {
-		std::cout << "\n" << "Printing matrix to file: " << p_filename << ".";
-
-		std::ofstream mxgb( g_mxgPath + p_filename, std::ios_base::binary );
-		bool success = mxgb.is_open();
-		if( success==true ) {
-			unsigned precision = (int)m_precision;
-			unsigned rows = p_matrix->getNumRows();
[…]

### 2014-08-17 src/matrixgen/Reader.h

@@ -1,40 +1,0 @@
-#ifndef DV2549_MATRIXGEN_READER_H
-#define DV2549_MATRIXGEN_READER_H
-
-#include <Matrix.h>
-
-template < class T >
-class Reader {
-public:
-	Reader() {
-	}
-	~Reader() {
-		// Do nothing.
-	}
-
-	static Matrix< T >* loadMatrix( std::string p_filename ) {
-		std::string temp;
-		int precision;
-		unsigned rows, cols;
-		Matrix< T >* matrix = nullptr;
-
-		std::ifstream mxg( p_filename );
-		if( mxg.is_open() ) {
-			mxg >> temp >> precision >> temp >> rows >> temp >> cols;
-
-			unsigned i = 0;
-			matrix = new Matrix< T >( rows, cols );
-			T* m = matrix->get();
-			while( mxg.eof()==false ) {
-				mxg >> m[ i ];
-				i++;
-			}
-		}
-
-		return matrix;
-	}
-protected:
-private:
-};
-
-#endif // DV2549_MATRIXGEN_READER_H

### 2014-08-17 src/matrixgen/Util.cpp

@@ -1,28 +1,0 @@
-#include <stdafx.h>
-
-void CrudeMemoryLeakDetection() {
-	_CrtSetDbgFlag( _CRTDBG_ALLOC_MEM_DF | _CRTDBG_LEAK_CHECK_DF );
-	_CrtSetReportMode( _CRT_ERROR, _CRTDBG_MODE_DEBUG );
-}
-
-std::string Util::toString( int p_int ) {
-	std::stringstream ss;
-	ss << p_int;
-	return ss.str();
-}
-std::string Util::toString( unsigned p_uint ) {
-	std::stringstream ss;
-	ss << p_uint;
-	return ss.str();
-}
-
-const char* Util::toStringC( int p_int ) {
-	return toString( p_int ).c_str();
-}
-const char* Util::toStringC( unsigned p_uint ) {
-	return toString( p_uint ).c_str();
-}
-
-int Util::toInt( std::string p_string ) {
-	return atoi( p_string.c_str() );
-}

### 2014-08-17 src/matrixgen/Util.h

@@ -1,37 +1,0 @@
-#ifndef DV2549_MATRIXGEN_UTIL_H
-#define DV2549_MATRIXGEN_UTIL_H
-
-#ifdef MATRIXGEN_DEBUG
-#define _CRTDBG_MAP_ALLOC
-#include <stdlib.h>
-#include <crtdbg.h>
-void CrudeMemoryLeakDetection();
-#endif // MATRIXGEN_DEBUG
-
-template < class T >
-T* MatrixAlloc( unsigned p_rows, unsigned p_cols ) {
-	T* matrix;
-	matrix = (T*)calloc( p_rows * p_cols, sizeof( T ) );
-
-	return matrix;
-}
-template < class T >
-void MatrixFree( T* p_matrix ) {
-	free( p_matrix );
-}
-
-class Util {
-public:
-	Util();
-	~Util();
-
-	static std::string toString( int p_int );
-	static std::string toString( unsigned p_uint );
-
-	static const char* toStringC( int p_int );
-	static const char* toStringC( unsigned p_uint );
-
-	static int toInt( std::string p_string );
-};
-
-#endif // DV2549_MATRIXGEN_UTIL_H

### 2014-08-17 src/matrixgen/main.cpp

@@ -1,52 +1,0 @@
-#include <stdafx.h>
-
-#include <Matrixgen.h>
-
-void MemLeakDetect() {
-#ifdef MATRIXGEN_DEBUG
-	CrudeMemoryLeakDetection();
-#endif // MATRIXGEN_DEBUG
-}
-
-int main( int argc, char* argv[] ) {
-	MemLeakDetect();
-	std::cout << "\n" << "---" << "\n" << "Matrixgen Utility" << "\n" << "---" << "\n";
-
-	int result = 1;
-	unsigned numExpectedArgs = 6; // First argument is the command invoking application.
-	if( argc==numExpectedArgs ) {
-		std::string precision( argv[ 1 ] );
-		unsigned dim = atoi( argv[ 2 ] );
-		unsigned min = atoi( argv[ 3 ] );
-		unsigned max = atoi( argv[ 4 ] );
-		bool pop = (atoi( argv[ 5 ] )!=0);
-		if( pop==true ) {
-			std::cout << "Populate flag specified as true. Will populate matrices a & b.\n";
-		} else {
-			std::cout << "Populate flag specified as false. Will only compile reference matrix ref.mxgb.\n";
-		}
-
-		if( precision=="INT" ) {
-			Matrixgen< int > mgen( MatrixgenPrecisions_INT, dim, min, max, pop );
-			result = (int)!mgen.run();
-		} else if( precision=="FLOAT" ) {
-			Matrixgen< float > mgen( MatrixgenPrecisions_FLOAT, dim, min, max, pop );
-			result = (int)!mgen.run();
-		} else {
-			std::cerr << "Unsupported precision: " << precision;
-		}
-	} else {
-		std::cerr << "Usage: " << argv[ 0 ] << " PRECISION [ INT FLOAT ] DIM MIN MAX POPULATE" << std::endl;
-	}
-
-	if( result==0 ) {
-		std::cout << "\n" << "Matrixgen was run sucessfully.";
-	} else {
-		std::cout << "\n" << "Matrixgen encountered an error!";
-	}
-
-#ifdef MATRIXGEN_DEBUG
-	getchar();
-#endif // MATRIXGEN_DEBUG
-	return result;
-}

### 2014-08-17 src/matrixgen/stdafx.h

@@ -1,19 +1,0 @@
-#ifndef DV2549_MATRIXGEN_STDAFX_H
-#define DV2549_MATRIXGEN_STDAFX_H
-
-#include <amp.h>
-#include <amp_math.h>
-
-#include <time.h>
-#include <string>
-#include <cassert>
-#include <sstream>
-#include <fstream>
-#include <iostream>
-#include <exception>
-
-#include <Conf.h>
-#include <Util.h>
-#include <ExceptionMatrixgen.h>
-
-#endif // DV2549_MATRIXGEN_STDAFX_H

### 2014-08-17 paper/GAME_HARD_01_INTRODUCTION.tex
Implemented build script in Perl rather than Python because of downtime.

--- 2014-07-26 tex/GAME_HARD_01_INTRODUCTION.tex
@@
 A preferred solution to this problem is to simulate GPU workloads on CPUs~\citeweb[]{drivertypes}, such as described by Kerr~et~al.~\cite[p.~416-419]{Hwu:2011:GCG:2103614} concerning the implementation of the GPU~Ocelot compilation framework~\citeweb[]{gpuocelot}, often in exchange for substantial performance implications.
-Other resons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existant, when hardware is busy, or otherwise unavailable~\citeweb[]{warp}.
+Other reasons to simulate GPU-kernels may concern pre-silicon development - that is, development for hardware not yet existent, when hardware is busy, or otherwise unavailable~\citeweb[]{warp}.
 

### 2014-08-17 build.pl

@@ -1,0 +1,27 @@
+#!/usr/local/bin/perl
+
+sub help_and_exit{
+    print "Usage: build.pl paper|presentation\n";
+    exit;
+}
+
+$num_args = $#ARGV + 1;
+if($num_args!=1) {
+    help_and_exit();
+}
+
+$target=$ARGV[0];
+if($target eq "paper"){
+    system("gnuplot msswarp.gnuplot");
+    chdir "paper/";
+    system("pdflatex -shell-escape GAME_HARD_01.tex");
+    system("bibtex web.aux");
+    system("bibtex GAME_HARD_01.aux");
+    system("pdflatex -shell-escape GAME_HARD_01.tex");
+    system("pdflatex -shell-escape GAME_HARD_01.tex");
+} elsif($target eq "presentation"){
+    print "Not yet implemented!";
+    exit;
+} else{
+    help_and_exit();
+}

### 2014-08-17 build.py

@@ -1,20 +1,0 @@
-#!/bin/python
-
-import os
-import sys
-import shutil
-import subprocess
-
-subprocess.call(["gnuplot", "msswarp.gnuplot"])
-
-os.chdir('tex/')
-
-subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)
-
-subprocess.call(["bibtex", "web.aux"])
-subprocess.call(["bibtex", "GAME_HARD_01.aux"])
-
-subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)
-subprocess.call("pdflatex -shell-escape GAME_HARD_01.tex", shell=True)
-
-shutil.copyfile("GAME_HARD_01.pdf", "../GAME_HARD_01.pdf")

### 2014-08-24 build.pl
Added presentation build using the bth-beamer-style.

@@ -1,5 +1,7 @@
 #!/usr/local/bin/perl
 
+use File::Copy;
+
 sub help_and_exit{
     print "Usage: build.pl paper|presentation\n";
     exit;
@@ -19,9 +21,12 @@ if($target eq "paper"){
     system("bibtex GAME_HARD_01.aux");
     system("pdflatex -shell-escape GAME_HARD_01.tex");
     system("pdflatex -shell-escape GAME_HARD_01.tex");
+    copy("GAME_HARD_01.pdf", "../GAME_HARD_01.pdf") or die "Failed to copy: $!";
 } elsif($target eq "presentation"){
-    print "Not yet implemented!";
-    exit;
+    chdir "presentation/";
+    system("pdflatex GAME_HARD_01_PRESENTATION.tex");
+    copy("GAME_HARD_01_PRESENTATION.pdf", "../GAME_HARD_01_PRESENTATION.pdf")
+        or die "Failed to copy: $!";
 } else{
     help_and_exit();
 }

### 2014-08-24 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Added presentation outline.

% GAME_HARD_01_PRESENTATION_CONCLUSION.tex
\section{Conclusion}

% SUBSECTION
\subsection{Subsection}
\begin{frame}
\frametitle{SUBSECTION}

\end{frame}

### 2014-08-24 build.pl

@@ -25,6 +25,7 @@ if($target eq "paper"){
 } elsif($target eq "presentation"){
     chdir "presentation/";
     system("pdflatex GAME_HARD_01_PRESENTATION.tex");
+    system("pdflatex GAME_HARD_01_PRESENTATION.tex");
     copy("GAME_HARD_01_PRESENTATION.pdf", "../GAME_HARD_01_PRESENTATION.pdf")
         or die "Failed to copy: $!";
 } else{

### 2014-09-07 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Added draft results tables to section Conclusion.

@@
 
-% SUBSECTION
-\subsection{Subsection}
+% Arrowhead command. Sets a tikz node for rendering an entire arrow.
+\newcommand\ah[2]{\tikz[remember picture,baseline]\node[inner sep=2pt,outer sep=0](#1){#2};}
+% Arrow command. Draws an arrow between two tikz nodes.
+\newcommand\arrow[2]{%
+  \begin{tikzpicture}[remember picture, overlay, >=stealth, shift={(0,0)}]
+    \draw[->] (#1) to (#2);
+  \end{tikzpicture}%
+}
+
+% RESULTS
+\subsection{Results}
 \begin{frame}
-\frametitle{SUBSECTION}
+\frametitle{RESULTS}
+
+\begin{columns}[T]
+  \begin{column}{\widthof{I}}
+    \begin{sideways}
+      Integer
+    \end{sideways}
+  \end{column}
+  \begin{column}{\textwidth - \widthof{I}}
+    \begin{center}
+      \begin{tabular}{r|r|r|r|}
+        \cline{2-3}
+        & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+        \multicolumn{1}{|l|}{\textbf{HARD}}     & \ah{hh1}{$1.16$}      & \ah{hf1}{\phantom{0000}$0.24$}\ah{spc}{}      & \ah{spc}{$-79.3\%$} \\ \hline \hline
+        \multicolumn{1}{|l|}{\textbf{SOFT}}     & \ah{vh2}{}\ah{hh2}{$11610.02$}        & \ah{hf2}{\phantom{0}$9866.40$}\ah{vh1}{}      & \ah{spc}{$-15.0\%$} \\ \hline
+        \multicolumn{1}{|l|}{\textbf{WARP}}     & \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}      & \ah{hf3}{\phantom{000}$18.97$}\ah{vf1}{}      & \ah{spc}{$+23.9\%$} \\ \hline
+        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
+      \end{tabular}
+      \arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+      \arrow{hh2}{hf2}
+      \arrow{hh3}{hf3}
+      \arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+      \arrow{vh2}{vf2}
+    \end{center}
+  \end{column}
+\end{columns}
+
+\begin{columns}[T]
+  \begin{column}{\widthof{I}}
+    \begin{sideways}
+      Floating point
+    \end{sideways}
+  \end{column}
+  \begin{column}{\textwidth - \widthof{I}}
+    \begin{center}
+      \begin{tabular}{r|r|r|r|}
+        \cline{2-3}
+        & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
+        \multicolumn{1}{|l|}{\textbf{HARD}}     & \ah{hh1}{$0.77$}      & \ah{hf1}{\phantom{0000}$0.22$}\ah{spc}{}      & \ah{spc}{$-71.4\%$} \\ \hline \hline
+        \multicolumn{1}{|l|}{\textbf{SOFT}}     & \ah{vh1}{}\ah{hh2}{$10247.03$}        & \ah{hf2}{$10909.88$}\ah{vh2}{}        & \ah{spc}{$+6.5\%$} \\ \hline
+        \multicolumn{1}{|l|}{\textbf{WARP}}     & \ah{vf1}{}\phantom{000}\ah{hh3}{$14.08$}      & \ah{hf3}{\phantom{000}$17.44$}\ah{vf2}{}      & \ah{spc}{$+23.9\%$} \\ \hline
+        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
+      \end{tabular}
+      \arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+      \arrow{hh2}{hf2}
+      \arrow{hh3}{hf3}
+      \arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+      \arrow{vh2}{vf2}
+    \end{center}
+  \end{column}
+\end{columns}
 
 \end{frame}
+
+% Results
+
+% Impact of Shared Memory
+
+% Future Work
+
+% Source code and data available
+% May be downloaded if you want to replicate the test

### 2014-09-07 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Cleaned up the results tables a bit.

--- 2014-08-24 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
@@
 
-% SUBSECTION
-\subsection{Subsection}
+% Arrowhead command. Sets a tikz node for rendering an entire arrow.
+\newcommand\ah[2]{\tikz[remember picture,baseline]\node[inner sep=2pt,outer sep=0](#1){#2};}
+% Arrow command. Draws an arrow between two tikz nodes.
+\newcommand\arrow[2]{%
+  \begin{tikzpicture}[remember picture, overlay, >=stealth, shift={(0,0)}]
+    \draw[->] (#1) to (#2);
+  \end{tikzpicture}%
+}
+
+% RESULTS
+\subsection{Results}
 \begin{frame}
-\frametitle{SUBSECTION}
+\frametitle{RESULTS}
+
+\begin{columns}[T]
+  \begin{column}{\widthof{I}}
+    \begin{sideways}
+      Integer
+    \end{sideways}
+  \end{column}
+  \begin{column}{\textwidth - \widthof{I}}
+    \begin{center}
+      \begin{tabular}{r|r|r|r|}
+        \cline{2-3}
+        & \multicolumn{1}{|c|}{1. Basic} & \multicolumn{1}{|c|}{2. Tiled} \\ \hline
+        \multicolumn{1}{|l|}{Hard}     & \ah{hh1}{$1.16$}      & \ah{hf1}{\phantom{0000}$0.24$}\ah{spc}{}      & \ah{spc}{$-79.3\%$} \\ \hline \hline
+        \multicolumn{1}{|l|}{Soft}     & \ah{vh2}{}\ah{hh2}{$11610.02$}        & \ah{hf2}{\phantom{0}$9866.40$}\ah{vh1}{}      & \ah{spc}{$-15.0\%$} \\ \hline
+        \multicolumn{1}{|l|}{WARP}     & \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}      & \ah{hf3}{\phantom{000}$18.97$}\ah{vf1}{}      & \ah{spc}{$+23.9\%$} \\ \hline
+        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
+      \end{tabular}
+      \arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+      \arrow{hh2}{hf2}
+      \arrow{hh3}{hf3}
+      \arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+      \arrow{vh2}{vf2}
+    \end{center}
+  \end{column}
+\end{columns}
+
+\begin{columns}[T]
+  \begin{column}{\widthof{I}}
+    \begin{sideways}
+      Floating point
+    \end{sideways}
+  \end{column}
+  \begin{column}{\textwidth - \widthof{I}}
+    \begin{center}
+      \begin{tabular}{r|r|r|r|}
+        \cline{2-3}
+        & \multicolumn{1}{|c|}{1. Basic} & \multicolumn{1}{|c|}{2. Tiled} \\ \hline
+        \multicolumn{1}{|l|}{Hard}     & \ah{hh1}{$0.77$}      & \ah{hf1}{\phantom{0000}$0.22$}\ah{spc}{}      & \ah{spc}{$-71.4\%$} \\ \hline \hline
+        \multicolumn{1}{|l|}{Soft}     & \ah{vh1}{}\ah{hh2}{$10247.03$}        & \ah{hf2}{$10909.88$}\ah{vh2}{}        & \ah{spc}{$+6.5\%$} \\ \hline
+        \multicolumn{1}{|l|}{WARP}     & \ah{vf1}{}\phantom{000}\ah{hh3}{$14.08$}      & \ah{hf3}{\phantom{000}$17.44$}\ah{vf2}{}      & \ah{spc}{$+23.9\%$} \\ \hline
+        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
+      \end{tabular}
+      \arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
+      \arrow{hh2}{hf2}
+      \arrow{hh3}{hf3}
+      \arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
+      \arrow{vh2}{vf2}
+    \end{center}
+  \end{column}
+\end{columns}
 
 \end{frame}
+
+% Results
+
+% Impact of Shared Memory
+
+% Future Work
+
+% Source code and data available
+% May be downloaded if you want to replicate the test

### 2014-09-07 build.pl
Added frame presenting visualization.

@@ -12,9 +12,10 @@ if($num_args!=1) {
     help_and_exit();
 }
 
+system("gnuplot msswarp.gnuplot");
+
 $target=$ARGV[0];
 if($target eq "paper"){
-    system("gnuplot msswarp.gnuplot");
     chdir "paper/";
     system("pdflatex -shell-escape GAME_HARD_01.tex");
     system("bibtex web.aux");

### 2014-09-08 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Added frame presenting visualization.
Moved results and shared memory impacts to section Contribution.
Added closing frame.
Authored draft conclusion material under section CONCLUSION.

--- 2014-08-24 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
@@
 % GAME_HARD_01_PRESENTATION_CONCLUSION.tex
+
+% CONCLUSION
 \section{Conclusion}
+\begin{frame}
+\frametitle{CONCLUSION}
 
-% SUBSECTION
-\subsection{Subsection}
-\begin{frame}
-\frametitle{SUBSECTION}
+\begin{itemize}
+\item Results indicate a major performance boost using WARP, when compared to that of the reference device driver
+  \begin{itemize}
+  \item Accounting for roughly three orders of magnitude
+  \end{itemize}
+\item However, important to keep in mind that the drivers may be useful for different purposes
+  \begin{itemize}
+  \item This calls into question what the flaws of using WARP, in place of the reference device driver, may be
+  \end{itemize}
+\end{itemize}
 
 \end{frame}
+
+% FUTURE WORK
+\subsection{Future Work}
+\begin{frame}
+\frametitle{FUTURE WORK}
+
+% Investigate potential memory bandwidth bottleneck
+% Establish what the flaws of using WARP are
+% Potential use-case: the acceleration of graphics in some virtual platforms
+% Double floating point precision
+% Complex kernel experiment
+
+\end{frame}

### 2014-09-08 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Authored draft future work material under section CONCLUSION.

@@
 
-% Investigate potential memory bandwidth bottleneck
-% Establish what the flaws of using WARP are
-% Potential use-case: the acceleration of graphics in some virtual platforms
-% Double floating point precision
-% Complex kernel experiment
+\begin{enumerate}
+\item Microsoft speculates memory bandwidth as a potential bottleneck for throughput-oriented workloads on latency-oriented systems
+\item Investigate the performance of WARP in coagency with more complex workloads
+\item For brevity, establish whether or not there may be precisional discrepency in double floating point precision
+\end{enumerate}
+
+A potential use-case worthy of investigating may be using WARP-like technologies for the purposes of accelerating graphics in virtual platforms.
 
